### 2017-02-22 Paper/Paper.tex
Skeleton for paper

\documentclass[a4paper,UKenglish]{lipics-v2016}
%This is a template for producing LIPIcs articles. 
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
% for section-numbered lemmas etc., use "numberwithinsect"

\usepackage{microtype}%if unwanted, comment out or use option "draft"

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

\bibliographystyle{plainurl}% the recommended bibstyle

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{A Sample Article for the LIPIcs series\footnote{This work was partially supported by someone.}}
\titlerunning{A Sample LIPIcs Article} %optional, in case that the title is too long; the running title should fit into the top page column

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{John Q. Open}
\author[2]{Joan R. Access}
\affil[1]{Dummy University Computing Laboratory, Address/City, Country\\
  \texttt{open@dummyuniversity.org}}
\affil[2]{Department of Informatics, Dummy College, Address/City, Country\\
  \texttt{access@dummycollege.org}}
\authorrunning{J.\,Q. Open and J.\,R. Access} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

\Copyright{John Q. Open and Joan R. Access}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
\keywords{Dummy keyword -- please provide 1--5 keywords}% mandatory: Please provide 1-5 keywords
% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Acces}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Praesent convallis orci arcu, eu mollis dolor. Aliquam eleifend suscipit lacinia. Maecenas quam mi, porta ut lacinia sed, convallis ac dui. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Suspendisse potenti. 
 \end{abstract}

\section{Introduction}

\section{Preliminaries}
Recall syntax, define colimit, interval, homotopy pushout.

\section{The Approximator}
Given a HIT, define a sequence $F : \mathbb{N} \rightarrow Type$ (approximator), and approximations $F n$ for $n : \mathbb{N}$.

\section{The Rules}

\subsection{Introduction Rules}

\subsection{Elimination Rule}

\subsection{Computation Rules}

\section{Lemmata}

\begin{lemma}
Colimits commute with coproducts.
\end{lemma}

\begin{lemma}
Colimits commute with products.
\end{lemma}

\begin{lemma}
Colimits commute with pullbacks.
\end{lemma}

\section{Conclusion and Further Work}

%%
%% Bibliography
%%

%% Either use bibtex (recommended),

\bibliography{lipics-v2016-sample-article}

%% .. or use the thebibliography environment explicitely

\end{document}

### 2017-02-25 Paper/Paper.tex
Added introduction, preliminaries, basic definition and start on rules.

@@
 % Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{A Sample Article for the LIPIcs series\footnote{This work was partially supported by someone.}}
-\titlerunning{A Sample LIPIcs Article} %optional, in case that the title is too long; the running title should fit into the top page column
+\title{The Three-HIT Theorem\footnote{This work was partially supported by someone.}}
+\titlerunning{The Three-HIT Theorem} %optional, in case that the title is too long; the running title should fit into the top page column
 
 %% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
-\author[1]{John Q. Open}
-\author[2]{Joan R. Access}
-\affil[1]{Dummy University Computing Laboratory, Address/City, Country\\
-  \texttt{open@dummyuniversity.org}}
-\affil[2]{Department of Informatics, Dummy College, Address/City, Country\\
-  \texttt{access@dummycollege.org}}
-\authorrunning{J.\,Q. Open and J.\,R. Access} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
+\author[1]{Andrej Bauer}
+\author[2]{Niels van der Weide}
+\affil[1]{Department of Mathematics and Physics, University of Ljubljana, Ljubljana, Slovenia\\
+  \texttt{Andrej.Bauer@andrej.com}}
+\affil[2]{Department of Computer Science, Radboud University, Nijmegen, The Netherlands\\
+  \texttt{nweide@cs.ru.nl}}
+\authorrunning{A. Bauer and N. van der Weide} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
 
@@
 
+\usepackage[all,cmtip]{xy}
+\usepackage{xcolor}
+\usepackage{amssymb}
+\usepackage{amsthm}
+\usepackage{thmtools}
+
+\declaretheorem[style=definition,qed=$\blacksquare$]{construction}
+
+\input{coq.sty}
+\input{bussproofs.sty}
+
+\newcommand{\comment}[1]{-- #1 --}
+\newcommand{\remove}[1]{}
+\newcommand{\inn}{{\rm in}}
+
+\newcommand{\zero}[0]{\textbf{0}}
+\newcommand{\one}[0]{\textbf{1}}
+\newcommand{\two}[0]{\textbf{2}}
+
+\newcommand{\frec}[0]{\!\operatorname{rec}}
+\newcommand{\rec}[0]{\operatorname{rec}}
+\newcommand{\nonrec}[0]{\operatorname{nonrec}}
+
+\newcommand{\ap}[0]{\operatorname{ap}}
+\newcommand{\apd}[0]{\operatorname{apd}}
+
+\newcommand{\term}[0]{\textbf{term}}
+\newcommand{\Con}[0]{\textbf{Con}}
+\newcommand{\Approx}[0]{\textbf{Approx}}
+
+\newcommand{\hpushout}[0]{\operatorname{\textbf{hpushout}}}
+\newcommand{\hocolim}[0]{\operatorname{\textbf{hocolim}}}
+\newcommand{\seg}[0]{\operatorname{\textbf{seg}}}
+\newcommand{\inl}[0]{\operatorname{\textbf{inl}}}
+\newcommand{\inr}[0]{\operatorname{\textbf{inr}}}
+\newcommand{\glue}[0]{\operatorname{\textbf{glue}}}
+\newcommand{\inc}[0]{\operatorname{\textbf{inc}}}
+\newcommand{\com}[0]{\operatorname{\textbf{com}}}
+\newcommand{\Type}[0]{\operatorname{\textsc{Type}}}
+\newcommand{\pt}[0]{*}
+
+\newcommand{\dak}[1]{\widehat{#1}}
+\newcommand{\hatt}{\dak{t}}
+\newcommand{\hatr}{\dak{r}}
+
 \begin{document}
@@
 \section{Introduction}
+Higher inductive types extend normal inductive types by allowing constructors for equations as well rather than just for the points.
+Numerous examples and definitions of higher inductive types have been given in the literature \cite{altenkirch2016quotient,awodey2012inductive,basoldhigher,sojakova2015higher,hottbook}, but a definition with a good metatheory remains to be given.
+As a step towards that goal, we simplify the definition given in \cite{basoldhigher} bringing it closer to the intuition and the meaning.
+
+Philosophically, one sees an inductive type as a type `which is built step by step'.
+One starts with the nonrecursive constructors, and then at each step new terms are added by applying the recursive constructors to the previously built terms.
+This is explained by a theorem which says that inductive types are initial algebras for a functor \cite{dybjer1994inductive,dybjer2003induction} and how these algebras are obtained \cite{adamek1974free}.
+For higher inductive types one would expect a similar result which explains philosophically what they are.
+The only difference between higher inductive types and normal inductive types is that during the construction of higher inductive types several identifications are made which are described by the path constructors.
+
+The goal of this paper is to show that the higher inductive types defined in \cite{basoldhigher} can be generated from the interval, homotopy pushouts and colimits, and that formally justifies this intuition on higher inductive types,
+Also, this generalizes the results in \cite{doorn2016constructing,kraus2014general,kraus2016constructions} where the result is showed for truncations.
+With this result the metatheory of higher inductive types could be simplified significantly, because rather than a general class, one only needs to check for three types.
+
+In Section \ref{sec:prelims} we shall discuss some of the required notions for this paper.
+More concretely, we recall the definition of a higher inductive, and show the interval, the pushout, and the homotopy colimit.
+Next we define the approximating sequence of a higher inductive type in Section \ref{sec:approximator}, and in Section \ref{sec:rules} we show that the colimit of this sequence satisfies the rules of the given HIT.
+For this we need some lemmata which are proved in Section \ref{sec:Lemmata}.
 
 \section{Preliminaries}
-Recall syntax, define colimit, interval, homotopy pushout.
+\label{sec:prelims}
+Let us briefly recall the scheme of higher inductive types which we shall use \cite{basoldhigher}.
+First of all, we need polynomial functors.
+\begin{definition}
+Let $X$ be a variable.
+Then a \emph{polynomial} is given by the following grammar.
+\[
+F, G ::= A : \Type \ | \ X \ | \ F \times G \ | \ F + G
+\]
+\end{definition}
+A possible extension would be to use arbitrary containers as in \cite{abbott2005containers}, but we shall refrain to do so
+When we tried to do the proof with that extension, we needed the axiom of choice which does not hold in general in type theory.
+One can prove that polynomials are functors, and that given a type family $Y : T \rightarrow \Type$ and a polynomial $F$, we get a lift $\bar{F} : F \> T \rightarrow \Type$.
+We will write $F \> f$ to denote the application of a polynomial $F$ to a map $f$.
+
+Next we define the notion of a constructor term.
+\begin{definition}
+Given are functions $c_i : H_i \> T \rightarrow T$ for $i = 1, \ldots, k$.
+Then we say $t$ is a \emph{constructor term} over the $c_i$ if we can find polynomials $F$ and $G$ such that $x : F \> T \Vdash t : G \> T$ can be derived using the following rules.
+\begin{gather*}
+	\AxiomC{$t : A$}
+	\AxiomC{$T$ does not occur in $A$}
+	\BinaryInfC{$x:F \> T \Vdash t : A$}
+	\bottomAlignProof
+	\DisplayProof 
+	 \quad
+	\AxiomC{}
+	\UnaryInfC{$x : F \> T \Vdash x : F \> T$}
+	\bottomAlignProof
+	\DisplayProof
+	\quad
+	\AxiomC{$x : F \> T \Vdash r : H_i \> T$}
+	\UnaryInfC{$x : F \> T \Vdash c_i \> r : T$}
+	\bottomAlignProof
+	\DisplayProof
+	\\[7pt]
+	\AxiomC{$j \in \{1, 2\}$}
+	\AxiomC{$x : F \> T \Vdash r : G_1 \> T \times G_2 \> T$}
+	\BinaryInfC{$x : F \> T \Vdash\pi_j \> r : G_j \> T$}
+	\bottomAlignProof
+	\DisplayProof
+	\quad
+	\AxiomC{$j \in \{1, 2\}$}
+	\AxiomC{$x : F \> T \Vdash r_j : G_j$}
+	\BinaryInfC{$x : F \> T \Vdash (r_1, r_2) : G_1 \> T\times G_2 \> T$}
+	\bottomAlignProof
+	\DisplayProof
+	\\[7pt]
+	\AxiomC{$j \in \{1, 2\}$}
+	\AxiomC{$x : F \> T \Vdash r : G_j \> T$}
+	\BinaryInfC{$x : F \> T : \inn_j \> r : G_1 \> T + G_2 \> T$}
+	\bottomAlignProof
+	\DisplayProof
+\end{gather*}
+\end{definition}
+
+Using constructor terms we give the following scheme of higher inductive types.
+\begin{definition}
+A \emph{higher inductive type} is defined according to the following scheme
+\lstset{language=Coq}
+\begin{lstlisting}
+Inductive $H$ :=
+| $c$ : $A \> H \rightarrow H$
+| $p_i$ : $\prod (x : B_i \> H), t_i = r_i$ $\quad (i = 1, \ldots, m)$
+\end{lstlisting}
+where $A$ and each $B_i$ are polynomials, and each $t_i$ and $r_i$ are constructor terms over $c$ of type $H$ with $x : B_i \> H$ as variable..
+\end{definition}
+
+Before we can give the rules for higher inductive types, we need to define the lift of a constructor term.
+\begin{definition}
+Given is a constructor $c : A \> H \rightarrow H$, a type family $Y : H \rightarrow \Type$, and a term
+\[
+ \vdash f : \prod (x: A \> H), \bar{A} \> Y \> x \rightarrow  Y(c \> x).
+\]
+For a constructor term $F \> H \Vdash r : G \> H$ we define the \emph{lift $\dak{r}$ of $r$} with type
+\[
+ x : F \> H, h_x : \bar{F} \> Y \> x \vdash \dak{r} : \bar{G} \> Y \> r
+\]
+by induction in $r$ as follows.
+	\begin{align*}
+		\dak{t} & := t
+		& \dak{x} & := h_x &
+		\dak{c_i \> r} & := f_i \> r \> \dak{r}\\
+		\dak{\pi_j \> r} & := \pi_j \> \dak{r} &
+		\dak{(r_1, r_2)} & := (\dak{r_1}, \dak{r_2})
+		& \dak{\inn_j \> r} & := \dak{r}
+	\end{align*}
+\end{definition}
+
+The introduction rules for $H$ are
+\[
+c : A \> H \rightarrow H,
+\]
+\[
+p_i : \prod (x : B_i \> H), t_i = r_i.
+\]
+We also have an elimination rule for which we use the lifting of constructor terms.
+\begin{equation*}
+	\AxiomC{$\vdash Y : H \rightarrow \Type$}
+	\noLine
+	\UnaryInfC{$\vdash f : \prod (x : A \> H), \bar{A} \> Y \> x \rightarrow Y \> (c \> x)$}
+%	\noLine
+	\AxiomC{$\vdash q_i : \prod (x : B_i \> H) (h_x : \bar{B}_i \> Y \> x), \hatt_i =_{p_j \, x} \hatr_j$}
+	\BinaryInfC{$\vdash H\frec(f, q_1, \ldots, q_n) : \prod (x : H), Y \> x$}
+	\DisplayProof
+\end{equation*}
+Let us abbreviate $H\frec(f, q_1, \ldots, q_n)$ by $H\frec$.
+The type $H$ also has computation rules for each point $t : A \> H$
+\begin{equation*}
+H\frec \> (c_i \> t) \equiv f_i \> t \> (A \> H\frec \> t),
+\end{equation*}
+and for each $a : B_i \> H$
+\begin{equation*}
+\apd \> H\frec \> (p_j \> a) \equiv q_j \> a \> (\bar{B}_i \> H\frec \> a.
+\end{equation*}
+
+Let us finish by defining some examples of higher inductive types which will be used a lot in this paper.
+The first would be the interval
+\lstset{language=Coq}
+\begin{lstlisting}
+Inductive $I^1$ :=
+| $0$ : $I^1$
+| $1$ : $I^1$
+| $\seg$ : $0 = 1$
+\end{lstlisting}
+Note that for every type $A$ with inhabitants $x$ and $y$ we have a path $x = y$ iff we have a map $I^1$ to $A$ sending 0 and 1 to $x$ and $y$ respectively.
+Let $\one$ be the unit type with point $\pt$.
+Then we can define maps $\delta_0, \delta_1 : \one \rightarrow$ sending $\pt$ to 0 and 1 respectively.
+Also, we define $\delta : \one + \one \rightarrow I^1$ by $\delta_0 + \delta_1$.
+
+Next we define the homotopy pushout.
+\lstset{language=Coq}
+\begin{lstlisting}
+Inductive $\hpushout$ $(A, B, C : \Type)$ $(f : A \rightarrow B)$ $(g : A \rightarrow C)$ :=
+| $\inl$ : $B \rightarrow$ $\hpushout$ $A$ $B$ $C$ $f$ $g$
+| $\inr$ : $C \rightarrow$ $\hpushout$ $A$ $B$ $C$ $f$ $g$
+| $\glue$ : $\prod (a : A), \inl (f \> a) = \inr (g \> a)$
+\end{lstlisting}
+Note the similarities with the construction of the pushout.
+Also, we can define the homotopy colimit as a higher inductive type in much the same way.
+\lstset{language=Coq}
+\begin{lstlisting}
+Inductive $\hocolim$ $(F : \mathbb{N} \rightarrow \Type)$ $(f : \prod (n : \mathbb{N}, F \> n \rightarrow F(n+1)))$ :=
+| $\inc$ : $\prod (n : \mathbb{N}), F \> n \rightarrow$ $\hocolim$ $F$ $f$
+| $\com$ : $\prod (n : \mathbb{N}) (x : F \> n), \inc \> n \> x = \inc \> (n+1) \> (f \> n \> x)$
+\end{lstlisting}
 
 \section{The Approximator}
-Given a HIT, define a sequence $F : \mathbb{N} \rightarrow Type$ (approximator), and approximations $F n$ for $n : \mathbb{N}$.
+\label{sec:approximator}
+Let us assume that we some higher inductive type $H$ is given.
+In order to construct $H$ as a colimit, we first need to give how the approximations in the colimit are given, and for that we define the \emph{approximator}.
+
+Before giving the definition, let us think about how it should be given.
+By Ad\'amek's theorem, every inductive type can be given as a colimit.
+An inductive type $T$ is given by a polynomial functor $F$ and a constructor $c : F \> T \rightarrow T$, and then $T$ is the colimit of the sequence
+\[
+\xymatrix
+{
+	\zero \ar[r] & F \> \zero  \ar[r] & F(F \> \zero) \ar[r] & \ldots
+}
+\]
+To understand what this does, let us assume that $F \> X = X + 1$, so that $T = \mathbb{N}$.
+This means we have two inclusions  $\xymatrix{1 \ar[r] & 1+X}$ and  $\xymatrix{X \ar[r] & 1+X}$, and we call them $0_C$ and $S_C$ respectively.
+At every step we formally add for each $x : X$ a successor $S_C \> x$, and we add $0_C$.
+Repeatedly applying this construction to the empty type $\zero$ gives the natural numbers $\mathbb{N}$.
+
+For higher inductive types one would like to do a similar construction.
+However, since extra equalities might be present in the higher inductive type, several tweaks need to be made to the construction.
+Rather than just adding points at every step, identifications need to be made as well.
+
+To understand what should be done more precisely, let us consider an example.
+\lstset{language=Coq}
+\begin{lstlisting}
+Inductive $\mathbb{N}_2$ :=
+| $0$ : $\mathbb{N}_2$
+| $S$ : $\mathbb{N}_2 \rightarrow \mathbb{N}_2$
+| $p$ : $S(S \> 0) = 0$
+\end{lstlisting}
+The first approximation is the empty type, and after that we add a constructor for 0 to obtain the first approximation.
+After the third step we found inhabitants $0$, $S \> 0$, and $S(S \> 0)$ in the approximation $F(3)$, and now we can make the first identification.
+At this step we can do a homotopy pushout
+\[
+\xymatrix
+{
+	\one + \one \ar[d]_{0 + S(S \> 0)} \ar[r]^-{\delta} & I^1 \ar[d]\\
+	F(3) \ar[r] & F'(3)
+}
+\]
+to obtain the fixed third approximation $F'(3)$, and we continue our construction with that.
+To glue in $F \> n$, we need to use the elements from $F(n-2)$.
+So, the approximator $F$ the parameter should be one of the previous approximations of which the identifications can be taken.
+
+Note that one always have to go back a fixed number of steps due to the usage of constructor terms.
+By extending the syntax, one can also think of examples where one needs to go back an arbitrary amount of steps.
+For that we consider the following example.
+\lstset{language=Coq}
+\begin{lstlisting}
+Inductive $\mathbb{N}_2$ :=
+| $0$ : $\mathbb{N}_2$
+| $S$ : $\mathbb{N}_2 \rightarrow \mathbb{N}_2$
+| $p$ : $\prod (n : \mathbb{N}), S^n \> 0 = 0$
+\end{lstlisting}
+This example might seem like it is allowed in the syntax, but it is not.
+The term $S^n$ is defined as a polymorphic function which needs the type as argument, and that is not allowed with constructor terms.
+In this extension the construction will be more complicated, and the construction is not predicative, so this will not be considered in this paper.
+
+Let us make this idea more precise, and for that we start with a higher inductive type which is given as follows.
+\lstset{language=Coq}
+\begin{lstlisting}[label={lst:HIT}]
+Inductive $H$ :=
+| $c_{\nonrec}$ : $A_{\nonrec} \rightarrow H$
+| $c_{\rec}$ : $A_{\rec} \> H \rightarrow H$
+| $p_i$ : $\prod (x : B_i \> H), t_i = r_i$ $\quad (i = 1, \ldots, m)$
+\end{lstlisting}
+Note that the nonrecursive and recursive point constructor are separated in this definition.
+Our first approximation will be given using the nonrecursive constructors.
+\lstset{language=Coq}
+\begin{lstlisting}
+Inductive $H_{\nonrec}$ :=
+| $c_{\nonrec}'$ : $A_{\nonrec} \rightarrow H_{\nonrec}$
+\end{lstlisting}
+
+Next we need to generate the further approximations, and that will be done in two steps.
+First, we note that using the recursive constructors we can extend a type by using its inhabitants as the arguments.
+\lstset{language=Coq}
+\begin{lstlisting}
+Inductive $H_{\rec}$ $(P : \Type)$:=
+| $c_{\rec}'$ : $A_{\rec} \> P \rightarrow H_{\rec} \> P$
+\end{lstlisting}
+To do the identifications, we need to be able to interpret the constructor terms.
+For that we realize that each constructor terms uses each constructor only a finite amount of times, and thus there is a maximum number $n$ of times a constructor is used.
+From this we can define the \emph{approximator}.
+With this we can define
+\lstset{language=Coq}
+\begin{lstlisting}
+Inductive $H_{\Con}$ $(P : \Type)$:=
+| $\term$ : $P + H_{\rec} \> P + \ldots + H_{\rec}^n \> P \rightarrow H_{\Con} \> P$
+\end{lstlisting}
+
+\begin{lemma}
+A constructor term $t_i$ using a variable $x : B_i \> P$ with depth at most $n$ induces a map $B_i \> P \rightarrow H_{\Con}$.
+\end{lemma}
+
+\begin{definition}
+Let a higher inductive type $H$ be given as before, and let the types $H_{\Con}$ be defined as before.
+Then we define the \emph{approximator} $H_{\Approx}$, which has a parameter $P$, of $H$ the following pushout
+\[
+\xymatrix
+{
+	\sum_{i = 1}^m ((\one + \one) \times B_i \> P) \ar[d]_{t_i + r_i} \ar[r]^-\delta & \sum_{i = 1}^m (I^1 \times B_i \> P) \ar[d]\\
+	H_{\Con} \> P \ar[r]_{q_1} & H_{\Approx} \> P
+}
+\]
+Note that this can be written as the homotopy pushout.
+\end{definition}
+
+\begin{definition}
+In the setting as described, we can define a sequence of approximations to $H$ as follows
+\begin{align*}
+F \> 0 &= H_{\nonrec},\\
+F(n+1) &= H_{\Approx}(H \> n) \qedhere
+\end{align*}
+\end{definition}
+
+For the colimit we also need maps $f \> n : F \> n \rightarrow F(n + 1)$.
+Note that we always have the following sequence of maps
+\[
+\xymatrix@1
+{
+	P \ar[r] & H_{\Con} \> P \ar[r] & H_{\Approx} P.
+}
+\]
+Taking $P$ to be $F \> n$, then we have $F (n+1) = H_{\Approx} (F \> n)$, and thus the composition gives the map $F \> n \rightarrow F(n + 1)$.
 
 \section{The Rules}
+\label{sec:rules}
+Now we have a candidate for the higher inductive type, namely $\hocolim \> F \> f$.
+In this section we shall prove that we can define the introduction rules, the eliminator, and show the computation rules.
+We will do this step by step, and refer to lemmata in Section \ref{sec:Lemmata}.
 
 \subsection{Introduction Rules}
+In order to show that this is the desired type, we first show that it has the correct introduction rules.
+These come in three flavors: the nonrecursive and the recursive points, and the paths.
+
+Let us start by defining a map $A_{\nonrec} \rightarrow \hocolim \> F \> f$ which gives the introduction rule for the nonrecursive point constructors.
+Since $F \> 0$ is defined by $H_{\nonrec}$, which has a constructor $c'_{\nonrec} : A_{\nonrec} \rightarrow H_{\nonrec}$, this can be defined by the following composition.
+\[
+\xymatrix
+{
+	A_{\nonrec} \ar[rr]^-{c'_{\nonrec}}
+		& & F \> 0 \ar[rr]^-{\inc}
+		& & \hocolim \> F \> f
+}
+\]
+
+Next we show that we also have the recursive constructor meaning that we have a map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
+This is slightly more complicated, and for that we first need a lemma which says that colimits over $\mathbb{N}$ commute with polynomials.
+
+\begin{lemma}
+\label{lem:colim_commute_poly}
+The types $A \> (\hocolim \> F \> f)$ and $\hocolim \> (A \circ F) \> (A \> f)$ are isomorphic for all polynomials $A$.
+\end{lemma}
+
+\begin{proof}
+
+\end{proof}
+
+Now we will construct the map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$, and by Lemma \ref{lem:colim_commute_poly} it suffices to make a map $\hocolim \> (A_{\rec} \circ F) \> (A \> f) \rightarrow \hocolim \> F \> f$.
+For this we use the recursion rule of $\hocolim$, and we start with the following string of maps
+\[
+\xymatrix
+{
+		A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} 
+		& H_{\rec}(F \> n) \ar[rr]^{\term \circ \iota_1} &
+		& H_{\Con}(F \> n) \ar[r]^-{q_1}
+		& H_{\Approx}(F \> n) = F(n + 1)
+}
+\]
+where the map $H_{\rec}(F \> n) \rightarrow H_{\Con}(F \> n)$ is the inclusion and the map $H_{\Con}(F \> n) \rightarrow H_{\Approx}(F \> n)$ is the pushout map.
+Composing this map with $\inc$, gives maps $A_{\rec}(F \> n) \rightarrow \hocolim \> F \> f$ for all $n : \mathbb{N}$.
+
+Next we need to show the commutativity of the following triangle.
+\[
+\xymatrix
+{
+	A_{\rec}(F \> n) \ar[rr]^{A \> f \> n} \ar[dr] & & A_{\rec}(F(n+1)) \ar[dl] \\
+	& \hocolim \> F \> f &
+}
+\]
+Let us start with the following rectangle
+\[
+\xymatrix
+{
+	A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} \ar[d]_{A \> f \> n} 
+		& H_{\rec}(F \> n) \ar[rr]^{\term \circ \iota_1} \ar[d]_{H_{\rec} \> f \> n} &
+		& H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> f \> n}\\
+	A_{\rec}(F(n+1)) \ar[r]_-{c_{\rec}'} 
+		& H_{\rec}(F(n+1)) \ar[rr]_{\term \circ \iota_1} &
+		& H_{\Con}(F(n+1))
+}
+\]
+The left square commutes, because by definition of $H_{\rec} \> f$ we have
+\[
+H_{\rec} \> f \> n \> (c_{\rec}' x) = c_{\rec}' (A_{\rec} \> f \> n \> x).
+\]
+For a similar reason the right triangle commutes as well.
+Hence, it suffices to show that the following diagram commutes.
+\[
+\xymatrix
+{
+	H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> f \> n} \ar[r]^-{q_1}
+		& H_{\Approx}(F \> n) \ar[d]^{f \> n}\\
+	H_{\Con}(F(n+1)) \ar[r]_-{q_1}
+		& H_{\Approx}(F(n+1))
+}
+\]
+By expanding the definitions, we see that $H_{\Approx}(F \> n) \rightarrow H_{\Approx}(F(n+1))$ is defined by $p_1 \circ \term \circ \iota_1$.
+This means that it suffices to show that the upper triangle in the following square commutes.
+\[
+\xymatrix
+{
+	H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> f \> n} \ar[r]^{p_1}
+	& H_{\Approx}(F \> n) \ar[d]^{f \> n} \ar[dl]|{\term \circ \iota_0}\\
+	H_{\Con}(F(n+1)) \ar[r]_{p_1}
+	& H_{\Approx}(F(n+1))
+}
+\]
+The upper triangle commutes by definition.
+All in all, we get the desired map
+\[
+\xymatrix
+{
+	A \> (\hocolim \> F \> f) \ar[r] & \hocolim \> (A \circ F) \> (A \> f) \ar[r] & \hocolim \> F \> f
+}
+\]
+
+Next we need to define the introduction rules for the paths.
+For this we first need to observe that a type $X$ has the paths $p_i : \prod (x : B_i \> X), t_i = r_i$ iff the following diagram is a pushout
+\[
+\xymatrix
+{
+	\sum_{i = 1}^m \two \times (B_i \> X) \ar[r] \ar[d]_{t_i + r_i} & \sum_{i = 1}^m B_i \> X \times I^1 \ar[d]\\
+	X \ar[r] & X
+}
+\]
+We shall use this observation to show that $\hocolim \> F \> f$ has the right paths.
+Taking $X$ to be $\hocolim \> F \> f$, we thus need to show the following diagram is a pushout.
+\[
+\xymatrix
+{
+	\sum_{i = 1}^m \two \times (B_i \> (\hocolim \> F \> f)) \ar[r] \ar[d] & \sum_{i = 1}^m I^1 \times (B_i \> (\hocolim \> F \> f)) \ar[d]\\
+	\hocolim \> F \> f \ar[r] & \hocolim \> F \> f
+}
+\]
+Note that homotopy colimits commute with products, so we can rewrite it to where the summations are implicit.
+\[
+\xymatrix
+{
+	\hocolim \> ((2 \times B_i) \circ F) \> ((2 \times B_i) \> f) \ar[r] \ar[d] & \hocolim \> ((B_i \times I) \circ F) \> ((B_i \times I) \> f) \ar[d]\\
+	\hocolim \> F \> f \ar[r] & \hocolim \> F \> f
+}
+\]
+Since homotopy colimits commute with pushouts, it suffices to show that
+\[
+\xymatrix
+{
+	\sum_{i=1}^m 2 \times (B_i \> (F \> n)) \ar[r] \ar[d] & \sum_{i=1}^k I^1 \times B_i (F \> n) \ar[d]\\
+	F(n+1) \ar[r] & F(n+1)
+}
+\]
+This holds by definition of $F(n+1)$.
 
 \subsection{Elimination Rule}
+The next step will be to show that $\hocolim \> F \> f$ has the right eliminator.
 
@@
 \section{Lemmata}
+\label{sec:Lemmata}
 
@@
 
+\nocite{*}
+
 %%

### 2017-02-27 Paper/Paper.tex
Fixed minor typos, improved sentences, proof of Lemma 5 added

@@
 % Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{The Three-HIT Theorem\footnote{This work was partially supported by someone.}}
+\title{The Three-HIT Theorem\footnote{This work was partially supported by COST Action CA15123.}}
 \titlerunning{The Three-HIT Theorem} %optional, in case that the title is too long; the running title should fit into the top page column
@@
 
-\Copyright{John Q. Open and Joan R. Access}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+%\Copyright{Andrej Bauer and Niels van der Weide}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
 
-\subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html .
-E.g., cite as "F.1.1 Models of Computation".
-\keywords{Dummy keyword -- please provide 1--5 keywords}% mandatory: Please provide 1-5 keywords
+\subjclass{F.4.1 Mathematical Logic}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
+\keywords{homotopy type theory, higher inductive types, category theory}% mandatory: Please provide 1-5 keywords
 % Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Introduction}
-Higher inductive types extend normal inductive types by allowing constructors for equations as well rather than just for the points.
-Numerous examples and definitions of higher inductive types have been given in the literature \cite{altenkirch2016quotient,awodey2012inductive,basoldhigher,sojakova2015higher,hottbook}, but a definition with a good metatheory remains to be given.
-As a step towards that goal, we simplify the definition given in \cite{basoldhigher} bringing it closer to the intuition and the meaning.
+Higher inductive types (HITs) extend normal inductive types by allowing constructors for both points and paths, rather than just for the points.
+While inductive types are freely generated from a signature, a higher inductive type is freely generated from a signature with equations.
+Numerous examples and definitions of such types have been given in the literature \cite{altenkirch2016quotient,awodey2012inductive,basoldhigher,sojakova2015higher,hottbook}, but a definition with a good metatheory remains to be given.
+As a step towards that goal, we simplify the definition given in \cite{basoldhigher} bringing it closer to the intuition and the intended meaning.
 
@@
 One starts with the nonrecursive constructors, and then at each step new terms are added by applying the recursive constructors to the previously built terms.
-This is explained by a theorem which says that inductive types are initial algebras for a functor \cite{dybjer1994inductive,dybjer2003induction} and how these algebras are obtained \cite{adamek1974free}.
+This is explained by a theorem which says that inductive types are initial algebras for a functor \cite{dybjer1994inductive,dybjer2003induction} and another one about how these algebras are obtained \cite{adamek1974free}.
 For higher inductive types one would expect a similar result which explains philosophically what they are.
@@
 Also, this generalizes the results in \cite{doorn2016constructing,kraus2014general,kraus2016constructions} where the result is showed for truncations.
-With this result the metatheory of higher inductive types could be simplified significantly, because rather than a general class, one only needs to check for three types.
+With this result the metatheory of higher inductive types could be simplified significantly, because rather than a general class, one only needs to check metatheoretical properties for three types.
 
 In Section \ref{sec:prelims} we shall discuss some of the required notions for this paper.
-More concretely, we recall the definition of a higher inductive, and show the interval, the pushout, and the homotopy colimit.
+More concretely, we recall the syntax of higher inductive types, and as examples we give the interval, the homotopy pushout, and colimit.
 Next we define the approximating sequence of a higher inductive type in Section \ref{sec:approximator}, and in Section \ref{sec:rules} we show that the colimit of this sequence satisfies the rules of the given HIT.
@@
 Let us briefly recall the scheme of higher inductive types which we shall use \cite{basoldhigher}.
-First of all, we need polynomial functors.
+First of all, we need \emph{polynomial functors}.
 \begin{definition}
@@
 \[
-F, G ::= A : \Type \ | \ X \ | \ F \times G \ | \ F + G
+F, G ::= B : \Type \ | \ X \ | \ F \times G \ | \ F + G
 \]
 \end{definition}
-A possible extension would be to use arbitrary containers as in \cite{abbott2005containers}, but we shall refrain to do so
-When we tried to do the proof with that extension, we needed the axiom of choice which does not hold in general in type theory.
+A possible extension would be to use arbitrary containers as in \cite{abbott2005containers}, but we shall refrain to do so.
+With that extension the given proof requires the axiom of choice which generally does not hold in type theory.
 One can prove that polynomials are functors, and that given a type family $Y : T \rightarrow \Type$ and a polynomial $F$, we get a lift $\bar{F} : F \> T \rightarrow \Type$.
 We will write $F \> f$ to denote the application of a polynomial $F$ to a map $f$.
+Also, given $f : \prod (x : T), Y \> x$, one can define $\bar{F} \> f : \prod (x : H \> T), \bar{H} \> Y \> x$.
+Precise definitions of these are given in \cite{basoldhigher}.
 
@@
 \begin{definition}
-Given are functions $c_i : H_i \> T \rightarrow T$ for $i = 1, \ldots, k$.
-Then we say $t$ is a \emph{constructor term} over the $c_i$ if we can find polynomials $F$ and $G$ such that $x : F \> T \Vdash t : G \> T$ can be derived using the following rules.
+Given are functions $c : A \> T \rightarrow T$.
+Then we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F \> T \Vdash t : G \> T$ can be derived using the following rules.
 \begin{gather*}
-	\AxiomC{$t : A$}
-	\AxiomC{$T$ does not occur in $A$}
-	\BinaryInfC{$x:F \> T \Vdash t : A$}
+	\AxiomC{$t : B$}
+	\AxiomC{$T$ does not occur in $B$}
+	\BinaryInfC{$x:F \> T \Vdash t : B$}
 	\bottomAlignProof
@@
 	\quad
-	\AxiomC{$x : F \> T \Vdash r : H_i \> T$}
-	\UnaryInfC{$x : F \> T \Vdash c_i \> r : T$}
+	\AxiomC{$x : F \> T \Vdash r : A \> T$}
+	\UnaryInfC{$x : F \> T \Vdash c \> r : T$}
 	\bottomAlignProof
@@
 \begin{definition}
+\label{def:hit}
 A \emph{higher inductive type} is defined according to the following scheme
@@
 \begin{definition}
-Given is a constructor $c : A \> H \rightarrow H$, a type family $Y : H \rightarrow \Type$, and a term
+Given are a constructor $c : A \> H \rightarrow H$, a type family $Y : H \rightarrow \Type$, and a term
 \[
@@
 
-The introduction rules for $H$ are
+With all these notions we can give the introduction, elimination and computation rules of higher inductive types.
+The introduction rules for $H$ as given in Definition \ref{def:hit} are
 \[
@@
 \begin{equation*}
-H\frec \> (c_i \> t) \equiv f_i \> t \> (A \> H\frec \> t),
+H\frec \> (c_i \> t) \equiv f_i \> t \> (\bar{A} \> H\frec \> t),
 \end{equation*}
@@
 \begin{equation*}
-\apd \> H\frec \> (p_j \> a) \equiv q_j \> a \> (\bar{B}_i \> H\frec \> a.
+\apd \> H\frec \> (p_j \> a) \equiv q_j \> a \> (\bar{B}_i \> H\frec \> a).
 \end{equation*}
+Note that these equalities are definitional rather than propositional.
 
 Let us finish by defining some examples of higher inductive types which will be used a lot in this paper.
-The first would be the interval
+The first one would be the interval
 \lstset{language=Coq}
@@
 \label{sec:approximator}
-Let us assume that we some higher inductive type $H$ is given.
-In order to construct $H$ as a colimit, we first need to give how the approximations in the colimit are given, and for that we define the \emph{approximator}.
+Let us assume that some higher inductive type $H$ is given.
+In order to construct $H$ as a colimit, we first need to give the approximations in the colimit, and for that we define the \emph{approximator}.
 
@@
 For higher inductive types one would like to do a similar construction.
-However, since extra equalities might be present in the higher inductive type, several tweaks need to be made to the construction.
-Rather than just adding points at every step, identifications need to be made as well.
+The first difference is that instead of starting with nothing and adding each constructor at every step, we start with the nonrecursive constructors, and add recursive constructors at every step.
+Also, since extra equalities might be present in the higher inductive type, we need to make identifications during the construction.
+Rather than just adding points at every step, we also need to glue the right paths.
 
@@
 \end{lstlisting}
-The first approximation is the empty type, and after that we add a constructor for 0 to obtain the first approximation.
-After the third step we found inhabitants $0$, $S \> 0$, and $S(S \> 0)$ in the approximation $F(3)$, and now we can make the first identification.
-At this step we can do a homotopy pushout
+The first approximation just has a constructor $0$, and after that we add a constructor for $S \> 0$ to obtain the second approximation.
+In the third approximation, which we call $F \> 3$, we found inhabitants $0$, $S \> 0$, and $S(S \> 0)$, and now we can make the first identification.
+To do so, we take the following homotopy pushout
 \[
@@
 	\one + \one \ar[d]_{0 + S(S \> 0)} \ar[r]^-{\delta} & I^1 \ar[d]\\
-	F(3) \ar[r] & F'(3)
+	F \> 3\ar[r] & P \> 3
 }
 \]
-to obtain the fixed third approximation $F'(3)$, and we continue our construction with that.
-To glue in $F \> n$, we need to use the elements from $F(n-2)$.
-So, the approximator $F$ the parameter should be one of the previous approximations of which the identifications can be taken.
+to obtain the actual third approximation $P \> 3$, and we continue our construction with that one.
+Note that to glue during the $n$th step, we need refer to elements from the $(n-2)$th step.
+So, in order to do the identification of the $n$th step, one needs to refer back to a previous approximation.
 
-Note that one always have to go back a fixed number of steps due to the usage of constructor terms.
+Note that one always has to go back a fixed number of steps due to the usage of constructor terms.
 By extending the syntax, one can also think of examples where one needs to go back an arbitrary amount of steps.
-For that we consider the following example.
+For that, we consider the following example.
 \lstset{language=Coq}
@@
 
-Let us make this idea more precise, and for that we start with a higher inductive type which is given as follows.
+Let us make this idea formal, and for that we start with a higher inductive type which is given as follows.
 \lstset{language=Coq}
@@
 \end{lstlisting}
-Note that the nonrecursive and recursive point constructor are separated in this definition.
-Our first approximation will be given using the nonrecursive constructors.
+Note that the nonrecursive and recursive point constructors are separated in this definition.
+The first approximation will be given using the nonrecursive constructors.
 \lstset{language=Coq}
@@
 
-Next we need to generate the further approximations, and that will be done in two steps.
-First, we note that using the recursive constructors we can extend a type by using its inhabitants as the arguments.
+Next we need to generate the other approximations, and that will be done in two steps.
+First, we note that types can be extended with a recursive constructor.
 \lstset{language=Coq}
@@
 To do the identifications, we need to be able to interpret the constructor terms.
-For that we realize that each constructor terms uses each constructor only a finite amount of times, and thus there is a maximum number $n$ of times a constructor is used.
-From this we can define the \emph{approximator}.
-With this we can define
+For that we use that each constructor terms only uses each constructor  a finite amount of times, and thus there is a maximum number $n \geq 1$ of times a constructor is used.
+In order to define the approximator, we start with a type $H_{\Con}^n$ in which all the constructor terms can be interpreted.
 \lstset{language=Coq}
 \begin{lstlisting}
-Inductive $H_{\Con}$ $(P : \Type)$:=
+Inductive $H_{\Con}^n$ $(P : \Type)$:=
 | $\term$ : $P + H_{\rec} \> P + \ldots + H_{\rec}^n \> P \rightarrow H_{\Con} \> P$
@@
 
+If $n$ is clear from the context, then we shall not write it down.
+
 \begin{lemma}
-A constructor term $t_i$ using a variable $x : B_i \> P$ with depth at most $n$ induces a map $B_i \> P \rightarrow H_{\Con}$.
+Suppose, we have a constructor term $t$ such that $x : F \> T \Vdash t : G \>T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow P$.
+Then $t$ induces a map $\overline{t} : F \> P \rightarrow G \> H_{\Con}^n$ by replacing the constructors $c_{\nonrec}$ and $c_{\rec}$ by $c_{\nonrec}'$ and $c_{\rec}'$ respectively.
 \end{lemma}
 
+\begin{proof}
+We use induction on the form of the constructor term.
+\begin{itemize}
+	\item $t = a$ with $a : B$ and $B$ does not use $T$. Then we define $\overline{t} \> y = a$.
+	\item $t = x$ with $x : F \> T$. Then we define $\overline{t} \> y = \inn_P y$.
+	\item $t = c_{\nonrec} a$ with $a : A_{\nonrec}$. Then we define $\overline{t} \> y = c_{\nonrec}' a$.
+	\item $t = c_{\rec} r$ with $r : A_{\rec} \> T$ where $r$ uses at most $n-1$ constructors. 
+			  By induction we have a map $\overline{r} : F \> P \rightarrow A_{\rec} \> H_{\Con}^{n-1}$.
+			  Then we define $\overline{t} \> y = c_{\rec}' (\overline{r} \> x)$.
+	\item For the rules for the projection, pairing and injection it is trivial. \qedhere
+\end{itemize}
+\end{proof}
+
 \begin{definition}
-Let a higher inductive type $H$ be given as before, and let the types $H_{\Con}$ be defined as before.
+Let a higher inductive type $H$ be given as before, and let the type $H_{\Con}$ be defined as before.
 Then we define the \emph{approximator} $H_{\Approx}$, which has a parameter $P$, of $H$ the following pushout
@@
 F \> 0 &= H_{\nonrec},\\
-F(n+1) &= H_{\Approx}(H \> n) \qedhere
+F(n+1) &= H_{\Approx}(F \> n) \qedhere
 \end{align*}

### 2017-03-01 Paper/Paper.tex
Continued work on elimination and introduction rule.

@@
 % Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{The Three-HIT Theorem\footnote{This work was partially supported by COST Action CA15123.}}
-\titlerunning{The Three-HIT Theorem} %optional, in case that the title is too long; the running title should fit into the top page column
+\title{The Three-HITs Theorem\footnote{This work was partially supported by COST Action CA15123.}}
+\titlerunning{The Three-HITs Theorem} %optional, in case that the title is too long; the running title should fit into the top page column
 
@@
 
+\newcommand{\conc}[0]{\bullet}
+
 \newcommand{\zero}[0]{\textbf{0}}
@@
 
+\newcommand{\refl}[0]{\operatorname{\textbf{refl}}}
 \newcommand{\hpushout}[0]{\operatorname{\textbf{hpushout}}}
@@
 
-The goal of this paper is to show that the higher inductive types defined in \cite{basoldhigher} can be generated from the interval, homotopy pushouts and colimits, and that formally justifies this intuition on higher inductive types,
+The goal of this paper is to show that the higher inductive types defined in \cite{basoldhigher} can be generated from the interval, homotopy pushouts and colimits, and that formally justifies this intuition on higher inductive types.
+More concretely, we will prove the following theorem.
+\begin{theorem}[Three-HITs Theorem]
+\label{thm:three-hit}
+In Martin-L\"of Type Theory extended with an interval object, homotopy pushouts and colimits, we can define for each higher inductive type as in \cite{basoldhigher} a tye with the same introduction, elimination and computation rules.
+\end{theorem}
 Also, this generalizes the results in \cite{doorn2016constructing,kraus2014general,kraus2016constructions} where the result is showed for truncations.
@@
 \]
-To understand what this does, let us assume that $F \> X = X + 1$, so that $T = \mathbb{N}$.
+To understand what this does, let us assume that $F \> X = 1 + X$, so that $T = \mathbb{N}$.
 This means we have two inclusions  $\xymatrix{1 \ar[r] & 1+X}$ and  $\xymatrix{X \ar[r] & 1+X}$, and we call them $0_C$ and $S_C$ respectively.
@@
 
+Now we have enough to define the approximator.
+During the construction one also needs to pay attention to coherency.
+For example, in $P$ we have $c_{\nonrec}$, so in $H_{\Approx} \> P$ we might have duplicates of some terms.
+By tweaking the pushout a little bit, one can easily solve these coherency problems.
+
 \begin{definition}
 Let a higher inductive type $H$ be given as before, and let the type $H_{\Con}$ be defined as before.
-Then we define the \emph{approximator} $H_{\Approx}$, which has a parameter $P$, of $H$ the following pushout
+Then we define the \emph{approximator} $H_{\Approx}$, which has a parameters $P, Q$ and $f : Q \rightarrow P$, of $H$ the following pushout
 \[
@@
 {
-	\sum_{i = 1}^m ((\one + \one) \times B_i \> P) \ar[d]_{t_i + r_i} \ar[r]^-\delta & \sum_{i = 1}^m (I^1 \times B_i \> P) \ar[d]\\
-	H_{\Con} \> P \ar[r]_{q_1} & H_{\Approx} \> P
+	((\one + \one) \times B_i \> P) + H_{\Con} \> Q \ar[d]_{\overline{t_i} + \overline{r_i} + H_{\Con} \> f} \ar[rr]^-{\delta + \inl} & & (I^1 \times B_i \> P) + H_{\Approx} Q  \ar[d]^{\inr}\\
+	H_{\Con} \> P \ar[rr]_{\inl} & & H_{\Approx} \> P
 }
@@
 \begin{definition}
-In the setting as described, we can define a sequence of approximations to $H$ as follows
+In the setting as described, we simultaneously define a sequence of approximations $F : \mathbb{N} \rightarrow \Type$ to $H$ and maps $f : \prod(n : \mathbb{N}), F \> n \rightarrow F(n+1)$ as follows
 \begin{align*}
 F \> 0 &= H_{\nonrec},\\
-F(n+1) &= H_{\Approx}(F \> n) \qedhere
+F \> 1 &= H_{\Approx} \> (F \> 0) \> \zero \> (\zero\frec (F \> 0))\\
+F(n+2) &= H_{\Approx} \> (F(n+1)) \> (F \> n) \> (f \> n) \qedhere
 \end{align*}
-\end{definition}
-
-For the colimit we also need maps $f \> n : F \> n \rightarrow F(n + 1)$.
-Note that we always have the following sequence of maps
+For the maps maps $f \> n : F \> n \rightarrow F(n + 1)$, note that we always have the following sequence of maps
 \[
@@
 Taking $P$ to be $F \> n$, then we have $F (n+1) = H_{\Approx} (F \> n)$, and thus the composition gives the map $F \> n \rightarrow F(n + 1)$.
+\end{definition}
 
@@
 \label{sec:rules}
-Now we have a candidate for the higher inductive type, namely $\hocolim \> F \> f$.
-In this section we shall prove that we can define the introduction rules, the eliminator, and show the computation rules.
-We will do this step by step, and refer to lemmata in Section \ref{sec:Lemmata}.
+Now we have defined an object $\hocolim \> F \> f$, which is supposed to interpret the higher inductive type.
+In order to finish the proof of Theorem \ref{thm:three-hit}, we need to show that it satisfies the rules.
+This means that we have to make functions which interpret the introduction rules, and an eliminator such that the computation rules are satisfied.
+We will do this step by step, and refer to lemmata in Section \ref{sec:Lemmata} when needed.
 
@@
 
-Let us start by defining a map $A_{\nonrec} \rightarrow \hocolim \> F \> f$ which gives the introduction rule for the nonrecursive point constructors.
+Let us start by defining a map $A_{\nonrec} \rightarrow \hocolim \> F \> f$ which gives the introduction rule for the nonrecursive point constructor.
 Since $F \> 0$ is defined by $H_{\nonrec}$, which has a constructor $c'_{\nonrec} : A_{\nonrec} \rightarrow H_{\nonrec}$, this can be defined by the following composition.
@@
 	A_{\nonrec} \ar[rr]^-{c'_{\nonrec}}
-		& & F \> 0 \ar[rr]^-{\inc}
+		& & F \> 0 \ar[rr]^-{\inc \> 0}
 		& & \hocolim \> F \> f
@@
 
-Next we show that we also have the recursive constructor meaning that we have a map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
+Next we show that we also have the recursive point constructor meaning that we have a map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
 This is slightly more complicated, and for that we first need a lemma which says that colimits over $\mathbb{N}$ commute with polynomials.
@@
 		A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} 
-		& H_{\rec}(F \> n) \ar[rr]^{\term \circ \iota_1} &
-		& H_{\Con}(F \> n) \ar[r]^-{q_1}
+		& H_{\rec}(F \> n) \ar[rr]^{\term \circ \iota_2} &
+		& H_{\Con}(F \> n) \ar[r]^-{\inl}
 		& H_{\Approx}(F \> n) = F(n + 1)
@@
 {
-	A_{\rec}(F \> n) \ar[rr]^{A \> f \> n} \ar[dr] & & A_{\rec}(F(n+1)) \ar[dl] \\
+	A_{\rec}(F \> n) \ar[rr]^{A_{\rec}(f \> n)} \ar[dr] & & A_{\rec}(F(n+1)) \ar[dl] \\
 	& \hocolim \> F \> f &
@@
 \]
+Before we continue, let us recall that inductive types are functors.
+Suppose, we have an inductive type $T$ with a parameter $P$, then a function $f : P \rightarrow Q$ gives a function $T \> f : T \> P \rightarrow T \> Q$.
 Let us start with the following rectangle
@@
 {
-	A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} \ar[d]_{A \> f \> n} 
-		& H_{\rec}(F \> n) \ar[rr]^{\term \circ \iota_1} \ar[d]_{H_{\rec} \> f \> n} &
-		& H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> f \> n}\\
+	A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} \ar[d]_{A_{\rec}(f \> n)} 
+		& H_{\rec}(F \> n) \ar[rr]^{\term \circ \iota_2} \ar[d]_{H_{\rec}(f \> n)} &
+		& H_{\Con}(F \> n) \ar[d]_{H_{\Con}(f \> n)}\\
 	A_{\rec}(F(n+1)) \ar[r]_-{c_{\rec}'} 
-		& H_{\rec}(F(n+1)) \ar[rr]_{\term \circ \iota_1} &
+		& H_{\rec}(F(n+1)) \ar[rr]_{\term \circ \iota_2} &
 		& H_{\Con}(F(n+1))
@@
 \[
-H_{\rec} \> f \> n \> (c_{\rec}' x) = c_{\rec}' (A_{\rec} \> f \> n \> x).
+H_{\rec} \>(f \> n) \> (c_{\rec}' x) = c_{\rec}' (A_{\rec} \> (f \> n) \> x).
 \]
@@
 {
-	H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> f \> n} \ar[r]^-{q_1}
-		& H_{\Approx}(F \> n) \ar[d]^{f \> n}\\
-	H_{\Con}(F(n+1)) \ar[r]_-{q_1}
+	H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> (f \> n)} \ar[r]^-{\inl}
+		& H_{\Approx}(F \> n) \ar[d]^{f(n+1)}\\
+	H_{\Con}(F(n+1)) \ar[r]_-{\inl}
 		& H_{\Approx}(F(n+1))
@@
 \]
-By expanding the definitions, we see that $H_{\Approx}(F \> n) \rightarrow H_{\Approx}(F(n+1))$ is defined by $p_1 \circ \term \circ \iota_1$.
-This means that it suffices to show that the upper triangle in the following square commutes.
+Note that $H_{\Approx}(F(n+1)) = F(n+2)$ and $H_{\Approx}(F \> n) = F(n+1)$.
+Hence, this diagram commutes, because of the pushout.
+
+Next we need to define the introduction rules for the paths.
+Let us start by making a map $\sum_{i = 1}^m I^1 \times B_i \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
+Since homotopy colimits commute with polynomials, it suffices to make a map $\hocolim \> (I^1 \times B_i \> F) \> (I^1 \> B_i \> f)  \rightarrow \hocolim \> F \> f$.
+
+For this we use the eliminator of the homotopy colimit.
+First, we need to make for all $n$ a map $I^1 \times B_i \> (F \> n)  \rightarrow \hocolim \> F \> f$.
+By definition we have the following string of maps
 \[
@@
 {
-	H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> f \> n} \ar[r]^{p_1}
-	& H_{\Approx}(F \> n) \ar[d]^{f \> n} \ar[dl]|{\term \circ \iota_0}\\
-	H_{\Con}(F(n+1)) \ar[r]_{p_1}
-	& H_{\Approx}(F(n+1))
+	I^1 \times B_i \> (F \> n) \ar[rr]^-{\inr} & & F(n+1) \ar[rr]^-{\inc(n+1)} & & \hocolim \> F \> f.
 }
 \]
-The upper triangle commutes by definition.
-All in all, we get the desired map
+Next we need to show that the following diagram commutes.
 \[
@@
 {
-	A \> (\hocolim \> F \> f) \ar[r] & \hocolim \> (A \circ F) \> (A \> f) \ar[r] & \hocolim \> F \> f
+	I^1 \times B_i \> (F \> n) \ar[rr]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n)} & & F(n+1) \ar[d]^{f(n+1)}\\
+	I^1 \times B_i \> (F(n+1)) \ar[rr]^-{\inr} & & F(n+2)
+}
+\]
+This can be proven by induction on $B_i$, and using the definition of $I^1 \times B_i \> (f \> n)$.
+We can use the path $\refl$.
+All in all, we get a map $p_i : \hocolim \> (I^1 \times B_i \> F) \> (I^1 \times B_i \> f) \rightarrow \hocolim \> F \> f$
+
+Now we have the following diagram
+\[
+\xymatrix
+{
+	2 \times B_i(\hocolim \> F \> f) \ar[r] \ar[dr]_{\overline{t_i} + \overline{r_i}} & I^1 \times B_i(\hocolim \> F \> f) \ar[r] & \hocolim \> (I^1 \times B_i \> F) \> (I^1 \times B_i \> f) \ar[dl]\\
+	& \hocolim \> F \> f
 }
@@
 
-Next we need to define the introduction rules for the paths.
-For this we first need to observe that a type $X$ has the paths $p_i : \prod (x : B_i \> X), t_i = r_i$ iff the following diagram is a pushout
+$2 \times B_i(\hocolim \> F \> f)$ is isomorphic to $\hocolim \> (2 \times B_i \> F) \> 2 (\times B_i \> f)$.
+
+Induction to second, so we have $(0, x)$ (similar for $1$) and $x : F \> n$.
+This gets mapped to $(0, x)$ which is equal to $t_i$ via the path $\glue (\inl (0, x))$.
+
+Remaining:
+\begin{equation*}
+\begin{split}
+\com_*(\ap \> (\inc \> n) \> \glue (\inl (0, x))) = \ap \> (\inc (n+1))) \>\glue (\inl (0, f \> n \> x))\\
+(\ap \> \overline{t_i} \> \com)^{-1} \conc \ap \> (\inc \> n) \> \glue (\inl (0, x)) \conc \ap \> p_i \> \com
+\end{split}
+\end{equation*}
+$(\ap \> \overline{t_i} \> \com)^{-1}$ is like $\ap \> (\inc \> n) \> (\ap \> c \> \ldots (\ldots \ap \> \text{coherence path}))$, because of the computation rule of $c_i$.
+
+This is the coherence path which should be added on level $n$.
+
+\subsection{Elimination Rule}
+For the next step we define the right eliminator for $\hocolim \> F \> f$. 
+For this we suppose that we have
+\[
+Y : \hocolim \> F \> f \rightarrow \Type
+\]
+\[
+c_{Y, \nonrec} : \prod (a : A_{\nonrec}), Y(c_{\nonrec})
+\]
+\[
+c_{Y, \rec} : \prod (x : A_{\rec} \> \hocolim \> F \> f), \overline{A_{\rec}} \> Y \> x \rightarrow Y(c_{\rec} \> x)
+\]
+\[
+q_{Y, i} : \prod (x : B_i \> H)(h_x : \overline{B_i} \> Y \> x), \hatt_i =_{p_j \, x} \hatr_j
+\]
+In order to make a map $\prod (x : \hocolim \> F \> f), Y \> x$, we use the induction principle of $\hocolim \> F \> f$, and for that we need to make maps $\prod (x : F \> n), Y(\inc \> n \> x)$.
+
+First we need to make a map $\prod (x : F \> 0), Y(\inc \> 0 \> x)$.
+Recall that $F \> 0$ was defined to be $H_{\nonrec}$ which only has a constructor $c'_{\nonrec} : A_{\nonrec} \rightarrow H_{\nonrec}$.
+So, let us assume that we have $a : A_{\nonrec}$.
+Since $c_{\nonrec} \> a = \inc \> 0 \> (c\_{\nonrec} a)$, it suffices to find an inhabitant of $Y(c_{\nonrec} \> a)$, and for that we take $c_{Y, \nonrec} \> a$.
+Hence, we get a map $\prod (x : F \> 0), Y(\inc \> 0 \> x)$.
+
+Now suppose that we have a map $\prod (x : F \> n), Y(\inc \> n \> x)$, and our goal is to make a map $\prod  (x : F(n+1)), Y(\inc \> (n+1) x)$.
+In order to do so, we will first look at how to extend it to a map $\prod (x : H_{\Con} (F \> n)), Y(\inc \> (n+1) \> (\inl \> x))$.
+
+Let us do this in the general case.
+Suppose that we have $g : P \rightarrow \hocolim \> F \> f$, and that we have $h : \prod (x : P), Y(g \> x)$.
+Our goal is to extended the map into a $h' : \prod (x : H_{\rec} P), Y(c_{Y, \rec} \> x)$, and for that we use $H_{\rec}$ induction.
+Note that for each $c'_{\rec} \> x$ with $x : A_{\rec} \> P$ we have the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$, and thus we have a type family on $H_{\rec}$.
+Now let $x : A_{\rec} \> P$ and $y : \overline{A_{\rec}} \> Y \> x$ be given.
+Then we need to give an element of the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$ for which we take
+\[
+c_{Y,\rec} \> (A_{\rec} \> g \> x) \> y
+\]
+Now we can also extend the map to $H_{\Con}^n \> P$, because we can define this map on each component.
+On the component $P$ it is just $h$, and on the other components we define it via extension.
+
+Next we need to extend the map to $H_{\Approx} \> P \> Q$.
+For that we need to make a map $h' : \prod (x : I^1 \times B_i \> P), Y()$
+
+Let $(t, x) : I^1 \times B_i \> P$, and now we use $I^1$ induction.
+If $t = 0$, we map it to $\hatt_i (x)$, and for $t = 1$ we map it to $\hatr_i (x)$.
+Now the path $q_{Y, i}$ gives the image of $\seg$, and that finishes the induction.
+
+For the commutativity of the diagram note that by definition the dependent map from $H_{\Con} \> P$ to $Y$ sends the constructor term $t_i$ to the lift $\hatt_i$.
+This is because the map replaces each $c_{\rec}$ by $c_{Y, \rec}$ which is precisely how the lift was constructed.
+
+Next we do it for the coherency.
+
+Induction on the level (so, ultimately some kind of simultaneous induction?)
+
+Then induction on the depth.
+
+Base case: just induction assumption.
+
+Step case: then it can be worked out from the diagram.
+
+To finish the proof, we need to give the image for the path $\com$.
+More concretely, we need to show that $\inc \> n \> x$ and $\inc \> (n+1) \> (f \> x)$ are mapped to the same element.
+The map $f : F \> n \rightarrow F(n + 1)$ is defined by the pushout as follows
 \[
@@
 {
-	\sum_{i = 1}^m \two \times (B_i \> X) \ar[r] \ar[d]_{t_i + r_i} & \sum_{i = 1}^m B_i \> X \times I^1 \ar[d]\\
-	X \ar[r] & X
+	((\one + \one) \times B_i \> (F(n+1))) + H_{\Con} \>  (F \> n) \ar[d]_{\overline{t_i} + \overline{r_i} + H_{\Con} \> f} \ar[rr]^-{\delta + \inl} & & (I^1 \times B_i \> (F(n+1))) + F(n+1)  \ar[d]^{\inr}\\
+	H_{\Con} \> (F(n+1)) \ar[rr]_{\inl} & & F(n+2)
 }
 \]
-We shall use this observation to show that $\hocolim \> F \> f$ has the right paths.
-Taking $X$ to be $\hocolim \> F \> f$, we thus need to show the following diagram is a pushout.
-\[
-\xymatrix
-{
-	\sum_{i = 1}^m \two \times (B_i \> (\hocolim \> F \> f)) \ar[r] \ar[d] & \sum_{i = 1}^m I^1 \times (B_i \> (\hocolim \> F \> f)) \ar[d]\\
-	\hocolim \> F \> f \ar[r] & \hocolim \> F \> f
-}
-\]
-Note that homotopy colimits commute with products, so we can rewrite it to where the summations are implicit.
-\[
-\xymatrix
-{
-	\hocolim \> ((2 \times B_i) \circ F) \> ((2 \times B_i) \> f) \ar[r] \ar[d] & \hocolim \> ((B_i \times I) \circ F) \> ((B_i \times I) \> f) \ar[d]\\
-	\hocolim \> F \> f \ar[r] & \hocolim \> F \> f
-}
-\]
-Since homotopy colimits commute with pushouts, it suffices to show that
-\[
-\xymatrix
-{
-	\sum_{i=1}^m 2 \times (B_i \> (F \> n)) \ar[r] \ar[d] & \sum_{i=1}^k I^1 \times B_i (F \> n) \ar[d]\\
-	F(n+1) \ar[r] & F(n+1)
-}
-\]
-This holds by definition of $F(n+1)$.
+Since the map to $Y$ was defined as the pushout map, it will commute automatically.
 
-\subsection{Elimination Rule}
-The next step will be to show that $\hocolim \> F \> f$ has the right eliminator.
+All in all, we have acquired a map $\prod (x : \hocolim \> F \> f), Y \> x$, and this way we defined the right eliminator for $\hocolim \> F \> f$.
+We shall call the eliminator $H\frec$.
 
 \subsection{Computation Rules}
+Lastly, we show that this eliminator also satisfies the computation rules.
+First, we prove that for each $t : A_{\rec}(\hocolim \> F \> f)$ that $H\frec(c_{\rec} \> t) \equiv f_i \> t \> (\overline{A_{\rec}} H\frec t)$.
+Again we use that colimits commute with polynomials.
+
+Let $n : \mathbb{N}$ and $x : A_{\rec}(F \> n)$.
+Then by the computation rules we have
+\begin{equation*}
+\begin{split}
+H\frec(c_{\rec} \> x) 
+&\equiv H\frec(\inc \> (n+1) \> (c_{\rec}' x)) \\
+&\equiv c_{Y,\rec} \> (A_{\rec} \> (\inc \> n) \> x) \> (\overline{A} \> H\frec \> x)\\
+\end{split}
+\end{equation*}
+Hence, we can always take $\refl$ to be the path.
+This will also give an image for $\com$, and thus the computation rules for the points are satisfied.
+
+Note that the this computation rule is a propositional equality.
+This is logical, because it is proven all $x : A_{\rec}(F \> n)$.
+However, for closed terms, we have a definitional equality.
+This is because $c_{\nonrec} \> a$ for $a : A_{\nonrec}$ is defined to be$\inc \> 0 \> (c_{\nonrec}' \> a)$.
+All the closed terms are thus inhabitants of some $F \> n$, and since at every step the equalities are definitional, we can conclude that for closed terms the equality is definitional.
+
+Now we show the computation rules for the paths.
 
@@
 \label{sec:Lemmata}
+
+\begin{lemma}
+$\hocolim \> (\lambda n . A) \> \operatorname{Id}$ is $A$.
+\end{lemma}
 
@@
 Colimits commute with products.
-\end{lemma}
-
-\begin{lemma}
-Colimits commute with pullbacks.
 \end{lemma}

### 2017-03-02 Paper/Paper.tex
Fixed typos, improved sentences

@@
 
-%\Copyright{Andrej Bauer and Niels van der Weide}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+\Copyright{Andrej Bauer and Niels van der Weide}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
 
@@
 \section{Introduction}
-Higher inductive types (HITs) extend normal inductive types by allowing constructors for both points and paths, rather than just for the points.
-While inductive types are freely generated from a signature, a higher inductive type is freely generated from a signature with equations.
-Numerous examples and definitions of such types have been given in the literature \cite{altenkirch2016quotient,awodey2012inductive,basoldhigher,sojakova2015higher,hottbook}, but a definition with a good metatheory remains to be given.
+Higher inductive types (HITs) generalize normal inductive types by allowing constructors for both points and paths, rather than just for the points.
+While an inductive type is freely generated from a signature, a higher inductive type is freely generated from a signature with some equations.
+Numerous examples and definitions of such types have already been given in the literature \cite{altenkirch2016quotient,awodey2012inductive,basoldhigher,sojakova2015higher,hottbook}, but a definition with a good metatheory is still lacking.
 As a step towards that goal, we simplify the definition given in \cite{basoldhigher} bringing it closer to the intuition and the intended meaning.
@@
 This is explained by a theorem which says that inductive types are initial algebras for a functor \cite{dybjer1994inductive,dybjer2003induction} and another one about how these algebras are obtained \cite{adamek1974free}.
-For higher inductive types one would expect a similar result which explains philosophically what they are.
-The only difference between higher inductive types and normal inductive types is that during the construction of higher inductive types several identifications are made which are described by the path constructors.
+For higher inductive types one would expect a similar result which explains how they are constructed.
+However, since equations are also allowed in the definition of a higher inductive type, one would expect that during the construction identifications are made by gluing paths.
 
-The goal of this paper is to show that the higher inductive types defined in \cite{basoldhigher} can be generated from the interval, homotopy pushouts and colimits, and that formally justifies this intuition on higher inductive types.
+The goal of this paper is to formally justify this idea by showing that the higher inductive types defined in \cite{basoldhigher} can be generated from the interval, homotopy pushout and colimit.
 More concretely, we will prove the following theorem.
@@
 \label{thm:three-hit}
-In Martin-L\"of Type Theory extended with an interval object, homotopy pushouts and colimits, we can define for each higher inductive type as in \cite{basoldhigher} a tye with the same introduction, elimination and computation rules.
+In Martin-L\"of Type Theory extended with an interval object, homotopy pushouts and colimits, we can define for each higher inductive type from \cite{basoldhigher} a type with the same introduction, elimination and computation rules.
 \end{theorem}
 Also, this generalizes the results in \cite{doorn2016constructing,kraus2014general,kraus2016constructions} where the result is showed for truncations.
-With this result the metatheory of higher inductive types could be simplified significantly, because rather than a general class, one only needs to check metatheoretical properties for three types.
+With this result the metatheory of higher inductive types could be simplified significantly, because rather than a general class, one only needs to check metatheoretical properties for three HITs.
 
-In Section \ref{sec:prelims} we shall discuss some of the required notions for this paper.
-More concretely, we recall the syntax of higher inductive types, and as examples we give the interval, the homotopy pushout, and colimit.
+In Section \ref{sec:prelims} we shall recall some of the required material for this paper.
+More concretely, we give the syntax of higher inductive types, and using that we define the interval, homotopy pushout, and colimit.
 Next we define the approximating sequence of a higher inductive type in Section \ref{sec:approximator}, and in Section \ref{sec:rules} we show that the colimit of this sequence satisfies the rules of the given HIT.
@@
 We will write $F \> f$ to denote the application of a polynomial $F$ to a map $f$.
-Also, given $f : \prod (x : T), Y \> x$, one can define $\bar{F} \> f : \prod (x : H \> T), \bar{H} \> Y \> x$.
+Also, given a dependent function $f : \prod (x : T), Y \> x$, one can define $\bar{F} \> f : \prod (x : H \> T), \bar{H} \> Y \> x$.
 Precise definitions of these are given in \cite{basoldhigher}.
@@
 \begin{definition}
-Given are functions $c : A \> T \rightarrow T$.
+Given is a function $c : A \> T \rightarrow T$.
 Then we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F \> T \Vdash t : G \> T$ can be derived using the following rules.
@@
 \begin{definition}
-Given are a constructor $c : A \> H \rightarrow H$, a type family $Y : H \rightarrow \Type$, and a term
-\[
- \vdash f : \prod (x: A \> H), \bar{A} \> Y \> x \rightarrow  Y(c \> x).
-\]
+Given is a constructor $c : A \> H \rightarrow H$, a type family $Y : H \rightarrow \Type$, and a term $f : \prod (x: A \> H), \bar{A} \> Y \> x \rightarrow  Y(c \> x)$.
 For a constructor term $F \> H \Vdash r : G \> H$ we define the \emph{lift $\dak{r}$ of $r$} with type 
-\[
+$
 x : F \> H, h_x : \bar{F} \> Y \> x \vdash \dak{r} : \bar{G} \> Y \> r
-\]
+$
 by induction in $r$ as follows.
@@
 The introduction rules for $H$ as given in Definition \ref{def:hit} are
+\begin{minipage}{0.6\textwidth}
 \[
-c : A \> H \rightarrow H,
+c : A \> H \rightarrow H
 \]
+\end{minipage}
+\begin{minipage}{0.4\textwidth}
 \[
@@
 \]
+\end{minipage}
 We also have an elimination rule for which we use the lifting of constructor terms.
@@
 
-Let us finish by defining some examples of higher inductive types which will be used a lot in this paper.
+Let us now give some examples of higher inductive types which will be crucial in this paper.
 The first one would be the interval
@@
 Then we can define maps $\delta_0, \delta_1 : \one \rightarrow$ sending $\pt$ to 0 and 1 respectively.
-Also, we define $\delta : \one + \one \rightarrow I^1$ by $\delta_0 + \delta_1$.
+Also, we define the boundary inclusion $\delta : \one + \one \rightarrow I^1$ by $\delta_0 + \delta_1$.
 
@@
 Note the similarities with the construction of the pushout.
-Also, we can define the homotopy colimit as a higher inductive type in much the same way.
+Lastly, we can define the homotopy colimit as a higher inductive type in much the same way.
 \lstset{language=Coq}
@@
 The first approximation just has a constructor $0$, and after that we add a constructor for $S \> 0$ to obtain the second approximation.
-In the third approximation, which we call $F \> 3$, we found inhabitants $0$, $S \> 0$, and $S(S \> 0)$, and now we can make the first identification.
+In the third approximation, which we call $F' \> 3$, we found inhabitants $0$, $S \> 0$, and $S(S \> 0)$, and now we can make the first identification.
 To do so, we take the following homotopy pushout
@@
 	\one + \one \ar[d]_{0 + S(S \> 0)} \ar[r]^-{\delta} & I^1 \ar[d]\\
-	F \> 3\ar[r] & P \> 3
+	F' \> 3\ar[r] & F \> 3
 }
 \]
-to obtain the actual third approximation $P \> 3$, and we continue our construction with that one.
+to obtain the actual third approximation $F \> 3$, and we continue our construction with that one.
 Note that to glue during the $n$th step, we need refer to elements from the $(n-2)$th step.
@@
 By extending the syntax, one can also think of examples where one needs to go back an arbitrary amount of steps.
-For that, we consider the following example.
+This happens in the following example.
 \lstset{language=Coq}
 \begin{lstlisting}
-Inductive $\mathbb{N}_2$ :=
-| $0$ : $\mathbb{N}_2$
-| $S$ : $\mathbb{N}_2 \rightarrow \mathbb{N}_2$
-| $p$ : $\prod (n : \mathbb{N}), S^n \> 0 = 0$
+Inductive $H$ :=
+| $c$ : $H$
+| $f$ : $H \rightarrow H$
+| $p$ : $\prod (n : \mathbb{N}), f^n \> 0 = 0$
 \end{lstlisting}
-This example might seem like it is allowed in the syntax, but it is not.
-The term $S^n$ is defined as a polymorphic function which needs the type as argument, and that is not allowed with constructor terms.
-In this extension the construction will be more complicated, and the construction is not predicative, so this will not be considered in this paper.
+This example might seem like it is permitted by the syntax, but it is not.
+The function $f^n$ is defined as a polymorphic map, and using it requires the type $H$ as an argument.
+In constructor terms one cannot use the type, and hence this definition is not allowed
+An extension with such types will make the construction more complicated, and thus they will not be considered in this paper.
 
-Let us make this idea formal, and for that we start with a higher inductive type which is given as follows.
+Let us make this idea formal, and for that we start with a higher inductive type given as follows.
 \lstset{language=Coq}
@@
 Inductive $H_{\Con}^n$ $(P : \Type)$:=
-| $\term$ : $P + H_{\rec} \> P + \ldots + H_{\rec}^n \> P \rightarrow H_{\Con} \> P$
+| $\term$ : $P + H_{\rec} \> P + \ldots + H_{\rec}^n \> P \rightarrow H_{\Con}^n \> P$
 \end{lstlisting}
@@
 During the construction one also needs to pay attention to coherency.
-For example, in $P$ we have $c_{\nonrec}$, so in $H_{\Approx} \> P$ we might have duplicates of some terms.
+For example, in $P$ we have terms using $c_{\rec}$ at most $k$ times, so in $H_{\Approx} \> P$ we have duplicates of terms using $c_{\rec}$ less than $k$ times..
 By tweaking the pushout a little bit, one can easily solve these coherency problems.
@@
 Let a higher inductive type $H$ be given as before, and let the type $H_{\Con}$ be defined as before.
-Then we define the \emph{approximator} $H_{\Approx}$, which has a parameters $P, Q$ and $f : Q \rightarrow P$, of $H$ the following pushout
+Then we define the \emph{approximator} $H_{\Approx}$, which has a parameters $P, Q$ and $f : H_{\Con} \> Q \rightarrow P$, of $H$ the following pushout
 \[
@@
 {
-	((\one + \one) \times B_i \> P) + H_{\Con} \> Q \ar[d]_{\overline{t_i} + \overline{r_i} + H_{\Con} \> f} \ar[rr]^-{\delta + \inl} & & (I^1 \times B_i \> P) + H_{\Approx} Q  \ar[d]^{\inr}\\
-	H_{\Con} \> P \ar[rr]_{\inl} & & H_{\Approx} \> P
+	((\one + \one) \times B_i \> P) + H_{\Con} \> Q \ar[d]_{\overline{t_i} + \overline{r_i} + H_{\Con}(f \circ \inn_1)} \ar[rr]^-{\delta + f} & & (I^1 \times B_i \> P) + P  \ar[d]^{\inr}\\
+	H_{\Con} \> P \ar[rr]_{\inl} & & H_{\Approx} \> P \> Q \> f
 }
@@
 Note that this can be written as the homotopy pushout.
+Often we will suppress the maps $f$ from the notation.
 \end{definition}
@@
 F \> 1 &= H_{\Approx} \> (F \> 0) \> \zero \> (\zero\frec (F \> 0))\\
-F(n+2) &= H_{\Approx} \> (F(n+1)) \> (F \> n) \> (f \> n) \qedhere
+F(n+2) &= H_{\Approx} \> (F(n+1)) \> (F \> n) \> \inl \qedhere
 \end{align*}
@@
 {
-	P \ar[r] & H_{\Con} \> P \ar[r] & H_{\Approx} P.
+	P \ar[r] & (I^1 \times B_i \> P) + P \ar[r] & H_{\Approx} P.
 }
@@
 	H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> (f \> n)} \ar[r]^-{\inl}
-		& H_{\Approx}(F \> n) \ar[d]^{f(n+1)}\\
+		& F(n+1) \ar[d]^{f(n+1)}\\
 	H_{\Con}(F(n+1)) \ar[r]_-{\inl}
-		& H_{\Approx}(F(n+1))
+		& H_{\Approx} \> (F(n+1)) \> (F \> n)
 }
@@
 Note that $H_{\Approx}(F(n+1)) = F(n+2)$ and $H_{\Approx}(F \> n) = F(n+1)$.
-Hence, this diagram commutes, because of the pushout.
+Hence, this diagram commutes, because of the pushout we used to define $H_{\Approx}$.
 
 Next we need to define the introduction rules for the paths.
-Let us start by making a map $\sum_{i = 1}^m I^1 \times B_i \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
+Let us start by making maps $I^1 \times B_i \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
 Since homotopy colimits commute with polynomials, it suffices to make a map $\hocolim \> (I^1 \times B_i \> F) \> (I^1 \> B_i \> f)  \rightarrow \hocolim \> F \> f$.
@@
 {
-	I^1 \times B_i \> (F \> n) \ar[rr]^-{\inr} & & F(n+1) \ar[rr]^-{\inc(n+1)} & & \hocolim \> F \> f.
+	I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} & I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} + F \> n \ar[r]^-{\inr}& F(n+1) \ar[rr]^-{\inc(n+1)} & & \hocolim \> F \> f.
 }
@@
 {
-	I^1 \times B_i \> (F \> n) \ar[rr]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n)} & & F(n+1) \ar[d]^{f(n+1)}\\
-	I^1 \times B_i \> (F(n+1)) \ar[rr]^-{\inr} & & F(n+2)
+	I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} \ar[d]_{I^1 \times B_i \> (f \> n)} & I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} & F(n+1) \ar[d]^{f(n+1)}\\
+	I^1 \times B_i \> (F(n+1)) \ar[r]_-{\inn_1} & I^1 \times B_i \> (F(n+1)) + F(n+1) \ar[r]_-{\inr}& F(n+2) 
 }
 \]
-This can be proven by induction on $B_i$, and using the definition of $I^1 \times B_i \> (f \> n)$.
-We can use the path $\refl$.
-All in all, we get a map $p_i : \hocolim \> (I^1 \times B_i \> F) \> (I^1 \times B_i \> f) \rightarrow \hocolim \> F \> f$
+Note that the left diagram commutes.
+For the right diagram we can unpack the definition of $f(n+1)$.
+\[
+\xymatrix
+{
+	I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} & F(n+1) \ar[d]^{f(n+1)} \ar[dl]^{\inn_2}\\
+	I^1 \times B_i \> (F(n+1)) + F(n+1) \ar[r]_-{\inr}& F(n+2) 
+}
+\]
+\textbf{Another coherency which should be added.}
 
@@
 \]
-In order to make a map $\prod (x : \hocolim \> F \> f), Y \> x$, we use the induction principle of $\hocolim \> F \> f$, and for that we need to make maps $\prod (x : F \> n), Y(\inc \> n \> x)$.
+In order to make a map $\prod (x : \hocolim \> F \> f), Y \> x$, we use the induction principle of $\hocolim \> F \> f$, and for that we first need to make maps $\prod (x : F \> n), Y(\inc \> n \> x)$.
 
-First we need to make a map $\prod (x : F \> 0), Y(\inc \> 0 \> x)$.
+We start by making a map $\prod (x : F \> 0), Y(\inc \> 0 \> x)$.
 Recall that $F \> 0$ was defined to be $H_{\nonrec}$ which only has a constructor $c'_{\nonrec} : A_{\nonrec} \rightarrow H_{\nonrec}$.
 So, let us assume that we have $a : A_{\nonrec}$.
-Since $c_{\nonrec} \> a = \inc \> 0 \> (c\_{\nonrec} a)$, it suffices to find an inhabitant of $Y(c_{\nonrec} \> a)$, and for that we take $c_{Y, \nonrec} \> a$.
+Since $c_{\nonrec} \> a = \inc \> 0 \> (c_{\nonrec} \> a)$, it suffices to find an inhabitant of $Y(c_{\nonrec} \> a)$, and for that we take $c_{Y, \nonrec} \> a$.
 Hence, we get a map $\prod (x : F \> 0), Y(\inc \> 0 \> x)$.
 
-Now suppose that we have a map $\prod (x : F \> n), Y(\inc \> n \> x)$, and our goal is to make a map $\prod  (x : F(n+1)), Y(\inc \> (n+1) x)$.
+Now suppose that we have a map $\prod (x : F \> n), Y(\inc \> n \> x)$, and our goal is to make a map $\prod  (x : F(n+1)), Y(\inc \> (n+1) \> x)$.
 In order to do so, we will first look at how to extend it to a map $\prod (x : H_{\Con} (F \> n)), Y(\inc \> (n+1) \> (\inl \> x))$.
@@
 Let us do this in the general case.
-Suppose that we have $g : P \rightarrow \hocolim \> F \> f$, and that we have $h : \prod (x : P), Y(g \> x)$.
-Our goal is to extended the map into a $h' : \prod (x : H_{\rec} P), Y(c_{Y, \rec} \> x)$, and for that we use $H_{\rec}$ induction.
+Suppose, we have a map $g : P \rightarrow \hocolim \> F \> f$, and that we already constructed $h : \prod (x : P), Y(g \> x)$.
+Our goal is to extended the map into a $h' : \prod (x : H_{\rec} P), Y(c_{Y, \rec} \> x)$, and for that we use $H_{\rec}$-induction.
 Note that for each $c'_{\rec} \> x$ with $x : A_{\rec} \> P$ we have the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$, and thus we have a type family on $H_{\rec}$.

### 2017-03-03 Paper/Paper.tex
Further work on proof, some small improvements

@@
 
+\newcommand{\Boperator}[1]{\mathrm{\mathbf{#1}}}
 \newcommand{\comment}[1]{-- #1 --}
 \newcommand{\remove}[1]{}
-\newcommand{\inn}{{\rm in}}
+\newcommand{\inn}{\Boperator{in}}
 
 \newcommand{\conc}[0]{\bullet}
+\newcommand{\comp}[0]{\circ \,}
 
@@
 \newcommand{\ap}[0]{\operatorname{ap}}
-\newcommand{\apd}[0]{\operatorname{apd}}
+\newcommand{\apd}[0]{\operatorname{apD}}
 
@@
 
-\newcommand{\refl}[0]{\operatorname{\textbf{refl}}}
-\newcommand{\hpushout}[0]{\operatorname{\textbf{hpushout}}}
-\newcommand{\hocolim}[0]{\operatorname{\textbf{hocolim}}}
-\newcommand{\seg}[0]{\operatorname{\textbf{seg}}}
-\newcommand{\inl}[0]{\operatorname{\textbf{inl}}}
-\newcommand{\inr}[0]{\operatorname{\textbf{inr}}}
-\newcommand{\glue}[0]{\operatorname{\textbf{glue}}}
-\newcommand{\inc}[0]{\operatorname{\textbf{inc}}}
-\newcommand{\com}[0]{\operatorname{\textbf{com}}}
+\newcommand{\idmap}[0]{\Boperator{Id}}
+\newcommand{\refl}[0]{\Boperator{refl}}
+\newcommand{\hpushout}[0]{\Boperator{hpushout}}
+\newcommand{\hocolim}[0]{\Boperator{hocolim}}
+\newcommand{\seg}[0]{\Boperator{seg}}
+\newcommand{\inl}[0]{\Boperator{inl}}
+\newcommand{\inr}[0]{\Boperator{inr}}
+\newcommand{\glue}[0]{\Boperator{glue}}
+\newcommand{\inc}[0]{\Boperator{inc}}
+\newcommand{\com}[0]{\Boperator{com}}
 \newcommand{\Type}[0]{\operatorname{\textsc{Type}}}
@@
 \begin{equation*}
-H\frec \> (c_i \> t) \equiv f_i \> t \> (\bar{A} \> H\frec \> t),
+H\frec \> (c \> t) \equiv f \> t \> (\bar{A} \> H\frec \> t),
 \end{equation*}
@@
 \begin{equation*}
-\apd \> H\frec \> (p_j \> a) \equiv q_j \> a \> (\bar{B}_i \> H\frec \> a).
+\apd \> H\frec \> (p_i \> a) \equiv q_i \> a \> (\bar{B}_i \> H\frec \> a).
 \end{equation*}
@@
 \end{lstlisting}
-Note the similarities with the construction of the pushout.
+Note the similarities with the construction of the pushout \cite{mac2013categories}.
 Lastly, we can define the homotopy colimit as a higher inductive type in much the same way.
@@
 During the construction one also needs to pay attention to coherency.
-For example, in $P$ we have terms using $c_{\rec}$ at most $k$ times, so in $H_{\Approx} \> P$ we have duplicates of terms using $c_{\rec}$ less than $k$ times..
-By tweaking the pushout a little bit, one can easily solve these coherency problems.
+For example, in $P$ we have terms using $c_{\rec}$ at most $k$ times, so in $H_{\Approx} \> P$ we have duplicates of terms using $c_{\rec}$ less than $k$ times.
+There will be several coherency problems during the proof, so the pushout will seem rather intimidating at first.
 
@@
 Let a higher inductive type $H$ be given as before, and let the type $H_{\Con}$ be defined as before.
-Then we define the \emph{approximator} $H_{\Approx}$, which has a parameters $P, Q$ and $f : H_{\Con} \> Q \rightarrow P$, of $H$ the following pushout
+Given are parameters $P$ and $Q$ with amps $i_l : H_{\Con} \> Q \rightarrow P$ and $i_r : I^1 \times B_i \> Q + Q \rightarrow P$.
+Let us define the following maps.
+\begin{align*}
+\widetilde{i_l} &= i_l \comp \inn_1\\
+g_1 &: ((\one + \one) \times B_i \> P) + H_{\Con} \> Q  + (I^1 \times B_i \> Q + Q)\rightarrow (I^1 \times B_i \> P) + P\\
+g_1 &= (\inn_1 \comp \delta \times \idmap) + (\inn_2 \comp i_l) + (\inn_2 \comp i_r \circ \inn_1)\\
+g_2 &: ((\one + \one) \times B_i \> P) + H_{\Con} \> Q + (I^1 \times B_i \> Q + Q) \rightarrow H_{\Con} \> P + (I^1 \times B_i \> P + P)\\
+g_2 &= (\inn_1 \comp \overline{t_i} + \overline{r_i})+ (\inn_1 \comp H_{\Con} \> \widetilde{i_l}) + (\inn_2 \comp (I^1 \times B_i \> \widetilde{i_l}))
+\end{align*}
+Then we define the \emph{approximator} $H_{\Approx}$ of $H$ the following pushout.
 \[
@@
 {
-	((\one + \one) \times B_i \> P) + H_{\Con} \> Q \ar[d]_{\overline{t_i} + \overline{r_i} + H_{\Con}(f \circ \inn_1)} \ar[rr]^-{\delta + f} & & (I^1 \times B_i \> P) + P  \ar[d]^{\inr}\\
-	H_{\Con} \> P \ar[rr]_{\inl} & & H_{\Approx} \> P \> Q \> f
+	((\one + \one) \times B_i \> P) + H_{\Con} \> Q + (I^1 \times B_i \> Q) 
+	\ar[d]_{g_2} 
+	\ar[r]^-{g_1}
+	& (I^1 \times B_i \> P) + P  
+	\ar[d]^-{\inr}\\
+	H_{\Con} \> P + (I^1 \times B_i \> P)  
+	\ar[r]_-{\inl} 
+	& H_{\Approx} \> P \> Q \> i_l \> i_r
 }
@@
 Note that this can be written as the homotopy pushout.
-Often we will suppress the maps $f$ from the notation.
+Often we will suppress the maps from the notation.
 \end{definition}
+
+The types $Q$ and $P$ represent $F(n-2)$ and $F(n-1)$ respectively, and the maps $i_l$ and $i_r$ are the inclusion maps into $F(n-1)$.
+The new type is extended with constructors and paths given by $\inl \comp \inn_1$ and $\inr \comp \inn_1$ respectively.
+Also, there are coherency conditions added and these are given by the second and third component of the left upper corner.
+Their use will become clear in the Section \ref{sec:rules} when we show the introduction rules.
+Now we can define the approximating sequence.
 
@@
 F \> 0 &= H_{\nonrec},\\
-F \> 1 &= H_{\Approx} \> (F \> 0) \> \zero \> (\zero\frec (F \> 0))\\
-F(n+2) &= H_{\Approx} \> (F(n+1)) \> (F \> n) \> \inl \qedhere
+F \> 1 &= H_{\Approx} \> (F \> 0) \> \zero \> (\zero\frec (F \> 0)) \> (\zero\frec (F \> 0))\\
+F(n+2) &= H_{\Approx} \> (F(n+1)) \> (F \> n) \> \inl \> \inr \qedhere
 \end{align*}
@@
 \label{lem:colim_commute_poly}
-The types $A \> (\hocolim \> F \> f)$ and $\hocolim \> (A \circ F) \> (A \> f)$ are isomorphic for all polynomials $A$.
+The types $A \> (\hocolim \> F \> f)$ and $\hocolim \> (A \comp F) \> (A \> f)$ are isomorphic for all polynomials $A$.
 \end{lemma}
@@
 \begin{proof}
-
+If $A$ is constant then it follows from Lemma \ref{lem:colimcon}.
+For the identity it is trivial, and for sums and products, it follows from Lemmata \ref{lem:colimsum} and \ref{lem:colimprod} respectively. 
 \end{proof}
 
-Now we will construct the map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$, and by Lemma \ref{lem:colim_commute_poly} it suffices to make a map $\hocolim \> (A_{\rec} \circ F) \> (A \> f) \rightarrow \hocolim \> F \> f$.
+Now we will construct the map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$, and by Lemma \ref{lem:colim_commute_poly} it suffices to make a map $\hocolim \> (A_{\rec} \comp F) \> (A \> f) \rightarrow \hocolim \> F \> f$.
 For this we use the recursion rule of $\hocolim$, and we start with the following string of maps
@@
 		A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} 
-		& H_{\rec}(F \> n) \ar[rr]^{\term \circ \iota_2} &
+		& H_{\rec}(F \> n) \ar[rr]^{\term \comp \iota_2} &
 		& H_{\Con}(F \> n) \ar[r]^-{\inl}
@@
 	A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} \ar[d]_{A_{\rec}(f \> n)} 
-		& H_{\rec}(F \> n) \ar[rr]^{\term \circ \iota_2} \ar[d]_{H_{\rec}(f \> n)} &
+		& H_{\rec}(F \> n) \ar[rr]^{\term \comp \iota_2} \ar[d]_{H_{\rec}(f \> n)} &
 		& H_{\Con}(F \> n) \ar[d]_{H_{\Con}(f \> n)}\\
 	A_{\rec}(F(n+1)) \ar[r]_-{c_{\rec}'} 
-		& H_{\rec}(F(n+1)) \ar[rr]_{\term \circ \iota_2} &
+		& H_{\rec}(F(n+1)) \ar[rr]_{\term \comp \iota_2} &
 		& H_{\Con}(F(n+1))
@@
 {
-	I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} & I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} + F \> n \ar[r]^-{\inr}& F(n+1) \ar[rr]^-{\inc(n+1)} & & \hocolim \> F \> f.
+	I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} & I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr}& F(n+1) \ar[rr]^-{\inc(n+1)} & & \hocolim \> F \> f.
 }
@@
 \]
-\textbf{Another coherency which should be added.}
+On the first coordinate it commutes by definition and on the second it commutes by how $F(n+2)$ was defined.
 
-Now we have the following diagram
+Now we check that the defined paths have the right endpoints, and for that we look at the following diagram.
 \[
@@
 \subsection{Elimination Rule}
-For the next step we define the right eliminator for $\hocolim \> F \> f$. 
-For this we suppose that we have
+For the next step we define the right eliminator for $\hocolim \> F \> f$, so suppose that we are given
 \[
-Y : \hocolim \> F \> f \rightarrow \Type
+Y : \hocolim \> F \> f \rightarrow \Type,
 \]
 \[
-c_{Y, \nonrec} : \prod (a : A_{\nonrec}), Y(c_{\nonrec})
+c_{Y, \nonrec} : \prod (a : A_{\nonrec}), Y(c_{\nonrec} \> a),
 \]
 \[
-c_{Y, \rec} : \prod (x : A_{\rec} \> \hocolim \> F \> f), \overline{A_{\rec}} \> Y \> x \rightarrow Y(c_{\rec} \> x)
+c_{Y, \rec} : \prod (x : A_{\rec} \> \hocolim \> F \> f), \overline{A_{\rec}} \> Y \> x \rightarrow Y(c_{\rec} \> x),
 \]
 \[
-q_{Y, i} : \prod (x : B_i \> H)(h_x : \overline{B_i} \> Y \> x), \hatt_i =_{p_j \, x} \hatr_j
+q_{Y, i} : \prod (x : B_i \> H)(h_x : \overline{B_i} \> Y \> x), \hatt_i =_{p_j \, x} \hatr_j.
 \]
-In order to make a map $\prod (x : \hocolim \> F \> f), Y \> x$, we use the induction principle of $\hocolim \> F \> f$, and for that we first need to make maps $\prod (x : F \> n), Y(\inc \> n \> x)$.
+In order to make a map $h : \prod (x : \hocolim \> F \> f), Y \> x$, we use the induction principle of $\hocolim \> F \> f$, and for that we first need to make maps $h \> n : \prod (x : F \> n), Y(\inc \> n \> x)$ for $n : \mathbb{N}$.
 
-We start by making a map $\prod (x : F \> 0), Y(\inc \> 0 \> x)$.
+We start by making a map $h \> 0 : \prod (x : F \> 0), Y(\inc \> 0 \> x)$.
 Recall that $F \> 0$ was defined to be $H_{\nonrec}$ which only has a constructor $c'_{\nonrec} : A_{\nonrec} \rightarrow H_{\nonrec}$.
 So, let us assume that we have $a : A_{\nonrec}$.
-Since $c_{\nonrec} \> a = \inc \> 0 \> (c_{\nonrec} \> a)$, it suffices to find an inhabitant of $Y(c_{\nonrec} \> a)$, and for that we take $c_{Y, \nonrec} \> a$.
-Hence, we get a map $\prod (x : F \> 0), Y(\inc \> 0 \> x)$.
+Since $c_{\nonrec} \> a = \inc \> 0 \> (c_{\nonrec}' \> a)$, it suffices to find an inhabitant of $Y(c_{\nonrec} \> a)$, and for that we take $c_{Y, \nonrec} \> a$.
+Hence, we get a map $h \> 0$.
 
-Now suppose that we have a map $\prod (x : F \> n), Y(\inc \> n \> x)$, and our goal is to make a map $\prod  (x : F(n+1)), Y(\inc \> (n+1) \> x)$.
-In order to do so, we will first look at how to extend it to a map $\prod (x : H_{\Con} (F \> n)), Y(\inc \> (n+1) \> (\inl \> x))$.
+Now suppose that we have a map $h \> n : \prod (x : F \> n), Y(\inc \> n \> x)$, and our goal is to make a map $h(n+1) : \prod  (x : F(n+1)), Y(\inc \> (n+1) \> x)$.
+In order to do so, we will first look at how to extend $h \> n$ to a map $\prod (x : H_{\Con} (F \> n)), Y(\inc \> (n+1) \> (\inl \> x))$.
 
 Let us do this in the general case.
-Suppose, we have a map $g : P \rightarrow \hocolim \> F \> f$, and that we already constructed $h : \prod (x : P), Y(g \> x)$.
-Our goal is to extended the map into a $h' : \prod (x : H_{\rec} P), Y(c_{Y, \rec} \> x)$, and for that we use $H_{\rec}$-induction.
+Suppose, we have a map $g : P \rightarrow \hocolim \> F \> f$, and that we already constructed $\varphi : \prod (x : P), Y(g \> x)$.
+Our goal is to extended the map into a $\varphi' : \prod (x : H_{\rec} P), Y(c_{Y, \rec} \> x)$, and for that we use $H_{\rec}$-induction.
 Note that for each $c'_{\rec} \> x$ with $x : A_{\rec} \> P$ we have the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$, and thus we have a type family on $H_{\rec}$.
 Now let $x : A_{\rec} \> P$ and $y : \overline{A_{\rec}} \> Y \> x$ be given.
-Then we need to give an element of the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$ for which we take
-\[
-c_{Y,\rec} \> (A_{\rec} \> g \> x) \> y
-\]
+Then we need to give an element of the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$ for which we take $c_{Y,\rec} \> (A_{\rec} \> g \> x) \> y$.
+
 Now we can also extend the map to $H_{\Con}^n \> P$, because we can define this map on each component.
-On the component $P$ it is just $h$, and on the other components we define it via extension.
+On the component $P$ it is just $\varphi$, and on the other components we define it via extension.
 
 Next we need to extend the map to $H_{\Approx} \> P \> Q$.
-For that we need to make a map $h' : \prod (x : I^1 \times B_i \> P), Y()$
-
-Let $(t, x) : I^1 \times B_i \> P$, and now we use $I^1$ induction.
-If $t = 0$, we map it to $\hatt_i (x)$, and for $t = 1$ we map it to $\hatr_i (x)$.
+This is done by the universal mapping property of the pushout, and that requires two steps.
+First, we need to extend the map to $I^1 \times B_i \> P$, and second we need to check that the diagram given by the pushout commutes.
+For that we start with $(y, x) : I^1 \times B_i \> P$, and we use $I^1$-induction.
+If $y = 0$, we map it to $\hatt_i (x)$, and for $y = 1$ we map it to $\hatr_i (x)$.
 Now the path $q_{Y, i}$ gives the image of $\seg$, and that finishes the induction.
 
-For the commutativity of the diagram note that by definition the dependent map from $H_{\Con} \> P$ to $Y$ sends the constructor term $t_i$ to the lift $\hatt_i$.
-This is because the map replaces each $c_{\rec}$ by $c_{Y, \rec}$ which is precisely how the lift was constructed.
+Since $H_{\Approx}$ is a pushout, we also need to show that a diagram commutes.
+The left upper corner is defined to be a sum, and thus it suffices to check it for each of the components.
+For the first, $H_{\Con} \> P$, note that the map $\varphi'$ to $Y$ defined by extension, sends the constructor term $t_i$ to its lift $\hatt_i$, since it replaces each $c_{\rec}$ by $c_{Y, \rec}$.
+On $I^1 \times B_i \> P$ the points are mapped to the lifts $\hatt_i$ as well, and thus the diagram commutes on this component.
 
-Next we do it for the coherency.
+Next we do it for the coherency condition on the points where we look at the following corner
+\[
+\xymatrix
+{
+	H_{\Con}(F \> n) \ar[r]^{\inl} \ar[d]_{H_{\Con} (f \> n)} & F(n+1)\\
+	H_{\Con} (F(n+1))
+}
+\]
+Elements of $H_{\Con}(F \> n)$ are terms built from $c_{\rec}$ on $F \> n$.
+In order to show that it commutes for all inhabitants of $H_{\Con}(F \> n)$, we use induction on the depth.
+If the inhabitant is of the form $\inn_1 \> x$ with $x : F \> n$, then it gets mapped to the first component of $H_{\Con} (F(n+1))$ and $F(n+1)$.
+In both cases it is just mapped with $h \> (n+1)$ and thus they are equal.
 
-Induction on the level (so, ultimately some kind of simultaneous induction?)
+To show that it holds for the other inhabitants as well, we take a look at $c_{\rec}' \> x$.
+By $\inl$ it gets mapped $\inl (c_{\rec}' \> x)$.
+Since $h(n+1)$ is defined as the pushout map, it maps $\inl (c_{\rec}' \> x)$ to $h \> (n+1) \> (c_{\rec}' \> x) \equiv c_{Y, \rec}(h \> n \> x)$.
+The map $H_{\Con} (f \> n)$ sends $c_{\rec}' \> x$ to $c_{\rec}' (f \> n \> x)$, and the dependent map $h$ sends it to $c_{Y, \rec}(h \> (n+1) \> (f \> x))$.
+Using the definition of the pushout map, this is equal to $c_{Y, \rec}(h \> n \> x)$
+Hence, this diagram commutes, and thus the first coherency is fine.
 
-Then induction on the depth.
-
-Base case: just induction assumption.
-
-Step case: then it can be worked out from the diagram.
+Now we also need to check the second coherency, and then we look at another corner
+\[
+\xymatrix
+{
+	I^1 \times B_i (F \> n) \ar[rr]^-{\inr \circ \inn_1} \ar[d]_{I^1 \times B_i \inl} & & F(n+1)\\
+	I^1 \times B_i(F(n+1)) 
+}
+\]
+Let $(y, x) : I^1 \times B_i (F \> n)$.
+Note that 
+\[
+h \> (n+1) \> (\inr(\inn_1 (y, x))) = h \> n \> (\inn_1 (y, x)) = \overline{q_{Y, i}}(y, h \> n \> x).
+\]
+\[
+h \> (n+1) \> (I^1 \times B_i \> \inl \> (y, x)) = h \> (n+1) \> (y, \inl x) = \overline{q_{Y, i}}(y, h \> (n+1) \> (\inl \> x)) = \overline{q_{Y, i}}(y, h \> n \> x).
+\]
+Hence, this coherency is fine as well.
 
@@
 Lastly, we show that this eliminator also satisfies the computation rules.
-First, we prove that for each $t : A_{\rec}(\hocolim \> F \> f)$ that $H\frec(c_{\rec} \> t) \equiv f_i \> t \> (\overline{A_{\rec}} H\frec t)$.
+First, we prove that for each $t : A_{\rec}(\hocolim \> F \> f)$ that $H\frec(c_{\rec} \> t) \equiv f_i \> t \> (\overline{A_{\rec}} \> H\frec \> t)$.
 Again we use that colimits commute with polynomials.
@@
 
-Now we show the computation rules for the paths.
+Now we show the computation rules for the paths, and in that case we have a parameter $a : B_i \> (\hocolim \> F \> f)$.
+By using that polynomials commute with homotopy colimits, we can again assume that we have $n : \mathbb{N}$ and $x : B_i(F \> n)$.
+\begin{equation*}
+\begin{split}
+\apd \> H\frec \> (p_i \> (\inc \> n \> x))
+&\equiv \apd \> H\frec \> (\apd \> (\inc (n+1)) \> (\inr \> x))\\
+&= \apd \> (H\frec \comp  \> \inc (n+1)) \> (\inr \> x))\\
+&\equiv q_i \> (H\frec x)
+\end{split}
+\end{equation*}
 
@@
 \label{sec:Lemmata}
+In this section we proof the required lemmata to show that colimits over $\mathbb{N}$ commute with polynomials.
+In category theory this result is standard \cite{mac2013categories}.
 
 \begin{lemma}
-$\hocolim \> (\lambda n . A) \> \operatorname{Id}$ is $A$.
+\label{lem:colimcon}
+$\hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id})$ is isomorphic to $A$.
 \end{lemma}
 
+\begin{proof}
+We define $f : A \rightarrow \hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id})$ to be $\inc \> 0$.
+Next we define $g : \hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id}) \rightarrow A$ by $\hocolim$ recursion.
+We send $\inc \> n \> a$ to $a$, and then the required diagrams commute by reflexivity.
+For the proof that it these maps are mutual inverses, we refer the reader to the accompanying Coq code \cite{CoqImpl}.
+\end{proof}
+
 \begin{lemma}
+\label{lem:colimsum}
 Colimits commute with coproducts.
@@
 \begin{lemma}
+\label{lem:colimprod}
 Colimits commute with products.

### 2017-03-06 Paper/Paper.tex
Small fixes in spelling and grammar

@@
 For higher inductive types one would expect a similar result which explains how they are constructed.
-However, since equations are also allowed in the definition of a higher inductive type, one would expect that during the construction identifications are made by gluing paths.
+However, since equations are also allowed in the specification of a higher inductive type, one would expect that during the construction identifications are made by gluing paths.
 
@@
 \label{thm:three-hit}
-In Martin-L\"of Type Theory extended with an interval object, homotopy pushouts and colimits, we can define for each higher inductive type from \cite{basoldhigher} a type with the same introduction, elimination and computation rules.
+In Martin-L\"of type theory extended with an interval object, homotopy pushouts and colimits, we can interpret each higher inductive type from \cite{basoldhigher}.
+This means that we can define a type with the same introduction, elimination and computation rules.
 \end{theorem}
@@
 \[
-F, G ::= B : \Type \ | \ X \ | \ F \times G \ | \ F + G
+F, G ::= B \ | \ X \ | \ F \times G \ | \ F + G
 \]
+where $B : \Type$.
 \end{definition}
@@
 \end{lstlisting}
-where $A$ and each $B_i$ are polynomials, and each $t_i$ and $r_i$ are constructor terms over $c$ of type $H$ with $x : B_i \> H$ as variable..
+where $A$ and each $B_i$ are polynomials, and each $t_i$ and $r_i$ are constructor terms over $c$ of type $H$ with $x : B_i \> H$ as variable.
 \end{definition}
@@
 The introduction rules for $H$ as given in Definition \ref{def:hit} are
-\begin{minipage}{0.6\textwidth}
+%\begin{minipage}{0.6\textwidth}
 \[
@@
 \]
-\end{minipage}
-\begin{minipage}{0.4\textwidth}
+%\end{minipage}
+%\begin{minipage}{0.4\textwidth}
 \[
@@
 \]
-\end{minipage}
+%\end{minipage}
 We also have an elimination rule for which we use the lifting of constructor terms.
@@
 \end{lstlisting}
-Note the similarities with the construction of the pushout \cite{mac2013categories}.
+Note the similarities with the definition of the pushout \cite{mac2013categories}.
 Lastly, we can define the homotopy colimit as a higher inductive type in much the same way.
@@
 For higher inductive types one would like to do a similar construction.
-The first difference is that instead of starting with nothing and adding each constructor at every step, we start with the nonrecursive constructors, and add recursive constructors at every step.
-Also, since extra equalities might be present in the higher inductive type, we need to make identifications during the construction.
-Rather than just adding points at every step, we also need to glue the right paths.
+The first difference is that instead of starting with $\zero$, we start with the nonrecursive constructors.
+Also, in this construction, the functor $F$ is applied at every step.
+Instead we will add terms built from the recursive constructors using previously constructed terms as arguments.
+Since extra equalities might be present in the higher inductive type, we need to make identifications during the construction.
+Rather than just adding points at every step, we also need to specified the right paths.
 
-To understand what should be done more precisely, let us consider an example.
+To understand more precisely what should be done, let us consider an example.
 \lstset{language=Coq}
@@
 
+Note that this type is actually a labeled sum.
+This is because $H_{\rec} \> P$ is isomorphic to $A_{\rec} \> P$, and thus this $H_{\Con}^n \> P$ is actually $P + A_{\rec} \> P + \ldots + A_{\rec}^n \> P$.
+Hence, we do not need inductive types in general for the construction, but we just need to have sums and products.
 If $n$ is clear from the context, then we shall not write it down.
@@
 
-Now we have enough to define the approximator.
+Now we have sufficient to define the approximator.
 During the construction one also needs to pay attention to coherency.
@@
 Also, there are coherency conditions added and these are given by the second and third component of the left upper corner.
-Their use will become clear in the Section \ref{sec:rules} when we show the introduction rules.
+Their use will become clear in the Section \ref{sec:rules} when we construct the right introduction rules.
 Now we can define the approximating sequence.
@@
 {
-	P \ar[r] & (I^1 \times B_i \> P) + P \ar[r] & H_{\Approx} P.
+	P \ar[r] & (I^1 \times B_i \> P) + P \ar[r] & H_{\Approx} \> P \> Q \> i_l \> i_r.
 }
@@
 \]
-where the map $H_{\rec}(F \> n) \rightarrow H_{\Con}(F \> n)$ is the inclusion and the map $H_{\Con}(F \> n) \rightarrow H_{\Approx}(F \> n)$ is the pushout map.
 Composing this map with $\inc$, gives maps $A_{\rec}(F \> n) \rightarrow \hocolim \> F \> f$ for all $n : \mathbb{N}$.
@@
 \]
-On the first coordinate it commutes by definition and on the second it commutes by how $F(n+2)$ was defined.
+On the second coordinate it commutes by definition and on the first it commutes by how $F(n+2)$ was defined.
 

### 2017-03-06 Paper/Paper.tex
Added proof that colimits commute with sums (in TeX and Coq code).

@@
 {
-	I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} \ar[d]_{I^1 \times B_i \> (f \> n)} & I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} & F(n+1) \ar[d]^{f(n+1)}\\
-	I^1 \times B_i \> (F(n+1)) \ar[r]_-{\inn_1} & I^1 \times B_i \> (F(n+1)) + F(n+1) \ar[r]_-{\inr}& F(n+2) 
+	I^1 \times B_i \> (F \> n) 
+		\ar[r]^-{\inn_1} \ar[d]_{I^1 \times B_i \> (f \> n)} 
+	& I^1 \times B_i \> (F \> n) + F \> n 
+		\ar[r]^-{\inr} 
+		%\ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} 
+	& F(n+1) 
+		\ar[d]^{f(n+1)}
+	\\
+	I^1 \times B_i \> (F(n+1)) 
+		\ar[r]_-{\inn_1} 
+	& I^1 \times B_i \> (F(n+1)) + F(n+1) 
+		\ar[r]_-{\inr}
+	& F(n+2) 
 }
 \]
-Note that the left diagram commutes.
-For the right diagram we can unpack the definition of $f(n+1)$.
+Note that this diagram commutes.
+For $x : I^1 \times B_i(F \> n)$ the path is $\glue(\inn_3 \> x)$.
+In particular, this means that $\apd \> p_i \> (\com \> n) \equiv \apd \> \inc(n+2) \> \glue(\inn_3 \> x)$
+%For the right diagram we can unpack the definition of $f(n+1)$.
+%\[
+%\xymatrix
+%{
+%	I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} & F(n+1) \ar[d]^{f(n+1)} \ar[dl]^{\inn_2}\\
+%	I^1 \times B_i \> (F(n+1)) + F(n+1) \ar[r]_-{\inr}& F(n+2) 
+%}
+%\]
+%On the second coordinate it commutes by definition and on the first it commutes by how $F(n+2)$ was defined.
+
+In order to check that the paths have the right endpoints, we first need to extend the $\overline{t_i} \> n : B_i(F \> n) \rightarrow H_{\Con} (F \> n)$ to a map $B_i(\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
+For $n : \mathbb{N}$ and $(y, x) : 2 \times B_i(F \> n)$, we take 
 \[
-\xymatrix
-{
-	I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} & F(n+1) \ar[d]^{f(n+1)} \ar[dl]^{\inn_2}\\
-	I^1 \times B_i \> (F(n+1)) + F(n+1) \ar[r]_-{\inr}& F(n+2) 
-}
+\inc \> (n+1) \> (\inl (g_1 (\inn_1 \> (y, x)))) \equiv \inc \> (n+1) \> (\inl(\overline{t_i} \> n \> (y, x))).
 \]
-On the second coordinate it commutes by definition and on the first it commutes by how $F(n+2)$ was defined.
+For the image of com we have the following propositional equalities.
+\begin{equation*}
+\begin{split}
+\inc &\> (n+2) \> (\inl(\overline{t_i} \> (n+1) \> (y, f \> n \> x)))
+\\
+&= \inc \> (n+2) \> ( f \> (n+1) \> (\inl(\overline{t_i} \> n \> (y, x))))
+\\
+&= \inc \> (n+1) \> (\inl(\overline{t_i} \> n \> (y, x))).
+\end{split}
+\end{equation*}
+The first equation holds by the coherency on the points, and the second by $\com$.
 
@@
 
-Remaining:
+We have
 \begin{equation*}
 \begin{split}
-\com_*(\ap \> (\inc \> n) \> \glue (\inl (0, x))) = \ap \> (\inc (n+1))) \>\glue (\inl (0, f \> n \> x))\\
-(\ap \> \overline{t_i} \> \com)^{-1} \conc \ap \> (\inc \> n) \> \glue (\inl (0, x)) \conc \ap \> p_i \> \com
+(\com \> n)_*(\ap \> (\inc \> n) \> \glue (\inl (0, x))) 
+&= (\ap \> \overline{t_i} \> (\com \> n))^{-1} \conc \ap \> (\inc \> n) \> \glue (\inl (0, x)) \conc \ap \> p_i \> (\com \> n)\\
+= \ap \> (\inc (n+1))) \>\glue (\inl (0, f \> n \> x))\\
 \end{split}
@@
 We send $\inc \> n \> a$ to $a$, and then the required diagrams commute by reflexivity.
-For the proof that it these maps are mutual inverses, we refer the reader to the accompanying Coq code \cite{CoqImpl}.
+The proof that these maps are mutual inverses is straightforward but tedious, so we refer the reader to the accompanying Coq code \cite{CoqImpl}.
 \end{proof}
@@
 \label{lem:colimsum}
-Colimits commute with coproducts.
+Colimits commute with coproducts, so $\hocolim \> ((G_1 + G_2) \circ F) \> ((G_1 + G_2) \> f)$ and $\hocolim \> (G_1 \circ F) \> (G_1 \> f) + \hocolim \> (G_2 \circ F) \> (gG2 \> f)$ are isomorphic.. 
 \end{lemma}
+
+\begin{proof}
+This one is not difficult either, so we will be brief and refer the reader to \cite{CoqImpl} for details.
+We start by making a map 
+\[
+\hocolim \> ((G_1 + G_2) \circ F) \> ((G_1 + G_2) \> f) \rightarrow \hocolim \> (G_1 \circ F) \> (G_1 \> f) + \hocolim \> (G_2 \circ F) \> (G_2 \> f).
+\]
+This map is defined by recursion over the colimit, so take any $n : \mathbb{N}$ and $x : F \> n$.
+Then the image of $\inc \> n \> (\inn_i \> x)$ is defined to be $\inn_i (\inc \> n \> x)$, and the image of $\com \> n \> (\inn_i \> x)$ is defined by
+$\ap \> \inn_i \> (\com \> (G1 \circ F) \> (G_1 \> f) \> n \> x)$.
+
+For the map in the other direction, we need to make 
+\[
+\hocolim \> (G_i \circ F) \> (G_i \> f) \rightarrow \hocolim \> ((G_1 + G_2) \circ F) \> ((G_1 + G_2) \> f).
+\]
+We send $\inc \> n \> x$ to $\inc \> n \> (\inn_i \> x)$ and $\com \> n \> x$ to $\com \> n \> (\inn_i \> x)$.
+\end{proof}
 

### 2017-03-07 Paper/Paper.tex
Further work in proving that colim commute with product

@@
 Let us start by making maps $I^1 \times B_i \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
-Since homotopy colimits commute with polynomials, it suffices to make a map $\hocolim \> (I^1 \times B_i \> F) \> (I^1 \> B_i \> f)  \rightarrow \hocolim \> F \> f$.
+Since homotopy colimits commute with polynomials, it suffices to make a map $\hocolim \> (I^1 \times B_i \> F) \> (I^1 \times B_i \> f)  \rightarrow \hocolim \> F \> f$.
 
@@
 
+\begin{proof}
+This is the most difficult one, because colimits only commute with products if there are exponentials.
+\end{proof}
+
 \section{Conclusion and Further Work}

### 2017-03-13 Paper/Paper.tex
Added reference (colims commute with sigma)
Improved code.

@@
 Philosophically, one sees an inductive type as a type `which is built step by step'.
-One starts with the nonrecursive constructors, and then at each step new terms are added by applying the recursive constructors to the previously built terms.
-This is explained by a theorem which says that inductive types are initial algebras for a functor \cite{dybjer1994inductive,dybjer2003induction} and another one about how these algebras are obtained \cite{adamek1974free}.
-For higher inductive types one would expect a similar result which explains how they are constructed.
-However, since equations are also allowed in the specification of a higher inductive type, one would expect that during the construction identifications are made by gluing paths.
+Starting with the nonrecursive constructors, new terms are made by applying recursive constructors to previously built terms.
+This is explained by the fact that inductive types are initial algebras for a functor \cite{dybjer1994inductive,dybjer2003induction} and that such algebras are obtained by fixed point iteration \cite{adamek1974free}.
+Following our intuition on higher inductive types, one would expect that they can be constructed in a similar fashion.
+However, since equations are also allowed in the specification, identifications need to be made during the construction.
 
@@
 In Martin-L\"of type theory extended with an interval object, homotopy pushouts and colimits, we can interpret each higher inductive type from \cite{basoldhigher}. 
-This means that we can define a type with the same introduction, elimination and computation rules.
+This means that for each HIT we can define a type with the same introduction, elimination and computation rules.
 \end{theorem}
@@
 
-Before giving the definition, let us think about how it should be given.
-By Ad\'amek's theorem, every inductive type can be given as a colimit.
-An inductive type $T$ is given by a polynomial functor $F$ and a constructor $c : F \> T \rightarrow T$, and then $T$ is the colimit of the sequence
+Before giving the definition, let us acquire inspiration by looking in more detail at how an inductive type is constructed.
+Such a type $T$ is defined by a constructor $c : F \> T \rightarrow T$ with $F$ polynomial.
+Equivalently, we can define the type with a signature which is a polynomial functor $F$, and then by Ad\'amek's theorem it is the following colimit.
 \[
@@
 
-For higher inductive types one would like to do a similar construction.
-The first difference is that instead of starting with $\zero$, we start with the nonrecursive constructors.
+One would like to construct higher inductive types in a similar fashion.
+The first difference is that instead of starting with $\zero$, we start with all the nonrecursive constructors.
 Also, in this construction, the functor $F$ is applied at every step.
@@
 Since extra equalities might be present in the higher inductive type, we need to make identifications during the construction.
-Rather than just adding points at every step, we also need to specified the right paths.
+Rather than just adding points at every step, we also need to glue the specified paths.
 
@@
 Note that to glue during the $n$th step, we need refer to elements from the $(n-2)$th step.
-So, in order to do the identification of the $n$th step, one needs to refer back to a previous approximation.
+So, in order to do the identification of the $n$th step, inhabitants from a previous approximation need to be used.
 
-Note that one always has to go back a fixed number of steps due to the usage of constructor terms.
-By extending the syntax, one can also think of examples where one needs to go back an arbitrary amount of steps.
+Due to the usage of constructor terms, one always has to go back a fixed number of steps.
+By extending the syntax, it might be needed to go back an arbitrary amount of steps.
 This happens in the following example.
@@
 \end{lstlisting}
-This example might seem like it is permitted by the syntax, but it is not.
+This example might seem like it is permitted by the syntax, but actually it is not.
 The function $f^n$ is defined as a polymorphic map, and using it requires the type $H$ as an argument.
@@
 Let a higher inductive type $H$ be given as before, and let the type $H_{\Con}$ be defined as before.
-Given are parameters $P$ and $Q$ with amps $i_l : H_{\Con} \> Q \rightarrow P$ and $i_r : I^1 \times B_i \> Q + Q \rightarrow P$.
+Given are parameters $P$ and $Q$ with maps $i_l : H_{\Con} \> Q \rightarrow P$ and $i_r : I^1 \times B_i \> Q + Q \rightarrow P$.
 Let us define the following maps.
@@
 
-Now we will construct the map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$, and by Lemma \ref{lem:colim_commute_poly} it suffices to make a map $\hocolim \> (A_{\rec} \comp F) \> (A \> f) \rightarrow \hocolim \> F \> f$.
+Now we will construct the map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$, and by Lemma \ref{lem:colim_commute_poly} it suffices to make a map $\hocolim \> (A_{\rec} \comp F) \> (A_{\rec} \> f) \rightarrow \hocolim \> F \> f$.
 For this we use the recursion rule of $\hocolim$, and we start with the following string of maps
@@
 \begin{proof}
-This is the most difficult one, because colimits only commute with products if there are exponentials.
+This follows from a more general result which says that colimits commute with sigma types which is proven in \cite{boulier2015colimites,boulier2016} under `commutation with sigmas'.
 \end{proof}
@@
 \section{Conclusion and Further Work}
+Higher inductive types can be thus be constructed if we have the interval, homotopy pushout and homotopy colimits.
+The proof is constructive because it is done in type theory.
+Notice that we did not use that inductive types exist in general, but instead we only used the existence of sum and product types.
+Hence, from this theorem we can also construct all intervals.
+
+There is still some work which remains to be done.
+First of all, we expect that this theorem will have applications in the semantics and the metatheory of higher inductive types.
+The development should be simplified by it.
+Also, it should also allow generic programming in HoTT.
+
+Furthermore, there might be some interesting theoretical possibilities for the Three-HIT Theorem.
+We expect that it can be generalized if a syntax of higher inductive types with a higher dimensional paths is given.
+If constructor terms are used, then most of the proof might be reusable.
+Also, it would be interesting to relate it to other definitions of HITs.
+The work of Sojakova \cite{sojakova2015higher} relates higher inductive types to homotopy initial algebra.
+Since initial algebra are made as a colimit, it would be nice if this construction can be related to homotopy initial algebras some way.
+Also, the work by Altenkirch et al. \cite{altenkirch2016quotient} allows more general constructors which is not allowed in the current syntax.
+If the proof can be extended somehow to also allows these constructors, then that would pave the way towards constructive semantics of QIITs.
 

### 2017-03-19 Paper/Paper.tex
Usage of coequalizers to simplify the presentation.

@@
 \newcommand{\refl}[0]{\Boperator{refl}}
+
+\newcommand{\coeq}[0]{\Boperator{coeq}}
+\newcommand{\inC}[0]{\Boperator{inC}}
+\newcommand{\glueC}[0]{\Boperator{glueC}}
+
+\newcommand{\pcoeq}[0]{\Boperator{pcoeq}}
+\newcommand{\inP}[0]{\Boperator{inP}}
+\newcommand{\glueP}[0]{\Boperator{glueP}}
+
 \newcommand{\hpushout}[0]{\Boperator{hpushout}}
@@
 
-The goal of this paper is to formally justify this idea by showing that the higher inductive types defined in \cite{basoldhigher} can be generated from the interval, homotopy pushout and colimit.
+The goal of this paper is to formally justify this idea by showing that the higher inductive types defined in \cite{basoldhigher} can be generated from three specific higher inductive types, namely coequalizers, path coequalizers, and homotopy colimit.
 More concretely, we will prove the following theorem.
@@
 \label{thm:three-hit}
-In Martin-L\"of type theory extended with an interval object, homotopy pushouts and colimits, we can interpret each higher inductive type from \cite{basoldhigher}. 
+In Martin-L\"of type theory extended with a coequalizers, path coequalizers and homotopy colimits, we can interpret each higher inductive type from \cite{basoldhigher}. 
 This means that for each HIT we can define a type with the same introduction, elimination and computation rules.
@@
 In Section \ref{sec:prelims} we shall recall some of the required material for this paper.
-More concretely, we give the syntax of higher inductive types, and using that we define the interval, homotopy pushout, and colimit.
+More concretely, we give the syntax of higher inductive types, and using that we define required types.
 Next we define the approximating sequence of a higher inductive type in Section \ref{sec:approximator}, and in Section \ref{sec:rules} we show that the colimit of this sequence satisfies the rules of the given HIT.
 For this we need some lemmata which are proved in Section \ref{sec:Lemmata}.
+These are formalized in \textsc{Coq} \cite{CoqImpl} using the library from \cite{bauer2016hott}.
 
@@
 The introduction rules for $H$ as given in Definition \ref{def:hit} are
-%\begin{minipage}{0.6\textwidth}
 \[
-c : A \> H \rightarrow H
+c : A \> H \rightarrow H,
 \]
-%\end{minipage}
-%\begin{minipage}{0.4\textwidth}
 \[
@@
 \]
-%\end{minipage}
 We also have an elimination rule for which we use the lifting of constructor terms.
@@
 Let us now give some examples of higher inductive types which will be crucial in this paper.
-The first one would be the interval
+The first one identifies points in some type, and we call it the \emph{coequalizer}.
 \lstset{language=Coq}
 \begin{lstlisting}
-Inductive $I^1$ :=
-| $0$ : $I^1$
-| $1$ : $I^1$
-| $\seg$ : $0 = 1$
+Inductive $\coeq$ $(A, B : \Type)$ $(f, g : A \rightarrow B)$ :=
+| $\inC$ : $B \rightarrow \coeq \> A \> B \> f \> g$
+| $\glueC$ : $\prod (a : A), \inC \> (f \> a) = \inC \> (g \> a)$
 \end{lstlisting}
-Note that for every type $A$ with inhabitants $x$ and $y$ we have a path $x = y$ iff we have a map $I^1$ to $A$ sending 0 and 1 to $x$ and $y$ respectively.
-Let $\one$ be the unit type with point $\pt$.
-Then we can define maps $\delta_0, \delta_1 : \one \rightarrow$ sending $\pt$ to 0 and 1 respectively.
-Also, we define the boundary inclusion $\delta : \one + \one \rightarrow I^1$ by $\delta_0 + \delta_1$.
+The elimination rule for this type is as follows
+\begin{equation*}
+	\AxiomC{$\vdash Y : \coeq \> A \> B \> f \> g \rightarrow \Type$}
+	\noLine
+	\UnaryInfC{$\vdash i_Y : \prod (b : B), Y \> (\inC \> b)$}
+	%	\noLine
+	\AxiomC{$\vdash g_Y : \prod (a : A), \glueC_*(i_Y \> (f \> a)) = i_Y \> (g \> a)$}
+	\BinaryInfC{$\vdash \coeq\frec(i_Y, g_Y) : \prod (x : \coeq \> A \> B \> f \> g), Y \> x$}
+	\DisplayProof
+\end{equation*}
+Note the similarities with the definition of the coequalizer in category theory \cite{mac2013categories}.
 
-Next we define the homotopy pushout.
+Next we define a type which identifies two paths in some type which we shall call the \emph{path coequalizer}.
 \lstset{language=Coq}
 \begin{lstlisting}
-Inductive $\hpushout$ $(A, B, C : \Type)$ $(f : A \rightarrow B)$ $(g : A \rightarrow C)$ :=
-| $\inl$ : $B \rightarrow$ $\hpushout$ $A$ $B$ $C$ $f$ $g$
-| $\inr$ : $C \rightarrow$ $\hpushout$ $A$ $B$ $C$ $f$ $g$
-| $\glue$ : $\prod (a : A), \inl (f \> a) = \inr (g \> a)$
+Inductive $\pcoeq$ $(A, B : \Type)$ $(p : A \rightarrow \sum (b_1, b_2 : B), (b_1 = b_2) \times (b_1 = b_2))$ :=
+| $\inP$ : $B \rightarrow \pcoeq \> A \> B \> f \> g$
+| $\glueP$ : $\prod (a : A), \ap \> \inC \> (\pi_1(\pi_3(p \> a))) = \ap \> \inC \> (\pi_2(\pi_3(p \> a)))$
 \end{lstlisting}
-Note the similarities with the definition of the pushout \cite{mac2013categories}.
-Lastly, we can define the homotopy colimit as a higher inductive type in much the same way.
+We will abbreviate $p_i \> a = \pi_i(\pi_3(p \> a))$ for $i = 1, 2$.
+Note that this type has 2-paths, so it does not follow the given syntax.
+Furthermore, the identified paths used in the parameter are obliged to have the same endpoints.
+The introduction and computation rules are as expected, but we will give the elimination rule.
+\begin{equation*}
+	\AxiomC{$\vdash Y : \pcoeq \> A \> B \> f \> g \rightarrow \Type$}
+	\noLine
+	\UnaryInfC{$\vdash i_Y : \prod (b : B), Y \> (\inP \> b)$}
+	%	\noLine
+	\AxiomC{$\vdash g_Y : \prod (a : A), \apd \> i_Y \> (p_1 \> a) = \apd \> i_Y \> (p_2 \> a)$}
+	\BinaryInfC{$\vdash \pcoeq\frec(i_Y, g_Y) : \prod (x : \pcoeq \> A \> B \> f \> g), Y \> x$}
+	\DisplayProof
+\end{equation*}
+
+The last HIT we need is the homotopy colimit, and for that we again are inspired by the definition from category theory.
 \lstset{language=Coq}
@@
 \end{lstlisting}
+Now the elimination rule is as follows.
+\begin{equation*}
+	\AxiomC{$\vdash Y : \hocolim \> F \> f \rightarrow \Type$}
+	\noLine
+	\UnaryInfC{$\vdash i_Y : \prod (n : \mathbb{N}) (x : F \> n), Y \> (\inc \> n \> x)$}
+	\noLine
+	\UnaryInfC{$\vdash c_Y : \prod (n : \mathbb{N}) (x : F \> n), \com_*(i_Y \> n \> x) = i_Y \> (n+1) \> (f \> n \> x)$}
+	\UnaryInfC{$\vdash \hocolim\frec(i_Y, c_Y) : \prod (x : \hocolim \> F \> f), Y \> x$}
+	\DisplayProof
+\end{equation*}
 
@@
 Before giving the definition, let us acquire inspiration by looking in more detail at how an inductive type is constructed.
-Such a type $T$ is defined by a constructor $c : F \> T \rightarrow T$ with $F$ polynomial.
-Equivalently, we can define the type with a signature which is a polynomial functor $F$, and then by Ad\'amek's theorem it is the following colimit.
+Such a type $T$ is defined by a constructor $c : A \> T \rightarrow T$ with $A$ polynomial.
+Equivalently, we can define the type $T$ with a signature which is a polynomial functor $A$, and then by Ad\'amek's theorem $T$ is the following colimit.
 \[
@@
 {
-	\zero \ar[r] & F \> \zero  \ar[r] & F(F \> \zero) \ar[r] & \ldots
+	\zero \ar[r] & A \> \zero  \ar[r] & A(A \> \zero) \ar[r] & \ldots
 }
 \]
-To understand what this does, let us assume that $F \> X = 1 + X$, so that $T = \mathbb{N}$.
+To understand what this does, let us assume that $A \> X = 1 + X$, so that $T = \mathbb{N}$.
 This means we have two inclusions  $\xymatrix{1 \ar[r] & 1+X}$ and  $\xymatrix{X \ar[r] & 1+X}$, and we call them $0_C$ and $S_C$ respectively.
@@
 The first difference is that instead of starting with $\zero$, we start with all the nonrecursive constructors.
-Also, in this construction, the functor $F$ is applied at every step.
+Also, in this construction, the functor $A$ is applied at every step.
 Instead we will add terms built from the recursive constructors using previously constructed terms as arguments.
@@
 \end{lstlisting}
+We build a sequence $F$ of approximations.
 The first approximation just has a constructor $0$, and after that we add a constructor for $S \> 0$ to obtain the second approximation.
-In the third approximation, which we call $F' \> 3$, we found inhabitants $0$, $S \> 0$, and $S(S \> 0)$, and now we can make the first identification.
-To do so, we take the following homotopy pushout
+Continuing this way, we ultimately arrive at the third approximation, which we call $F' \> 3$, where we found inhabitants $0$, $S \> 0$, and $S(S \> 0)$.
+Now we can make the first identification, and to do so, we take the following homotopy pushout
 \[
@@
 Inductive $H$ :=
-| $c_{\nonrec}$ : $A_{\nonrec} \rightarrow H$
+| $c$ : $A_{\nonrec} \rightarrow H$
 | $c_{\rec}$ : $A_{\rec} \> H \rightarrow H$
@@
 Suppose, we have a constructor term $t$ such that $x : F \> T \Vdash t : G \>T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow P$.
-Then $t$ induces a map $\overline{t} : F \> P \rightarrow G \> H_{\Con}^n$ by replacing the constructors $c_{\nonrec}$ and $c_{\rec}$ by $c_{\nonrec}'$ and $c_{\rec}'$ respectively.
+Then $t$ induces a map $\overline{t} : F \> P \rightarrow G(H_{\Con}^n \> P)$ by replacing the constructors $c_{\nonrec}$ and $c_{\rec}$ by $c_{\nonrec}'$ and $c_{\rec}'$ respectively.
 \end{lemma}
@@
 Now we have sufficient to define the approximator.
-During the construction one also needs to pay attention to coherency.
-For example, in $P$ we have terms using $c_{\rec}$ at most $k$ times, so in $H_{\Approx} \> P$ we have duplicates of terms using $c_{\rec}$ less than $k$ times.
-There will be several coherency problems during the proof, so the pushout will seem rather intimidating at first.
+Given is the following data
+\begin{enumerate}
+	\item Types $P, Q, R$;
+	\item A map $j_Q : H_{\Con} \> Q \rightarrow P$;
+	\item An inclusion $j_R : H_{\Con} \> R \rightarrow Q$;
+	\item Paths $p_Q : \prod (x : Q), j_Q(\overline{t_i} \> x) = j_Q(\overline{r_i} \> x)$;
+	\item Paths $p_R : \prod (x : R), j_R(\overline{t_i} \> x) = j_R(\overline{r_i} \> x)$.
+\end{enumerate}
+The type $H_{\Approx}$ depends on the given data, but for clarity we will suppress it from the notation.
+We start with $H_{\Con} \> P$.
 
-\begin{definition}
-Let a higher inductive type $H$ be given as before, and let the type $H_{\Con}$ be defined as before.
-Given are parameters $P$ and $Q$ with maps $i_l : H_{\Con} \> Q \rightarrow P$ and $i_r : I^1 \times B_i \> Q + Q \rightarrow P$.
-Let us define the following maps.
-\begin{align*}
-\widetilde{i_l} &= i_l \comp \inn_1\\
-g_1 &: ((\one + \one) \times B_i \> P) + H_{\Con} \> Q  + (I^1 \times B_i \> Q + Q)\rightarrow (I^1 \times B_i \> P) + P\\
-g_1 &= (\inn_1 \comp \delta \times \idmap) + (\inn_2 \comp i_l) + (\inn_2 \comp i_r \circ \inn_1)\\
-g_2 &: ((\one + \one) \times B_i \> P) + H_{\Con} \> Q + (I^1 \times B_i \> Q + Q) \rightarrow H_{\Con} \> P + (I^1 \times B_i \> P + P)\\
-g_2 &= (\inn_1 \comp \overline{t_i} + \overline{r_i})+ (\inn_1 \comp H_{\Con} \> \widetilde{i_l}) + (\inn_2 \comp (I^1 \times B_i \> \widetilde{i_l}))
-\end{align*}
-Then we define the \emph{approximator} $H_{\Approx}$ of $H$ the following pushout.
+First, we need to guarantee that the added paths have the right endpoints.
+Note that we have two maps $\overline{t_i}, \overline{r_i} : B_i \> P \rightarrow H_{\Con} \> P$, and that gives the first coequalizer.
 \[
@@
 {
-	((\one + \one) \times B_i \> P) + H_{\Con} \> Q + (I^1 \times B_i \> Q) 
-	\ar[d]_{g_2} 
-	\ar[r]^-{g_1}
-	& (I^1 \times B_i \> P) + P  
-	\ar[d]^-{\inr}\\
-	H_{\Con} \> P + (I^1 \times B_i \> P)  
-	\ar[r]_-{\inl} 
-	& H_{\Approx} \> P \> Q \> i_l \> i_r
+	B_i \> P \ar@<-.5ex>[r]_-{\overline{r_i}} \ar@<.5ex>[r]^-{\overline{t_i}} & H_{\Con} \> P \ar[r]^-{\inC_1} & C_1
 }
 \]
-Note that this can be written as the homotopy pushout.
-Often we will suppress the maps from the notation.
-\end{definition}
 
-The types $Q$ and $P$ represent $F(n-2)$ and $F(n-1)$ respectively, and the maps $i_l$ and $i_r$ are the inclusion maps into $F(n-1)$.
-The new type is extended with constructors and paths given by $\inl \comp \inn_1$ and $\inr \comp \inn_1$ respectively.
-Also, there are coherency conditions added and these are given by the second and third component of the left upper corner.
-Their use will become clear in the Section \ref{sec:rules} when we construct the right introduction rules.
+However, this is not exactly the type we want due to coherency issues.
+For example, in $P$ we have terms using $c_{\rec}$ at most $k$ times, so in $H_{\Approx} \> P$ we have duplicates of terms using $c_{\rec}$ less than $k$ times.
+
+Remember that we we have $j_Q : H_{\Con} \> Q \rightarrow P$.
+Now we define the type $C_2$ which is the coequalizer of the following two arrows.
+\[
+\xymatrix
+{
+	H_{\Con} \> Q \ar@<-.5ex>[rrr]_-{H_{\Con} \> (j_Q \circ \inn_1)} \ar@<.5ex>[rrr]^-{\inn_1 \circ j_Q} & & & H_{\Con} \> P \ar[rr]^-{\inC_1} & & C_1
+}
+\]
+To explain what this does, let us assume for a moment that we have one construct $c$ with arity 1.
+For $c' \> x$ with $x : Q$, the upper map is the inclusion of $H_{\Con} \> Q$ on the first coordinate of $H_{\Con} \> P$.
+The lower map sends $c' \> x$ to $c' \> (j_Q \> (\inn_1 \> x))$, so it replaces $x$ by its image in $P$.
+
+Another coherency we need is for the paths.
+The paths use arguments from $B_i \> H$, and we want to prevent the presence of duplicates.
+For this we define $C_3$ as the coequalizer of the following two arrows.
+\[
+\xymatrix
+{
+	B_i \> Q
+	\ar@<-.5ex>[rrr]_-{H_{\Con} \> i \circ \overline{t_i}} \ar@<.5ex>[rrr]^-{\overline{t_i} \circ B_i(i \circ \inn_1)} 
+	& & & 
+	H_{\Con} \> P \ar[rrr]^-{\inC_2 \circ \inC_1}
+	& & &
+	C_2 
+}
+\]
+Similarly, we define $C_4$ by replacing $\overline{t_i}$ by $\overline{r_i}$.
+
+Lastly, we define $H_\Approx$, and for this we make one more identification.
+Instead of identifying points, we will identify paths in this step.
+Since also paths are added during the construction, there might also be duplicated paths.
+The resulting type should be free, so these paths should be identified.
+We define a map $q : B_i \> R \rightarrow \Sigma (x, y : P), (x = y) \times (x = y)$ sending $x : B_i \> R$ to the pair
+\[
+(\overline{t_i} \> x, \overline{r_i} \> x, \ap \> (i \circ \inn_1) \> (p_R \> x), p_Q \> (i_R \> x))
+\]
+Concluding the construction, we define $H_{\Approx}$ as $\pcoeq \> (B_i \> R) \> C_4 \> q$.
+
 Now we can define the approximating sequence.
@@
 	F \> 0 &= H_{\nonrec},\\
-F \> 1 &= H_{\Approx} \> (F \> 0) \> \zero \> (\zero\frec (F \> 0)) \> (\zero\frec (F \> 0))\\
-F(n+2) &= H_{\Approx} \> (F(n+1)) \> (F \> n) \> \inl \> \inr \qedhere
+	F \> 1 &= H_{\Approx} \> (F \> 0) \> \zero \> \zero \> \zero\frec \> \zero\frec \> \zero\frec \> \zero \frec \> \zero\frec\\
+	F \> 2 &= H_{\Approx} \> (F \> 1) \> (F \> 0) \> \zero \> \inl \> \inr \> \zero\frec \> \zero\frec \> \zero\frec\\
+	F(n+3) &= H_{\Approx} \> (F(n+2)) \> (F(n+1)) \> (F \> n) \> \inl \> \inr \> (f \> n) \> \overline{\glue} \> \overline{\glue} \qedhere
 \end{align*}
+where $\overline{\glue}$ is the map induced by the path $\glue$.
 For the maps maps $f \> n : F \> n \rightarrow F(n + 1)$, note that we always have the following sequence of maps
@@
 {
-	P \ar[r] & (I^1 \times B_i \> P) + P \ar[r] & H_{\Approx} \> P \> Q \> i_l \> i_r.
+	P \ar[r] & (I^1 \times B_i \> P) + P \ar[r] & H_{\Approx}.
 }
@@
 		A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} 
-		& H_{\rec}(F \> n) \ar[rr]^{\term \comp \iota_2} &
-		& H_{\Con}(F \> n) \ar[r]^-{\inl}
+		& H_{\rec}(F \> n) \ar[rr]^{\term \comp \inn_2} &
+		& H_{\Con}(F \> n) \ar[r]^-{\inC}
 		& H_{\Approx}(F \> n) = F(n + 1)
@@
 	A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} \ar[d]_{A_{\rec}(f \> n)} 
-		& H_{\rec}(F \> n) \ar[rr]^{\term \comp \iota_2} \ar[d]_{H_{\rec}(f \> n)} &
+		& H_{\rec}(F \> n) \ar[rr]^{\term \comp \inn_2} \ar[d]_{H_{\rec}(f \> n)} &
 		& H_{\Con}(F \> n) \ar[d]_{H_{\Con}(f \> n)}\\
 	A_{\rec}(F(n+1)) \ar[r]_-{c_{\rec}'} 
-		& H_{\rec}(F(n+1)) \ar[rr]_{\term \comp \iota_2} &
+		& H_{\rec}(F(n+1)) \ar[rr]_{\term \comp \inn_2} &
 		& H_{\Con}(F(n+1))
@@
 \]
-For a similar reason the right triangle commutes as well.
+For a similar reason, the right square commutes as well.
 Hence, it suffices to show that the following diagram commutes.
@@
 {
-	H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> (f \> n)} \ar[r]^-{\inl}
+	H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> (f \> n)} \ar[r]^-{\inC}
 		& F(n+1) \ar[d]^{f(n+1)}\\
-	H_{\Con}(F(n+1)) \ar[r]_-{\inl}
-		& H_{\Approx} \> (F(n+1)) \> (F \> n)
+	H_{\Con}(F(n+1)) \ar[r]_-{\inC}
+		& H_{\Approx} \> (F(n+1))
 }
@@
 Note that $H_{\Approx}(F(n+1)) = F(n+2)$ and $H_{\Approx}(F \> n) = F(n+1)$.
-Hence, this diagram commutes, because of the pushout we used to define $H_{\Approx}$.
+Hence, this diagram commutes, because of the coherency added in $C_2$.
 
 Next we need to define the introduction rules for the paths.
-Let us start by making maps $I^1 \times B_i \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
-Since homotopy colimits commute with polynomials, it suffices to make a map $\hocolim \> (I^1 \times B_i \> F) \> (I^1 \times B_i \> f)  \rightarrow \hocolim \> F \> f$.
+Let us start by extending the maps $t_i, r_i : B_i \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
+Since homotopy colimits commute with polynomials, it suffices to make a map $\hocolim \> (B_i \> F) \> (B_i \> f)  \rightarrow \hocolim \> F \> f$, and for this we need to start by defining maps $B_i(F \> n) \rightarrow \hocolim \> F \> f$.
+Note that by construction we always have maps $\overline{t_i}, \overline{r_i} : B_i(F \> n) \rightarrow H_{\Con}(F \> n)$, and thus we obtain maps $B_i(F \> n) \rightarrow F(n+1)$ by composing these with $\inC$.
 
-For this we use the eliminator of the homotopy colimit.
-First, we need to make for all $n$ a map $I^1 \times B_i \> (F \> n)  \rightarrow \hocolim \> F \> f$.
-By definition we have the following string of maps
+Now we need to check the commutativity of the following diagram
 \[
@@
 {
-	I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} & I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr}& F(n+1) \ar[rr]^-{\inc(n+1)} & & \hocolim \> F \> f.
+	B_i(F \> n) 
+	\ar[r]^-{\overline{t_i}} 
+	\ar[d]_{B_i(f \> n)} 
+	& 
+	H_{\Con}(F \> n) 
+	\ar[r]^-{\inC}
+	\ar[d]^{H_{\Con}(f \> n)}  
+	& 
+	C_2(F \> n)
+	\ar[r]^{\inC}
+	& 
+	F(n+1) 
+	\ar[d]^{f \> n}\\
+	B_i(F(n+1)) 
+	\ar[r]_-{\overline{t_i}} 
+	& 
+	H_{\Con}(F(n+1)) 
+	\ar[r]_-{\inC} 
+	& 
+	C_2(F(n+1))
+	\ar[r]_{\inC} 
+	& 
+	F(n+2)
 }
 \]
-Next we need to show that the following diagram commutes.
-\[
-\xymatrix
-{
-	I^1 \times B_i \> (F \> n) 
-		\ar[r]^-{\inn_1} \ar[d]_{I^1 \times B_i \> (f \> n)} 
-	& I^1 \times B_i \> (F \> n) + F \> n 
-		\ar[r]^-{\inr} 
-		%\ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} 
-	& F(n+1) 
-		\ar[d]^{f(n+1)}
-	\\
-	I^1 \times B_i \> (F(n+1)) 
-		\ar[r]_-{\inn_1} 
-	& I^1 \times B_i \> (F(n+1)) + F(n+1) 
-		\ar[r]_-{\inr}
-	& F(n+2) 
-}
-\]
-Note that this diagram commutes.
-For $x : I^1 \times B_i(F \> n)$ the path is $\glue(\inn_3 \> x)$.
-In particular, this means that $\apd \> p_i \> (\com \> n) \equiv \apd \> \inc(n+2) \> \glue(\inn_3 \> x)$
-%For the right diagram we can unpack the definition of $f(n+1)$.
-%\[
-%\xymatrix
-%{
-%	I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} & F(n+1) \ar[d]^{f(n+1)} \ar[dl]^{\inn_2}\\
-%	I^1 \times B_i \> (F(n+1)) + F(n+1) \ar[r]_-{\inr}& F(n+2) 
-%}
-%\]
-%On the second coordinate it commutes by definition and on the first it commutes by how $F(n+2)$ was defined.
+The right rectangle commutes, because the maps $\inC$ are built by composing constructors of the coequalizer, and thus it commutes by definition.
+Now it computes overall due to the second added coherency which says that $\inC(\overline{t_i}(B_i(f \> n) \> x))$ and $\inC(H_{\Con}(f \> n)(\overline{t_i} \> x))$ are equal for all $x : B_i(F \> n)$.
 
-In order to check that the paths have the right endpoints, we first need to extend the $\overline{t_i} \> n : B_i(F \> n) \rightarrow H_{\Con} (F \> n)$ to a map $B_i(\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
-For $n : \mathbb{N}$ and $(y, x) : 2 \times B_i(F \> n)$, we take 
-\[
-\inc \> (n+1) \> (\inl (g_1 (\inn_1 \> (y, x)))) \equiv \inc \> (n+1) \> (\inl(\overline{t_i} \> n \> (y, x))).
-\]
-For the image of com we have the following propositional equalities.
+In order to show that we indeed have paths $p_i$, we use the eliminator of the homotopy colimit.
+We need to show that for all $x : \hocolim \> F \> f$ we have $t_i \> x = r_i \> x$. 
+First, we need to give for all $x : F \> n$ an inhabitant of $t_i \> (\inc \> n \> x) = r_i \> (\inc \> n \> x)$.
+By the first identification we have a path $\glueC \> x$ between $\overline{t_i} \> x$ and $\overline{r_i} \> x$, and thus the right path is $\ap \> (\inc \> n) \> (\glueC \> x)$.
+
+To finish the proof, we need to show that $\com_*(\ap \> (\inc \> n) \> (\glueC \> x)) = \ap \> (\inc \> (n+1)) \> (\glueC \> ((B_i \>(f \>n)) \> x))$.
+This follows from the following computation.
 \begin{equation*}
 \begin{split}
-\inc &\> (n+2) \> (\inl(\overline{t_i} \> (n+1) \> (y, f \> n \> x)))
-\\
-&= \inc \> (n+2) \> ( f \> (n+1) \> (\inl(\overline{t_i} \> n \> (y, x))))
-\\
-&= \inc \> (n+1) \> (\inl(\overline{t_i} \> n \> (y, x))).
+\ap &\> (\inc \> (n+1)) \> (\glueC \> ((B_i \>(f \> n)) \> x))\\
+&= \ap \> (\inc \> (n+1)) \> (\ap \> (f \> n) \>\glueC \> x))\\
+&= \ap \> (\inc \> (n+1) \circ (f \> n)) \>\glueC \> x))\\
+&=\com_* \> (\ap \> (\inc \> n) \> (\glueC \> x))
 \end{split}
 \end{equation*}
-The first equation holds by the coherency on the points, and the second by $\com$.
-
-Now we check that the defined paths have the right endpoints, and for that we look at the following diagram.
-\[
-\xymatrix
-{
-	2 \times B_i(\hocolim \> F \> f) \ar[r] \ar[dr]_{\overline{t_i} + \overline{r_i}} & I^1 \times B_i(\hocolim \> F \> f) \ar[r] & \hocolim \> (I^1 \times B_i \> F) \> (I^1 \times B_i \> f) \ar[dl]\\
-	& \hocolim \> F \> f
-}
-\]
-
-$2 \times B_i(\hocolim \> F \> f)$ is isomorphic to $\hocolim \> (2 \times B_i \> F) \> 2 (\times B_i \> f)$.
-
-Induction to second, so we have $(0, x)$ (similar for $1$) and $x : F \> n$.
-This gets mapped to $(0, x)$ which is equal to $t_i$ via the path $\glue (\inl (0, x))$.
-
-We have
-\begin{equation*}
-\begin{split}
-(\com \> n)_*(\ap \> (\inc \> n) \> \glue (\inl (0, x))) 
-&= (\ap \> \overline{t_i} \> (\com \> n))^{-1} \conc \ap \> (\inc \> n) \> \glue (\inl (0, x)) \conc \ap \> p_i \> (\com \> n)\\
-= \ap \> (\inc (n+1))) \>\glue (\inl (0, f \> n \> x))\\
-\end{split}
-\end{equation*}
-$(\ap \> \overline{t_i} \> \com)^{-1}$ is like $\ap \> (\inc \> n) \> (\ap \> c \> \ldots (\ldots \ap \> \text{coherence path}))$, because of the computation rule of $c_i$.
-
-This is the coherence path which should be added on level $n$.
+The first step follows from the third added coherency, the second from Lemma 2.2.2 in \cite{hottbook}, and the last step from Lemma \ref{lem:pathext}.
 
@@
 Hence, this diagram commutes, and thus the first coherency is fine.
+The equality between the points is $\refl$ as they are definitionally equal.
 
@@
 \[
-h \> (n+1) \> (\inr(\inn_1 (y, x))) = h \> n \> (\inn_1 (y, x)) = \overline{q_{Y, i}}(y, h \> n \> x).
+h \> (n+1) \> (\inr(\inn_1 (y, x))) \equiv h \> n \> (\inn_1 (y, x)) \equiv \overline{q_{Y, i}}(y, h \> n \> x).
 \]
 \[
-h \> (n+1) \> (I^1 \times B_i \> \inl \> (y, x)) = h \> (n+1) \> (y, \inl x) = \overline{q_{Y, i}}(y, h \> (n+1) \> (\inl \> x)) = \overline{q_{Y, i}}(y, h \> n \> x).
+h \> (n+1) \> (I^1 \times B_i \> \inl \> (y, x)) \equiv h \> (n+1) \> (y, \inl \> x) \equiv \overline{q_{Y, i}}(y, h \> (n+1) \> (\inl \> x)) \equiv \overline{q_{Y, i}}(y, h \> n \> x).
 \]
 Hence, this coherency is fine as well.
+Since they are definitionally equal, we can just take the path $\refl$.
+
+Lastly, we need to check a coherency condition for the path $\glue$, and here the point is that all coherencies, including this one, are mapped to $\refl$.
+This means that $\glue$ gets mapped mapped to $\refl$.
+We thus take a look at the following corner
+\[
+\xymatrix
+{
+	(\two \times B_i \> (F \> n)) \times I^1
+	\ar[d]_{(f \> n) \circ \overline{\glue}}
+	\ar[rrrr]^-{\overline{\glue} \circ (\two \times B_i \> (f(n+1)))}
+	& & & & F(n+2)
+	\\
+	F(n+2)
+}
+\]
+The maps are induced by $\glue$.
+\[
+\ap \> (h \> (n+2)) \> (\glue(y, f \> n \> x)) = \refl?
+\]
+\begin{equation*}
+\begin{split}
+\ap & \> (h \> (n+2)) \> (\ap \> (f(n+1)) \> (\overline{\glue} \> (y, x)))
+\\
+&=
+\ap \> (h \> (n+2) \circ f(n+1)) \> (\overline{\glue} \> (y, x))\\
+&=
+\ap \> (h \> (n+1)) \> (\overline{\glue} \> (y, x))\\
+\end{split}
+\end{equation*}
 
@@
 {
-	((\one + \one) \times B_i \> (F(n+1))) + H_{\Con} \>  (F \> n) \ar[d]_{\overline{t_i} + \overline{r_i} + H_{\Con} \> f} \ar[rr]^-{\delta + \inl} & & (I^1 \times B_i \> (F(n+1))) + F(n+1)  \ar[d]^{\inr}\\
+	(\two \times B_i \> (F(n+1))) + H_{\Con} \>  (F \> n) \ar[d]_{\overline{t_i} + \overline{r_i} + H_{\Con} \> f} \ar[rr]^-{\delta + \inl} & & (I^1 \times B_i \> (F(n+1))) + F(n+1)  \ar[d]^{\inr}\\
 	H_{\Con} \> (F(n+1)) \ar[rr]_{\inl} & & F(n+2)
@@
 \label{sec:Lemmata}
-In this section we proof the required lemmata to show that colimits over $\mathbb{N}$ commute with polynomials.
+In this section we prove the required lemmata to show that colimits over $\mathbb{N}$ commute with polynomials.
 In category theory this result is standard \cite{mac2013categories}.
@@
 \label{lem:colimcon}
-$\hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id})$ is isomorphic to $A$.
+The type $\hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id})$ is isomorphic to $A$.
 \end{lemma}
@@
 \label{lem:colimsum}
-Colimits commute with coproducts, so $\hocolim \> ((G_1 + G_2) \circ F) \> ((G_1 + G_2) \> f)$ and $\hocolim \> (G_1 \circ F) \> (G_1 \> f) + \hocolim \> (G_2 \circ F) \> (gG2 \> f)$ are isomorphic.. 
+Colimits commute with coproducts, so $\hocolim \> (G_1 + G_2) \> (g_1 + g_2)$ and $\hocolim \> G_1 \> g_1 + \hocolim \> G_2 \> g_2$ are isomorphic.
 \end{lemma}
@@
 \[
-\hocolim \> ((G_1 + G_2) \circ F) \> ((G_1 + G_2) \> f) \rightarrow \hocolim \> (G_1 \circ F) \> (G_1 \> f) + \hocolim \> (G_2 \circ F) \> (G_2 \> f).
+\hocolim \> (G_1+G_2) \> (g_1 + g_2) \rightarrow \hocolim \> G_1 \> g_1 + \hocolim \> G_2 \> g_2.
 \]
-This map is defined by recursion over the colimit, so take any $n : \mathbb{N}$ and $x : F \> n$.
+This map is defined by recursion over the colimit, so take any $n : \mathbb{N}$ and $x : G_i \> n$.
 Then the image of $\inc \> n \> (\inn_i \> x)$ is defined to be $\inn_i (\inc \> n \> x)$, and the image of $\com \> n \> (\inn_i \> x)$ is defined by
-$\ap \> \inn_i \> (\com \> (G1 \circ F) \> (G_1 \> f) \> n \> x)$.
+$\ap \> \inn_i \> (\com \> G_i \> g_i \> n \> x)$.
 
@@
 \[
-\hocolim \> (G_i \circ F) \> (G_i \> f) \rightarrow \hocolim \> ((G_1 + G_2) \circ F) \> ((G_1 + G_2) \> f).
+\hocolim \> G_i \> g_i \rightarrow \hocolim \> (G_1 + G_2) \> (g_1 + g_2).
 \]
@@
 
+\begin{lemma}
+\label{lem:pathext}
+Given are types $A, B$ and functions $f, g : A \rightarrow B$ such that we have an inhabitant $e : \prod (x : A), f \> x = g \> x$.
+Furthermore, assume that we have paths $q : \prod (x : A), l = r$ where $l$ and $r$ are terms using $x : A$ as free variable.
+Then for all $x : A$ we have a path
+\[
+(e \> x)_* \> (\ap \> f \> (q \> x)) = \ap \> g \> (q \> x).
+\]
+\end{lemma}
+
+\begin{proof}
+This follows from path induction on $e$.
+In the case $e$ happens to be $\refl$, then $(e \> x)_*$ is $\idmap$.
+Then the desired path is just $\refl$.
+\end{proof}
+
 \section{Conclusion and Further Work}
-Higher inductive types can be thus be constructed if we have the interval, homotopy pushout and homotopy colimits.
-The proof is constructive because it is done in type theory.
-Notice that we did not use that inductive types exist in general, but instead we only used the existence of sum and product types.
-Hence, from this theorem we can also construct all intervals.
+Higher inductive types can thus be constructed if we have the interval, homotopy pushout and homotopy colimits.
+Since the construction is done in homotopy type theory without assuming extra axioms, the proof is constructive.
+Notice that the only inductive types we needed were the sum and product types rather than the general class of W-types or those described inductive schemes.
+Hence, we can also deduce the existence of all inductive types from this theorem if we just have sums, products, and the three HITs.
 
@@
 First of all, we expect that this theorem will have applications in the semantics and the metatheory of higher inductive types.
-The development should be simplified by it.
-Also, it should also allow generic programming in HoTT.
+There are already several interpretations of homotopy type theory in abstract homotopy theory \cite{arndt2011homotopy,awodey2009homotopy,bezem2014model,cohen2016cubical,kapulkin2012simplicial}.
+Rather than using the full-blown definition one could instead just look at a small number of cases, and that could simplify checking whether all higher inductive types exist in some model.
+Also, the theorem could also be used for generic programming with higher inductive types \cite{altenkirch2003generic}.
+If we know how a function is defined for the interval, the homotopy pushout, and the homotopy colimit, then we know how it is defined for all higher inductive types.
 
-Furthermore, there might be some interesting theoretical possibilities for the Three-HIT Theorem.
+Furthermore, there might be some interesting theoretical possibilities for the Three-HITs Theorem.
 We expect that it can be generalized if a syntax of higher inductive types with a higher dimensional paths is given.
-If constructor terms are used, then most of the proof might be reusable.
-Also, it would be interesting to relate it to other definitions of HITs.
+If constructor terms are used, then most of the proof might even be reusable.
+
 The work of Sojakova \cite{sojakova2015higher} relates higher inductive types to homotopy initial algebra.
-Since initial algebra are made as a colimit, it would be nice if this construction can be related to homotopy initial algebras some way.
-Also, the work by Altenkirch et al. \cite{altenkirch2016quotient} allows more general constructors which is not allowed in the current syntax.
+Since initial algebra are made as a colimit, it could be that this construction and homotopy initial algebras are related in some way.
+Also, the work by Altenkirch et al. \cite{altenkirch2016quotient} allows more general constructors which is not allowed in the syntax used in this paper.
 If the proof can be extended somehow to also allows these constructors, then that would pave the way towards constructive semantics of QIITs.
 
-\nocite{*}
+%\nocite{*}
 

### 2017-03-20 Paper/Paper.tex
Fixed mistakes

@@
 If $n$ is clear from the context, then we shall not write it down.
-
-\begin{lemma}
-Suppose, we have a constructor term $t$ such that $x : F \> T \Vdash t : G \>T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow P$.
-Then $t$ induces a map $\overline{t} : F \> P \rightarrow G(H_{\Con}^n \> P)$ by replacing the constructors $c_{\nonrec}$ and $c_{\rec}$ by $c_{\nonrec}'$ and $c_{\rec}'$ respectively.
-\end{lemma}
-
-\begin{proof}
-We use induction on the form of the constructor term.
-\begin{itemize}
-	\item $t = a$ with $a : B$ and $B$ does not use $T$. Then we define $\overline{t} \> y = a$.
-	\item $t = x$ with $x : F \> T$. Then we define $\overline{t} \> y = \inn_P y$.
-	\item $t = c_{\nonrec} a$ with $a : A_{\nonrec}$. Then we define $\overline{t} \> y = c_{\nonrec}' a$.
-	\item $t = c_{\rec} r$ with $r : A_{\rec} \> T$ where $r$ uses at most $n-1$ constructors. 
-			  By induction we have a map $\overline{r} : F \> P \rightarrow A_{\rec} \> H_{\Con}^{n-1}$.
-			  Then we define $\overline{t} \> y = c_{\rec}' (\overline{r} \> x)$.
-	\item For the rules for the projection, pairing and injection it is trivial. \qedhere
-\end{itemize}
-\end{proof}
+From Lemma \ref{lem:constrTerm} we can conclude that we can interpret the constructor terms in $H_{\Con} \> P$
 
@@
 Given is the following data
-\begin{enumerate}
+\begin{itemize}
 	\item Types $P, Q, R$;
@@
 	\item Paths $p_R : \prod (x : R), j_R(\overline{t_i} \> x) = j_R(\overline{r_i} \> x)$.
-\end{enumerate}
+\end{itemize}
 The type $H_{\Approx}$ depends on the given data, but for clarity we will suppress it from the notation.
@@
 
-Another coherency we need is for the paths.
-The paths use arguments from $B_i \> H$, and we want to prevent the presence of duplicates.
-For this we define $C_3$ as the coequalizer of the following two arrows.
-\[
-\xymatrix
-{
-	B_i \> Q
-	\ar@<-.5ex>[rrr]_-{H_{\Con} \> i \circ \overline{t_i}} \ar@<.5ex>[rrr]^-{\overline{t_i} \circ B_i(i \circ \inn_1)} 
-	& & & 
-	H_{\Con} \> P \ar[rrr]^-{\inC_2 \circ \inC_1}
-	& & &
-	C_2 
-}
-\]
-Similarly, we define $C_4$ by replacing $\overline{t_i}$ by $\overline{r_i}$.
-
 Lastly, we define $H_\Approx$, and for this we make one more identification.
@@
 The resulting type should be free, so these paths should be identified.
-We define a map $q : B_i \> R \rightarrow \Sigma (x, y : P), (x = y) \times (x = y)$ sending $x : B_i \> R$ to the pair
+We define a map $q : B_i \> R \rightarrow \sum (x, y : P), (x = y) \times (x = y)$ sending $x : B_i \> R$ to the pair
 \[
-(\overline{t_i} \> x, \overline{r_i} \> x, \ap \> (i \circ \inn_1) \> (p_R \> x), p_Q \> (i_R \> x))
+(\overline{t_i} \> x, \overline{r_i} \> x, \ap \> (j_Q \circ \inn_1) \> (p_R \> x), p_Q \> (j_R \> x))
 \]
-Concluding the construction, we define $H_{\Approx}$ as $\pcoeq \> (B_i \> R) \> C_4 \> q$.
+Concluding the construction, we define $H_{\Approx}$ as $\pcoeq \> (B_i \> R) \> C_2 \> q$.
 
@@
 \begin{definition}
-In the setting as described, we simultaneously define a sequence of approximations $F : \mathbb{N} \rightarrow \Type$ to $H$ and maps $f : \prod(n : \mathbb{N}), F \> n \rightarrow F(n+1)$ as follows
-\begin{align*}
-	F \> 0 &= H_{\nonrec},\\
-	F \> 1 &= H_{\Approx} \> (F \> 0) \> \zero \> \zero \> \zero\frec \> \zero\frec \> \zero\frec \> \zero \frec \> \zero\frec\\
-	F \> 2 &= H_{\Approx} \> (F \> 1) \> (F \> 0) \> \zero \> \inl \> \inr \> \zero\frec \> \zero\frec \> \zero\frec\\
-	F(n+3) &= H_{\Approx} \> (F(n+2)) \> (F(n+1)) \> (F \> n) \> \inl \> \inr \> (f \> n) \> \overline{\glue} \> \overline{\glue} \qedhere
-\end{align*}
-where $\overline{\glue}$ is the map induced by the path $\glue$.
-For the maps maps $f \> n : F \> n \rightarrow F(n + 1)$, note that we always have the following sequence of maps
+In the setting as described, we simultaneously define a sequence of approximations $F : \mathbb{N} \rightarrow \Type$ to $H$ and maps $f : \prod(n : \mathbb{N}), F \> n \rightarrow F(n+1)$ as follows.
+\begin{itemize}
+	\item We define $F \> 0 = H_{\nonrec}$.
+	\item We define $F \> 1 = H_{\Approx}$ taking $P = F \> 0$ and $Q, R = \zero$ and the maps are defined by $\zero\frec$.
+	\item We define $F \> 2 = H_{\Approx}$ with $P= F \> 1, Q = F \> 0$ and $R =\zero$. We have a map $Q \rightarrow P$ defined to be the composition of all $\inC$ with $\inn_1$.
+	\item We define $F(n+3) = H_{\Approx}$ with $P = (F(n+2)$, $Q = F(n+1)$, and $R = F \> n$.
+The maps $Q \rightarrow P$ and $R \rightarrow Q$ are defined to be the composition of $\inC$ with $\inn_1$ as in the construction.
+The paths $p_Q$ and $p_R$ are given by the path $\glueC$ from the first coequalizer.
+\end{itemize}
+For the maps $f \> n : F \> n \rightarrow F(n + 1)$, note that we always have the following sequence of maps
 \[
@@
 {
-	P \ar[r] & (I^1 \times B_i \> P) + P \ar[r] & H_{\Approx}.
+	F \> n \ar[r] & H_{\Con} \> (F \> n) \ar[r] & C_1 \ar[r] & \ldots \ar[r] & C_4 \ar[r] & H_{\Approx}.
 }
@@
 The right rectangle commutes, because the maps $\inC$ are built by composing constructors of the coequalizer, and thus it commutes by definition.
-Now it computes overall due to the second added coherency which says that $\inC(\overline{t_i}(B_i(f \> n) \> x))$ and $\inC(H_{\Con}(f \> n)(\overline{t_i} \> x))$ are equal for all $x : B_i(F \> n)$.
+Now it computes overall due to Lemma \ref{lem:constrCoh} which says that $\inC(\overline{t_i}(B_i(f \> n) \> x))$ and $\inC(H_{\Con}(f \> n)(\overline{t_i} \> x))$ are equal for all $x : B_i(F \> n)$.
 
@@
 Now suppose that we have a map $h \> n : \prod (x : F \> n), Y(\inc \> n \> x)$, and our goal is to make a map $h(n+1) : \prod  (x : F(n+1)), Y(\inc \> (n+1) \> x)$.
-In order to do so, we will first look at how to extend $h \> n$ to a map $\prod (x : H_{\Con} (F \> n)), Y(\inc \> (n+1) \> (\inl \> x))$.
+In order to do so, we will first look at how to extend $h \> n$ to a map $\prod (x : H_{\Con} (F \> n)), Y(\inc \> (n+1) \> (\inC \> x))$.
 
@@
 
-Next we need to extend the map to $H_{\Approx} \> P \> Q$.
-This is done by the universal mapping property of the pushout, and that requires two steps.
-First, we need to extend the map to $I^1 \times B_i \> P$, and second we need to check that the diagram given by the pushout commutes.
-For that we start with $(y, x) : I^1 \times B_i \> P$, and we use $I^1$-induction.
-If $y = 0$, we map it to $\hatt_i (x)$, and for $y = 1$ we map it to $\hatr_i (x)$.
-Now the path $q_{Y, i}$ gives the image of $\seg$, and that finishes the induction.
+Next we need to extend the map to $H_{\Approx}$.
+This is done by the universal mapping property of the coequalizer, and that requires some steps.
+First, to give an paths between the images of $t_i \> x$ and $r_i \> x$.
+Note that the images of these are $\hatt_i \> x$ and $\hatr_i \> x$ respectively, and then $q_{Y, i}$ gives the desired paths..
 
-Since $H_{\Approx}$ is a pushout, we also need to show that a diagram commutes.
-The left upper corner is defined to be a sum, and thus it suffices to check it for each of the components.
-For the first, $H_{\Con} \> P$, note that the map $\varphi'$ to $Y$ defined by extension, sends the constructor term $t_i$ to its lift $\hatt_i$, since it replaces each $c_{\rec}$ by $c_{Y, \rec}$.
-On $I^1 \times B_i \> P$ the points are mapped to the lifts $\hatt_i$ as well, and thus the diagram commutes on this component.
+Next we check the coherency conditions, and we start with the first.
+We need to check that $\inn_1(\inC \> x)$ and $H_{\Con} \> \inC \> x$ get mapped to the same element for $x : H_{\Con}(F \> n)$.
+To do so, we use a case distinction on $H_{\Con}(F \> n)$, and for the case $x \equiv \inn_1 \> y$ with $y : F \> n$, we have the following equations 
+\begin{equation*}
+\begin{split}
+h \> (n+1) \> (\inn_1(\inC \> (\inn_1 \> y))) 
+\equiv 
+h \> (n+1) \> (\inn_1(f \> n \> y)),
+\end{split}
+\end{equation*}
+\begin{equation*}
+\begin{split}
+h \> (n+1) \> (H_{\Con} \> (\inC \circ \inn_1) \> (\inn_1 \> y)) 
+&\equiv 
+h \> (n+1) \> (\inn_1(\inC(\inn_1 \> y)))
+\\
+&\equiv
+h \> (n+1) \> (\inn_1(f \> n \> y)).
+\end{split}
+\end{equation*}
+Here we use that $f \> x$ is defined to be $\inC(\inn_1 \> x)$.
+Since they are definitionally equal, we can just use the path $\refl$.
 
-Next we do it for the coherency condition on the points where we look at the following corner
-\[
-\xymatrix
-{
-	H_{\Con}(F \> n) \ar[r]^{\inl} \ar[d]_{H_{\Con} (f \> n)} & F(n+1)\\
-	H_{\Con} (F(n+1))
-}
-\]
-Elements of $H_{\Con}(F \> n)$ are terms built from $c_{\rec}$ on $F \> n$.
-In order to show that it commutes for all inhabitants of $H_{\Con}(F \> n)$, we use induction on the depth.
-If the inhabitant is of the form $\inn_1 \> x$ with $x : F \> n$, then it gets mapped to the first component of $H_{\Con} (F(n+1))$ and $F(n+1)$.
-In both cases it is just mapped with $h \> (n+1)$ and thus they are equal.
+For the other cases, we take a look at $c_{\rec}' \> y$.
+\begin{equation*}
+\begin{split}
+h \> (n+1) \> (\inn_1(\inC \> (c_{\rec}' \> y))) 
+&\equiv h \> (n+1) \> (\inC \> (c_{\rec}' \> y))\\
+&\equiv h \> (n+1) \> (c_{\rec}' \> y)\\
+&\equiv c_{Y, \rec} (h \> n \> y)
+\end{split}
+\end{equation*}
+\begin{equation*}
+\begin{split}
+h \> (n+1) \> (H_{\Con} \> (\inC \circ \inn_1) \> (c_{\rec}' \> y)) 
+&\equiv 
+h \> (n+1) \> (c_{\rec}' \> (f \> n \> y))
+\\
+&\equiv
+c_{Y, \rec} \> (h \> (n+1) \> (f \> n \> y)\\
+&\equiv
+c_{Y, \rec} \> (h \> (n+1) \> (\inC(\inn_1 \> y)).
+\end{split}
+\end{equation*}
 
-To show that it holds for the other inhabitants as well, we take a look at $c_{\rec}' \> x$.
 By $\inl$ it gets mapped $\inl (c_{\rec}' \> x)$.
@@
 
-Now we also need to check the second coherency, and then we look at another corner
-\[
-\xymatrix
-{
-	I^1 \times B_i (F \> n) \ar[rr]^-{\inr \circ \inn_1} \ar[d]_{I^1 \times B_i \inl} & & F(n+1)\\
-	I^1 \times B_i(F(n+1)) 
-}
-\]
-Let $(y, x) : I^1 \times B_i (F \> n)$.
-Note that 
-\[
-h \> (n+1) \> (\inr(\inn_1 (y, x))) \equiv h \> n \> (\inn_1 (y, x)) \equiv \overline{q_{Y, i}}(y, h \> n \> x).
-\]
-\[
-h \> (n+1) \> (I^1 \times B_i \> \inl \> (y, x)) \equiv h \> (n+1) \> (y, \inl \> x) \equiv \overline{q_{Y, i}}(y, h \> (n+1) \> (\inl \> x)) \equiv \overline{q_{Y, i}}(y, h \> n \> x).
-\]
-Hence, this coherency is fine as well.
-Since they are definitionally equal, we can just take the path $\refl$.
-
-Lastly, we need to check a coherency condition for the path $\glue$, and here the point is that all coherencies, including this one, are mapped to $\refl$.
-This means that $\glue$ gets mapped mapped to $\refl$.
-We thus take a look at the following corner
-\[
-\xymatrix
-{
-	(\two \times B_i \> (F \> n)) \times I^1
-	\ar[d]_{(f \> n) \circ \overline{\glue}}
-	\ar[rrrr]^-{\overline{\glue} \circ (\two \times B_i \> (f(n+1)))}
-	& & & & F(n+2)
-	\\
-	F(n+2)
-}
-\]
-The maps are induced by $\glue$.
-\[
-\ap \> (h \> (n+2)) \> (\glue(y, f \> n \> x)) = \refl?
-\]
-\begin{equation*}
-\begin{split}
-\ap & \> (h \> (n+2)) \> (\ap \> (f(n+1)) \> (\overline{\glue} \> (y, x)))
-\\
-&=
-\ap \> (h \> (n+2) \circ f(n+1)) \> (\overline{\glue} \> (y, x))\\
-&=
-\ap \> (h \> (n+1)) \> (\overline{\glue} \> (y, x))\\
-\end{split}
-\end{equation*}
+For the second coherency we need to check that
 
@@
 \label{sec:Lemmata}
-In this section we prove the required lemmata to show that colimits over $\mathbb{N}$ commute with polynomials.
-In category theory this result is standard \cite{mac2013categories}.
+\begin{lemma}
+\label{lem:constrTerm}
+Suppose, we have a constructor term $t$ such that $x : F \> T \Vdash t : G \>T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow P$.
+Then $t$ induces a map $\overline{t} : F \> P \rightarrow H_{\Con}^n \> (G \> P)$ by replacing the constructors $c_{\nonrec}$ and $c_{\rec}$ by $c_{\nonrec}'$ and $c_{\rec}'$ respectively.
+\end{lemma}
+
+\begin{proof}
+We use induction on the form of the constructor term.
+\begin{itemize}
+	\item $t = a$ with $a : B$ and $B$ does not use $T$. Then we define $\overline{t} \> y = \inn_1 \> a$.
+	\item $t = x$ with $x : F \> T$. Then we define $\overline{t} \> y = \inn_1 \> y$.
+	\item $t = c_{\nonrec} \> a$ with $a : A_{\nonrec}$. Then we define $\overline{t} \> y = \inn_1 \> (c_{\nonrec}' \> a)$.
+	\item $t = c_{\rec} \> r$ with $r : A_{\rec} \> T$ where $r$ uses at most $n-1$ constructors. 
+	By induction we have a map $\overline{r} : F \> P \rightarrow A_{\rec} \> H_{\Con}^{n-1}$.
+	Then we define $\overline{t} \> y = c_{\rec}' (\overline{r} \> x)$.
+	\item For the rules for the projection, pairing and injection it is trivial. \qedhere
+\end{itemize}
+\end{proof}
+
+\begin{lemma}
+\label{lem:constrCoh}
+Suppose, we have a constructor term $t$ such that $x : F \> T \Vdash t : G \> T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow Q$.
+Furthermore, we assume that we have a map $f : Q \rightarrow P$
+Then for all $x : F \> P$ the terms $\overline{t}(F \> f \> x)$ and $(H_{\Con} \circ G) \> f \> (\overline{t} \> x)$ are equal.
+\end{lemma}
+
+\begin{proof}
+Again we use induction on the constructor term.
+\begin{itemize}
+	\item $t = a$ with $a : B$ and $B$ does not use $T$. 
+	Then we have $G \> P = B$, and thus 
+	$
+	\overline{t}(F \> f \> x) = a.
+	$
+	On the other hand, we have, 
+	\[
+	(H_{\Con} \circ G) \> f \> (\overline{t} \> x) = G \> f \> a = a.
+	\]
+	\item $t = x$ with $x : F \> T$. 
+	Then $G \> P = F \> P$, and thus
+	$
+	\overline{t}(F \> f \> x) = \inn_1(F \> f \> x).
+	$
+	Also,
+	\[
+	(H_{\Con} \circ G) \> f \> (\overline{t} \> x) = (H_{\Con} \circ G) \> f \> (\inn_1 \> x) = \inn_1(G \> f \> x) = \inn_1(F \> f \> x).
+	\]
+	\item $t = c_{\nonrec} \> a$ with $a : A_{\nonrec}$. 
+	Then $G \> P = P$, and thus
+	$
+	\overline{t}(F \> f \> x) = \inn_1(f(c'_{\nonrec} \> a))
+	$.
+	Also,
+	\[
+	(H_{\Con} \circ G) \> f \> (\overline{t} \> x) = H_{\Con} \> f \> (\inn_1(c'_{\nonrec} \> a)) = \inn_1(f(c'_{\nonrec} \> a))
+	\]
+	\item $t = c_{\rec} \> r$ with $r : A_{\rec} \> T$ where $r$ uses at most $n-1$ constructors. 
+	The induction hypothesis in this case is that $H_{\Con} \> f \> (\overline{r} \> x) = \overline{r}(F \> f \> x)$.
+	Then again $G \> P = P$, and thus
+	$
+	\overline{t}(F \> f \> x) = c'_{\rec} \> (\overline{r}(F \> f \> x))
+	$.
+	Furthermore,
+	\[
+	(H_{\Con} \circ G) \> f \> (\overline{t} \> x) = H_{\Con} \> f \> (c'_{\rec} \> (\overline{r} \> x)) = c'_{\rec} \> (H_{\Con} \> f \> (\overline{r} \> x)) = c'_{\rec} \> (\overline{r}(F \> f \> x))
+	\]
+	\item For the rules for the projection, pairing and injection it is trivial. \qedhere
+\end{itemize}
+\end{proof}
 

### 2017-03-20 Paper/Paper.tex
Fixed coherencies in elimination rule

@@
 \[
-(\overline{t_i} \> x, \overline{r_i} \> x, \ap \> (j_Q \circ \inn_1) \> (p_R \> x), p_Q \> (j_R \> x))
+(\overline{t_i} \> x, \overline{r_i} \> x, \ap \> (j_Q \circ \inn_1) \> (p_R \> x), p_Q \> (B_i \> j_R \> x))
 \]
@@
 Suppose, we have a map $g : P \rightarrow \hocolim \> F \> f$, and that we already constructed $\varphi : \prod (x : P), Y(g \> x)$.
-Our goal is to extended the map into a $\varphi' : \prod (x : H_{\rec} P), Y(c_{Y, \rec} \> x)$, and for that we use $H_{\rec}$-induction.
+Our goal is to extend the map into $\varphi' : \prod (x : H_{\rec} P), Y(c_{Y, \rec} \> x)$, and for that we use $H_{\rec}$-induction.
 Note that for each $c'_{\rec} \> x$ with $x : A_{\rec} \> P$ we have the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$, and thus we have a type family on $H_{\rec}$.
@@
 On the component $P$ it is just $\varphi$, and on the other components we define it via extension.
+We call this map $h_1$.
 
@@
 First, to give an paths between the images of $t_i \> x$ and $r_i \> x$.
-Note that the images of these are $\hatt_i \> x$ and $\hatr_i \> x$ respectively, and then $q_{Y, i}$ gives the desired paths..
+Note that the images of these are $\hatt_i \> x$ and $\hatr_i \> x$ respectively, and then $q_{Y, i}$ gives the desired paths.
+This gives an extension $h_2$ to $C_1$.
 
 Next we check the coherency conditions, and we start with the first.
-We need to check that $\inn_1(\inC \> x)$ and $H_{\Con} \> \inC \> x$ get mapped to the same element for $x : H_{\Con}(F \> n)$.
+We need to check that $\inn_1(\inC \> x)$ and $H_{\Con} \> \inC \> x$ get mapped to the same element for $x : H_{\Con}(F \> n)$ by $h_2$.
 To do so, we use a case distinction on $H_{\Con}(F \> n)$, and for the case $x \equiv \inn_1 \> y$ with $y : F \> n$, we have the following equations 
@@
 \begin{split}
-h \> (n+1) \> (\inn_1(\inC \> (\inn_1 \> y))) 
-\equiv 
-h \> (n+1) \> (\inn_1(f \> n \> y)),
+h_2 \> (\inC(\inn_1(\inC \> (\inn_1 \> y))))
+&\equiv
+h_1 \> (\inn_1(\inC \> (\inn_1 \> y))) \\
+&\equiv 
+h_1 \> (\inn_1(f \> n \> y))\\
+&\equiv 
+h_1 \> (\inn_1(\inC(\inn_1 \> y))),
 \end{split}
@@
 \begin{split}
-h \> (n+1) \> (H_{\Con} \> (\inC \circ \inn_1) \> (\inn_1 \> y)) 
+h_2 \> (\inC(H_{\Con} \> (\inC \circ \inn_1) \> (\inn_1 \> y)))
 &\equiv
-h \> (n+1) \> (\inn_1(\inC(\inn_1 \> y)))
-\\
+h_1 \> (H_{\Con} \> (\inC \circ \inn_1) \> (\inn_1 \> y))\\
 &\equiv 
-h \> (n+1) \> (\inn_1(f \> n \> y)).
+h_1 \> (\inn_1(\inC(\inn_1 \> y)))
 \end{split}
 \end{equation*}
-Here we use that $f \> x$ is defined to be $\inC(\inn_1 \> x)$.
+Here we use that $f \> n \> x$ is defined to be $\inC(\inn_1 \> x)$.
 Since they are definitionally equal, we can just use the path $\refl$.
 
-For the other cases, we take a look at $c_{\rec}' \> y$.
+For the other cases, we take a look at $c_{\rec}' \> y$, and for $y$ we assume that $h_1(\inn_1(\inC \> y)) = h_1(H_{\Con} \> (\inC \circ \inn_1) \> y)$.
+Note that at each level $h$ is defined using the eliminator of the coequalizer.
+This means that $h \> n \> (\inC \> (c_{\rec}' \> y))$ and $c_{Y, \rec}(h \> n \> (\inC \> y))$ are equal by definition, and thus we can make the following computations.
 \begin{equation*}
 \begin{split}
-h \> (n+1) \> (\inn_1(\inC \> (c_{\rec}' \> y))) 
-&\equiv h \> (n+1) \> (\inC \> (c_{\rec}' \> y))\\
-&\equiv h \> (n+1) \> (c_{\rec}' \> y)\\
-&\equiv c_{Y, \rec} (h \> n \> y)
+h_1 \> (\inn_1(\inC \> (c_{\rec}' \> y))) 
+&\equiv 
+h \> n \> (\inC \> (c_{\rec}' \> y))\\
+&
+= c_{Y, \rec} (h \> n \> (\inC \> y))
 \end{split}
@@
 \begin{split}
-h \> (n+1) \> (H_{\Con} \> (\inC \circ \inn_1) \> (c_{\rec}' \> y)) 
+h_1 \> (H_{\Con} \> (\inC \circ \inn_1) \> (c_{\rec}' \> y)) 
 &\equiv 
-h \> (n+1) \> (c_{\rec}' \> (f \> n \> y))
+h_1 \> (c_{\rec}' \> (H_{\Con} \> (\inC \circ \inn_1) \> y))
 \\
 &\equiv
-c_{Y, \rec} \> (h \> (n+1) \> (f \> n \> y)\\
+c_{Y, \rec} \> (h_1 \> (H_{\Con} \> (\inC \circ \inn_1) \> y))\\
+&=
+c_{Y, \rec} \> (h_1(\inn_1(\inC \> y)))\\
 &\equiv
-c_{Y, \rec} \> (h \> (n+1) \> (\inC(\inn_1 \> y)).
+c_{Y, \rec} \> (h \> n \> (\inC \> y)).
 \end{split}
@@
 
-By $\inl$ it gets mapped $\inl (c_{\rec}' \> x)$.
-Since $h(n+1)$ is defined as the pushout map, it maps $\inl (c_{\rec}' \> x)$ to $h \> (n+1) \> (c_{\rec}' \> x) \equiv c_{Y, \rec}(h \> n \> x)$.
-The map $H_{\Con} (f \> n)$ sends $c_{\rec}' \> x$ to $c_{\rec}' (f \> n \> x)$, and the dependent map $h$ sends it to $c_{Y, \rec}(h \> (n+1) \> (f \> x))$.
-Using the definition of the pushout map, this is equal to $c_{Y, \rec}(h \> n \> x)$
-Hence, this diagram commutes, and thus the first coherency is fine.
-The equality between the points is $\refl$ as they are definitionally equal.
-
-For the second coherency we need to check that
+For the second coherency we need to check that the paths $\ap \> h_2 \> (\ap \> (f \> n) \> (p_i \> x))$ and $\ap \> h_2 \> (p_i \> (f \> n \> x))$ are equal.
+Here we use several Lemmata, namely Lemma 2.2.2 from \cite{hottbook} and Lemma \ref{lem:pathext}.
+For the first path we can show that it is equal to $q_{Y, i} \> (h \> n \> x)$.
+\begin{equation*}
+\begin{split}
+\ap \> h_2 \> (\ap \> (f \> n) \> (p_i \> x))
+&\equiv
+\ap \> h_2 \> (\ap \> (\inC \circ \inn_1) \> (p_i \> x))\\
+&=
+\ap \> (h_2 \circ \inC) \> (\ap \> \inn_1 \> (p_i \> x))\\
+&=
+\ap \> h_1 \> (\ap \> \inn_1 \> (p_i \> x))\\
+&=
+\ap \> (h_1 \circ \inn_1) \> \> (p_i \> x)\\
+&=
+\ap \> (h \> n) \> \> (p_i \> x)\\
+&\equiv
+q_{Y, i} \> (h \> n \> x)
+\end{split}
+\end{equation*}
+Since $(h_2 \circ \inC) \> x \equiv h_1 \> x$ and $(h_1 \circ \inn_1) \> x \equiv h \> n \> x$, we can use the path $\refl$, and thus the transport is the identity.
+For the other path we can do the same.
+\begin{equation*}
+\begin{split}
+\ap \> h_2 \> (p_i \> (f \> n \> x))
+&\equiv
+q_{Y, i} \> (h_2 \> (f \> n \> x))\\
+&\equiv
+q_{Y, i} \> (h_2 \> (\inC \> \inn_1 \> x))\\
+&\equiv
+q_{Y, i} \> (h_1 \> (\inn_1 \> x))\\
+&\equiv
+q_{Y, i} \> (h \> n \> x)
+\end{split}
+\end{equation*}
 

### 2017-03-21 Paper/Paper.tex
Finished elimination rule and computation rule

@@
 \newcommand{\frec}[0]{\!\operatorname{rec}}
+\newcommand{\ind}[0]{\!\operatorname{ind}}
 \newcommand{\rec}[0]{\operatorname{rec}}
@@
 		A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} 
-		& H_{\rec}(F \> n) \ar[rr]^{\term \comp \inn_2} &
+		& H_{\rec}(F \> n) \ar[rr]^-{\term \comp \inn_2} &
 		& H_{\Con}(F \> n) \ar[r]^-{\inC}
@@
 
-To finish the proof, we need to show that $\com_*(\ap \> (\inc \> n) \> (\glueC \> x)) = \ap \> (\inc \> (n+1)) \> (\glueC \> ((B_i \>(f \>n)) \> x))$.
+To finish the proof, we need to show that 
+\[
+(\com \> n \> x)_*(\ap \> (\inc \> n) \> (\glueC \> x)) = \ap \> (\inc \> (n+1)) \> (\glueC \> ((B_i \>(f \>n)) \> x)).
+\]
 This follows from the following computation.
@@
 \subsection{Elimination Rule}
-For the next step we define the right eliminator for $\hocolim \> F \> f$, so suppose that we are given
+For the next step we define the right eliminator for $\hocolim \> F \> f$, so suppose that we are given the following data
 \[
@@
 Then we need to give an element of the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$ for which we take $c_{Y,\rec} \> (A_{\rec} \> g \> x) \> y$.
+We will often leave the argument $A_{\rec} \> g \> x$ implicit.
 
@@
 &\equiv 
-h_1 \> (\inn_1(\inC \> (\inn_1 \> y))) \\
-&\equiv 
-h_1 \> (\inn_1(f \> n \> y))\\
-&\equiv 
 h_1 \> (\inn_1(\inC(\inn_1 \> y))),
@@
 \end{equation*}
-Here we use that $f \> n \> x$ is defined to be $\inC(\inn_1 \> x)$.
 Since they are definitionally equal, we can just use the path $\refl$.
@@
 More concretely, we need to show that $\inc \> n \> x$ and $\inc \> (n+1) \> (f \> x)$ are mapped to the same element.
-The map $f : F \> n \rightarrow F(n + 1)$ is defined by the pushout as follows
+The map $f : F \> n \rightarrow F(n + 1)$ is defined by the elimination rule of the coequalizer as follows
 \[
@@
 {
-	(\two \times B_i \> (F(n+1))) + H_{\Con} \>  (F \> n) \ar[d]_{\overline{t_i} + \overline{r_i} + H_{\Con} \> f} \ar[rr]^-{\delta + \inl} & & (I^1 \times B_i \> (F(n+1))) + F(n+1)  \ar[d]^{\inr}\\
-	H_{\Con} \> (F(n+1)) \ar[rr]_{\inl} & & F(n+2)
+	F \> n \ar[r]^-{\inn_1} & H_{\Con} \> (F \> n) \ar[r]^-{\inC} & \ldots \ar[r]^-{\inC} & F(n+1)
 }
 \]
-Since the map to $Y$ was defined as the pushout map, it will commute automatically.
+Since the map to $Y$ was defined via the universal property of the coequalizer, it will commute automatically.
+The commutativity is given by the computation rule of the coequalizer.
 
 All in all, we have acquired a map $\prod (x : \hocolim \> F \> f), Y \> x$, and this way we defined the right eliminator for $\hocolim \> F \> f$.
-We shall call the eliminator $H\frec$.
+We shall call the eliminator $H\ind$.
 
@@
 Lastly, we show that this eliminator also satisfies the computation rules.
-First, we prove that for each $t : A_{\rec}(\hocolim \> F \> f)$ that $H\frec(c_{\rec} \> t) \equiv f_i \> t \> (\overline{A_{\rec}} \> H\frec \> t)$.
+First, we prove that for each $t : A_{\rec}(\hocolim \> F \> f)$ that $H\ind(c_{\rec} \> t) \equiv f_i \> t \> (\overline{A_{\rec}} \> H\ind \> t)$.
 Again we use that colimits commute with polynomials.
@@
 Let $n : \mathbb{N}$ and $x : A_{\rec}(F \> n)$.
-Then by the computation rules we have
+Now we can perform the computations in an intermediate stage of the construction, and using the computation rules we get
 \begin{equation*}
 \begin{split}
-H\frec(c_{\rec} \> x) 
-&\equiv H\frec(\inc \> (n+1) \> (c_{\rec}' x)) \\
-&\equiv c_{Y,\rec} \> (A_{\rec} \> (\inc \> n) \> x) \> (\overline{A} \> H\frec \> x)\\
+H\ind(c_{\rec} \> (\inc \> n \> x)) 
+&\equiv H\ind(\inc \> (n+1) \> (c_{\rec}' x)) \\
+&\equiv c_{Y,\rec} \> (A_{\rec} \> (\inc \> n) \> x) \> (\overline{A} \> H\ind \> x)
 \end{split}
@@
 This is logical, because it is proven all $x : A_{\rec}(F \> n)$.
-However, for closed terms, we have a definitional equality.
-This is because $c_{\nonrec} \> a$ for $a : A_{\nonrec}$ is defined to be$\inc \> 0 \> (c_{\nonrec}' \> a)$.
+However, for terms built from $c_{\nonrec}$ and $c_{\rec}$, we have a definitional equality.
+This is because $c_{\nonrec} \> a$ for $a : A_{\nonrec}$ is defined to be $\inc \> 0 \> (c_{\nonrec}' \> a)$.
 All the closed terms are thus inhabitants of some $F \> n$, and since at every step the equalities are definitional, we can conclude that for closed terms the equality is definitional.
@@
 \begin{split}
-\apd \> H\frec \> (p_i \> (\inc \> n \> x))
-&\equiv \apd \> H\frec \> (\apd \> (\inc (n+1)) \> (\inr \> x))\\
-&= \apd \> (H\frec \comp  \> \inc (n+1)) \> (\inr \> x))\\
-&\equiv q_i \> (H\frec x)
+\apd \> H\ind \> (p_i \> (\inc \> n \> x))
+&\equiv \apd \> H\ind \> (\ap \> (\inc \> (n+1)) \> \glueC \> x)\\
+&= \apd \> (H\ind \comp  \> \inc (n+1)) \> (\glueC \> x)\\
+&= \apd \> (h \> n) \> (\glueC \> x)\\
+&\equiv q_i \> (B_i \> H\frec \> x)
 \end{split}
@@
 \begin{proof}
-This follows from path induction on $e$.
-In the case $e$ happens to be $\refl$, then $(e \> x)_*$ is $\idmap$.
+This follows from path induction on $e \> x$.
+In the case $e \> x$ happens to be $\refl$, then $(e \> x)_*$ is $\idmap$.
 Then the desired path is just $\refl$.

### 2017-03-21 Paper/Paper.tex
Fix affiliation, remove files that do not belong to git repo.
A git repository should contain *only source code*.
Label Definition 3.

@@
 \author[2]{Niels van der Weide}
-\affil[1]{Department of Mathematics and Physics, University of Ljubljana, Ljubljana, Slovenia\\
+\affil[1]{Faculty of Mathematics and Physics, University of Ljubljana, Ljubljana, Slovenia\\
   \texttt{Andrej.Bauer@andrej.com}}
@@
   \texttt{nweide@cs.ru.nl}}
-\authorrunning{A. Bauer and N. van der Weide} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
+\authorrunning{A.\ Bauer and N.\ van der Weide} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
 
@@
 
-\newcommand{\Boperator}[1]{\mathrm{\mathbf{#1}}}
+\newcommand{\Boperator}[1]{\mathsf{#1}}
 \newcommand{\comment}[1]{-- #1 --}
@@
 Higher inductive types (HITs) generalize normal inductive types by allowing constructors for both points and paths, rather than just for the points.
-While an inductive type is freely generated from a signature, a higher inductive type is freely generated from a signature with some equations.
+While an inductive type is freely generated from a signature, a higher inductive type is freely generated from a signature together with constructors for equations.
 Numerous examples and definitions of such types have already been given in the literature \cite{altenkirch2016quotient,awodey2012inductive,basoldhigher,sojakova2015higher,hottbook}, but a definition with a good metatheory is still lacking.
@@
 \begin{definition}
+\label{def:constructor-term}
 Given is a function $c : A \> T \rightarrow T$.
@@
 
-\bibliography{lipics-v2016-sample-article}
+\bibliography{Paper}
 

### 2017-03-22 Paper/Paper.tex
Fixed def:constructor-term
Fixed lemma 13.

@@
 
+\newcommand{\fpath}[0]{\> @ \>}
 \newcommand{\conc}[0]{\bullet}
@@
 \label{def:constructor-term}
-Given is a function $c : A \> T \rightarrow T$.
+Given is a function $c : A \> T \rightarrow T$ with $A$ polynomial and $T$ a type.
 Then we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F \> T \Vdash t : G \> T$ can be derived using the following rules.
@@
 \begin{proof}
-We define $f : A \rightarrow \hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id})$ to be $\inc \> 0$.
+We define the map $f : A \rightarrow \hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id})$
+to be $\inc \> 0$.
 Next we define $g : \hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id}) \rightarrow A$ by $\hocolim$ recursion.
@@
 \label{lem:pathext}
-Given are types $A, B$ and functions $f, g : A \rightarrow B$ such that we have an inhabitant $e : \prod (x : A), f \> x = g \> x$.
-Furthermore, assume that we have paths $q : \prod (x : A), l = r$ where $l$ and $r$ are terms using $x : A$ as free variable.
-Then for all $x : A$ we have a path
+Given are types $A, B$ and functions $f, g : A \rightarrow B$ such that we have an inhabitant $e : f = g$.
+Furthermore, assume that we have a path $p : x = y$ where $x$ and $y$ are terms of type $A$.
+Then for all we have a path
 \[
-(e \> x)_* \> (\ap \> f \> (q \> x)) = \ap \> g \> (q \> x).
+e_* \> (\ap \> f \> p) = \ap \> g \> p.
+\]
+All in all, we have an inhabitant of the type
+\[
+\prod (f, g : A \rightarrow B) (e : f = g) (x, y : A) (p : x = y), e_* \> (\ap \> f \> p) = \ap \> g \> p
+\]
+where $A, B : \Type$.
+\end{lemma}
+
+\begin{proof}
+Since this statement is universally quantified over $p$, we can apply path induction.
+Assuming $p$ to be $\refl$, the map $e_*$ is the identity, and in that case it holds.
+Hence, it follows by path induction.
+\end{proof}
+
+\begin{lemma}
+\label{lem:funTrans}
+Again we are given types $A, B$, functions $f, g : A \rightarrow B$, an inhabitant $e : f = g$, and a path $p : f \> x = f \> y$ with $x, y : A$.
+Then we have a path 
+\[
+e_* \> p = (e \fpath x)^{-1} \conc p \conc (e \fpath x)
+\]
+Formally, this means that for $A, B : \Type$ we have an inhabitant of the type
+\[
+\prod (f, g : A \rightarrow B) (e : f = g) (x, y : A) (p : f \> x = f \> y), e_* \> p = (e \fpath x)^{-1} \conc p \conc (e \fpath y).
 \]
@@
 \begin{proof}
-This follows from path induction on $e \> x$.
-In the case $e \> x$ happens to be $\refl$, then $(e \> x)_*$ is $\idmap$.
-Then the desired path is just $\refl$.
+Again we use path induction on $e$, so we assume that $e = \refl$.
+Then $e \fpath x = \refl$ and $e \fpath y = \refl$, so the right side is equal to $p$.
+Also, in this case $e_*$ is the identity map, so the left side also is $p$.
 \end{proof}

### 2017-03-22 Paper/Paper.tex
Added part on function extensionality required for lemma 13 and 14

@@
 
-\newcommand{\fpath}[0]{\> @ \>}
+\newcommand{\fpath}[0]{\> \Box \>}
 \newcommand{\conc}[0]{\bullet}
@@
 
+\newcommand{\FE}[0]{\Boperator{FE}}
+\newcommand{\funext}[0]{\Boperator{FunExt}}
 \newcommand{\coeq}[0]{\Boperator{coeq}}
@@
 
+Lastly, we need function extensionality for the proof.
+Let us first introduce some notation.
+
+\begin{definition}
+Let $A, B$ be types, let $f, g : A \rightarrow B$ be maps, and let $x : A$ be a point of $A$.
+Then for all $e : f = g$ we define a path $e \fpath x : f \> x = g \> x$ using path induction which sends $\refl$ to $\refl$.
+\end{definition}
+
+\begin{definition}
+Given are types $A, B$ and two maps $f, g : A \rightarrow B$.
+Then we define the type $\funext$, of which the inhabitants represent proofs of function extensionality, as follows
+\[
+\funext = (\prod (x : A), f \> x = g \> x) \rightarrow f = g.
+\]
+\end{definition}
+
+We will assume that we have an inhabitant $\FE : \funext$ such that for $p : \prod (x : A), f \> x = g \> x$ and $x : A$ we have
+\[
+(\FE \> p) \fpath x = p \> x.
+\]
+In homotopy type theory function extensionality can be proved by assuming univalence \cite{UnivalenceFE} or by assuming the existence of an interval object \cite{IntervalFE}.
+
 \section{The Approximator}

### 2017-03-22 Paper/Paper.tex
Added small abstract

@@
 \begin{abstract}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Praesent convallis orci arcu, eu mollis dolor.
-Aliquam eleifend suscipit lacinia.
-Maecenas quam mi, porta ut lacinia sed, convallis ac dui.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Suspendisse potenti.
+We show that all higher inductive types can be constructed from coequalizers, path coequalizers and homotopy colimits.
+The proof is inspired by Ad\'amek's theorem which constructs inductive types as a colimit of a functor.
+This way one can reason about all higher inductive types by instead studying a small number of examples.
  \end{abstract}

### 2017-03-27 Paper/Paper.tex
Fix affiliation and acknowledgements.

@@
 % Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{The Three-HITs Theorem\footnote{This work was partially supported by COST Action CA15123.}}
+\title{The Three-HITs Theorem}
 \titlerunning{The Three-HITs Theorem} %optional, in case that the title is too long; the running title should fit into the top page column
@@
 %% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
-\author[1]{Andrej Bauer}
-\author[2]{Niels van der Weide}
-\affil[1]{Faculty of Mathematics and Physics, University of Ljubljana, Ljubljana, Slovenia\\
+\author[1]{Andrej Bauer\thanks{
+The author acknowledges the financial support from the Slovenian Research Agency (research core funding No.~P1-0294) at Institute of Mathematics, Physics and Mechanics, Ljubljana, Slovenia.
+This material is based upon work supported by the Air Force Office of Scientific Research, Air Force Materiel Command, USAF under Award No.~FA9550-14-1-0096.}}
+\author[2]{Niels van der Weide\thanks{This work was partially supported by EU COST Action Eutypes (CA15123).}}
+\affil[1]{University of Ljubljana, Slovenia\\
   \texttt{Andrej.Bauer@andrej.com}}

### 2017-03-27 Paper/Paper.tex
Include definitions of P[A], P[f], and lifting.
It is bad manners to refer the reader to some other paper for something
that is constantly used everywhere in the paper. So I included these.

@@
 
+% In order to avoid macro pollution, we should comment each macro
+% so that we know what it is about
+
+\newcommand{\tyFont}[1]{\textsf{#1}} % the font used to display types
+\newcommand{\termFont}[1]{\textsf{#1}} % the font used to term constants
+\newcommand{\nat}{\tyFont{N}} % the type of natural numbers
+\newcommand{\lift}[1]{\overline{#1}} % the lifting of a type family by a polynomial
+\newcommand{\defeq}{\mathrel{{:}{\equiv}}} % definitional equality
+\newcommand{\idmap}[1]{\termFont{id}_{#1}} % identity map
+\newcommand{\inl}[1]{\termFont{inl}\,#1} % left inclusion into a sum
+\newcommand{\inr}[1]{\termFont{inr}\,#1} % right inclusion into a sum
+
+\newcommand{\dprod}[1]{{\textstyle\prod_{#1}}\,} % dependent product
+\newcommand{\dsum}[1]{{\textstyle\sum_{#1}}\,} % dependent sum
+
+% Below are macros which have not been documented and are possibly
+% unused (probably not)
+
 \newcommand{\Boperator}[1]{\mathsf{#1}}
@@
 
-\newcommand{\idmap}[0]{\Boperator{Id}}
 \newcommand{\refl}[0]{\Boperator{refl}}
@@
 \newcommand{\seg}[0]{\Boperator{seg}}
-\newcommand{\inl}[0]{\Boperator{inl}}
-\newcommand{\inr}[0]{\Boperator{inr}}
 \newcommand{\glue}[0]{\Boperator{glue}}
@@
 
-\section{Preliminaries}
+\section{A definition of HITs}
 \label{sec:prelims}
-Let us briefly recall the scheme of higher inductive types which we shall use \cite{basoldhigher}.
-First of all, we need \emph{polynomial functors}.
+
+In this section we provide the definitions of higher inductive types that we shall
+consider. We recall the scheme for specifying higher inductive types
+from~\cite{basoldhigher}.
+
 \begin{definition}
-Let $X$ be a variable.
-Then a \emph{polynomial} is given by the following grammar.
-\[
-F, G ::= B \ | \ X \ | \ F \times G \ | \ F + G
-\]
-where $B : \Type$.
+  A \emph{polynomial (expression)} in a type variable $X$ is a built inductively from the
+  variable $X$, type constants~$C$, binary products $\times$, and binary sums $+$.
 \end{definition}
-A possible extension would be to use arbitrary containers as in \cite{abbott2005containers}, but we shall refrain to do so.
-With that extension the given proof requires the axiom of choice which generally does not hold in type theory.
-One can prove that polynomials are functors, and that given a type family $Y : T \rightarrow \Type$ and a polynomial $F$, we get a lift $\bar{F} : F \> T \rightarrow \Type$.
-We will write $F \> f$ to denote the application of a polynomial $F$ to a map $f$.
-Also, given a dependent function $f : \prod (x : T), Y \> x$, one can define $\bar{F} \> f : \prod (x : H \> T), \bar{H} \> Y \> x$.
-Precise definitions of these are given in \cite{basoldhigher}.
+
+For example, if $\nat$ is the type of natural numbers, the expression
+$(X + \nat) \times X$ is a polynomial expression in~$X$. We write $P[X]$ to indicate a
+polynomial in variable $X$. Given a type $A$, we may substutute $A$ for $X$ to obtain a
+type $P[A]$, as follows:
+%
+\begin{align*}
+  X[A] &\defeq A, &
+  (P_1 \times P_2)[A] &\defeq P_1[A] \times P_2[A], \\
+  C[A] &\defeq C, &
+  (P_1 + P_2)[A] &\defeq P_1[A] + P_2[A].
+\end{align*}
+%
+In a similar fashion a map $f \> A \to B$ is transformed to a map $P[f] : P[A] \to P[B]$:
+%
+\begin{align*}
+  X[f] &\defeq f, &
+  (P_1 \times P_2)[f] \, (x,y) &\defeq (P_1[f]\, x, P_2[f] \, y), \\
+  C[f] &\defeq \idmap{C}, &
+  (P_1 + P_2)[f](\inl{x}) &\defeq \inl{(P_1[f]\,x)}, \\
+  & &
+  (P_1 + P_2)[f](\inr{y}) &\defeq \inr{(P_2[f]\,y)}.
+\end{align*}
+%
+Somewhat less obviously, a polynomial acts on a type family $B : A \to \Type$ to
+give its lifting $\lift{P}[B] : P[A] \to \Type$,
+%
+\begin{align*}
+  \lift{X}[B] \, u &\defeq B\,u, &
+  \lift{P_1 \times P_2}[B] \, u \defeq (\lift{P_1}[B]\,u) \times (\lift{P_2}[B]\,u), \\
+  \lift{C}[B] \, u &\defeq C, &
+  \lift{P_1 + P_2}[B] \, (\inl{u})\defeq \lift{P_1}[B]\,u, \\
+  & &
+  \lift{P_1 + P_2}[B] \, (\inr{u})\defeq \lift{P_2}[B]\,u,
+\end{align*}
+%
+while a map $f \> \dprod{x \> A} B_1\,x \to B_2\,x$ lifts to
+$\lift{P}[f] \> \dprod{u : P[A]} \lift{P}[B_1]\,u \to \lift{P}[B_2]\,u$:
+%
+\begin{align*}
+  \lift{X}[f] \, u &\defeq f \, u &
+  \lift{P_1 \times P_2}[f] \, (u_1, u_2) &\defeq (\lift{P_1}[f]\,u_1, \lift{P_2}[f]\,u_2) \\
+  \lift{C}[f] \, u &\defeq u &
+  \lift{P_1 + P_2}[f] \, (\inl{u})\defeq \lift{P_1}[f]\,u, \\
+  & &
+  \lift{P_1 + P_2}[f] \, (\inr{u})\defeq \lift{P_2}[f]\,u.
+\end{align*}
+%
+There is of course a strong analogy between the action of $P[X]$ and a polynomial functor,
+but we hesitate to call $P[X]$ a functor as there is no category to speak of, and in any
+case the manipulations we have just described are syntactic.
 
@@
 \section{Conclusion and Further Work}
+
+MOVED FROM BEGINNING: A possible extension would be to use arbitrary containers as in \cite{abbott2005containers}, but we shall refrain to do so.
+With that extension the given proof requires the axiom of choice which generally does not hold in type theory.
+
 Higher inductive types can thus be constructed if we have the interval, homotopy pushout and homotopy colimits.

### 2017-03-27 Paper/Paper.tex
Replace `\>` with `:`.
I find `\>` much harder to type, it's not clear what the advantage over `:` is, and also
`\>` does not work in indices, e.g., `\prod_{x \> A}`, at least for me.

@@
 
-\newcommand{\fpath}[0]{\> \Box \>}
+\newcommand{\fpath}[0]{: \Box :}
 \newcommand{\conc}[0]{\bullet}
@@
 %
-In a similar fashion a map $f \> A \to B$ is transformed to a map $P[f] : P[A] \to P[B]$:
+In a similar fashion a map $f : A \to B$ is transformed to a map $P[f] : P[A] \to P[B]$:
 %
@@
 %
-while a map $f \> \dprod{x \> A} B_1\,x \to B_2\,x$ lifts to
-$\lift{P}[f] \> \dprod{u : P[A]} \lift{P}[B_1]\,u \to \lift{P}[B_2]\,u$:
+while a map $f : \dprod{x : A} B_1\,x \to B_2\,x$ lifts to
+$\lift{P}[f] : \dprod{u : P[A]} \lift{P}[B_1]\,u \to \lift{P}[B_2]\,u$:
 %
@@
 \label{def:constructor-term}
-Given is a function $c : A \> T \rightarrow T$ with $A$ polynomial and $T$ a type.
-Then we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F \> T \Vdash t : G \> T$ can be derived using the following rules.
+Given is a function $c : A : T \rightarrow T$ with $A$ polynomial and $T$ a type.
+Then we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F : T \Vdash t : G : T$ can be derived using the following rules.
 \begin{gather*}
@@
         \AxiomC{$T$ does not occur in $B$}
-        \BinaryInfC{$x:F \> T \Vdash t : B$}
+        \BinaryInfC{$x:F : T \Vdash t : B$}
         \bottomAlignProof
@@
         \AxiomC{}
-        \UnaryInfC{$x : F \> T \Vdash x : F \> T$}
+        \UnaryInfC{$x : F : T \Vdash x : F : T$}
         \bottomAlignProof
@@
         \quad
-        \AxiomC{$x : F \> T \Vdash r : A \> T$}
-        \UnaryInfC{$x : F \> T \Vdash c \> r : T$}
+        \AxiomC{$x : F : T \Vdash r : A : T$}
+        \UnaryInfC{$x : F : T \Vdash c : r : T$}
         \bottomAlignProof
@@
         \AxiomC{$j \in \{1, 2\}$}
-        \AxiomC{$x : F \> T \Vdash r : G_1 \> T \times G_2 \> T$}
-        \BinaryInfC{$x : F \> T \Vdash\pi_j \> r : G_j \> T$}
+        \AxiomC{$x : F : T \Vdash r : G_1 : T \times G_2 : T$}
+        \BinaryInfC{$x : F : T \Vdash\pi_j : r : G_j : T$}
         \bottomAlignProof
@@
         \AxiomC{$j \in \{1, 2\}$}
-        \AxiomC{$x : F \> T \Vdash r_j : G_j$}
-        \BinaryInfC{$x : F \> T \Vdash (r_1, r_2) : G_1 \> T\times G_2 \> T$}
+        \AxiomC{$x : F : T \Vdash r_j : G_j$}
+        \BinaryInfC{$x : F : T \Vdash (r_1, r_2) : G_1 : T\times G_2 : T$}
         \bottomAlignProof
@@
         \AxiomC{$j \in \{1, 2\}$}
-        \AxiomC{$x : F \> T \Vdash r : G_j \> T$}
-        \BinaryInfC{$x : F \> T : \inn_j \> r : G_1 \> T + G_2 \> T$}
+        \AxiomC{$x : F : T \Vdash r : G_j : T$}
+        \BinaryInfC{$x : F : T : \inn_j : r : G_1 : T + G_2 : T$}
         \bottomAlignProof
@@
 Inductive $H$ :=
-| $c$ : $A \> H \rightarrow H$
-| $p_i$ : $\prod (x : B_i \> H), t_i = r_i$ $\quad (i = 1, \ldots, m)$
+| $c$ : $A : H \rightarrow H$
+| $p_i$ : $\prod (x : B_i : H), t_i = r_i$ $\quad (i = 1, \ldots, m)$
 \end{lstlisting}
-where $A$ and each $B_i$ are polynomials, and each $t_i$ and $r_i$ are constructor terms over $c$ of type $H$ with $x : B_i \> H$ as variable.
+where $A$ and each $B_i$ are polynomials, and each $t_i$ and $r_i$ are constructor terms over $c$ of type $H$ with $x : B_i : H$ as variable.
 \end{definition}
@@
 \begin{definition}
-Given is a constructor $c : A \> H \rightarrow H$, a type family $Y : H \rightarrow \Type$, and a term $f : \prod (x: A \> H), \bar{A} \> Y \> x \rightarrow  Y(c \> x)$.
-For a constructor term $F \> H \Vdash r : G \> H$ we define the \emph{lift $\dak{r}$ of $r$} with type 
+Given is a constructor $c : A : H \rightarrow H$, a type family $Y : H \rightarrow \Type$, and a term $f : \prod (x: A : H), \bar{A} : Y : x \rightarrow  Y(c : x)$.
+For a constructor term $F : H \Vdash r : G : H$ we define the \emph{lift $\dak{r}$ of $r$} with type 
 $
-x : F \> H, h_x : \bar{F} \> Y \> x \vdash \dak{r} : \bar{G} \> Y \> r
+x : F : H, h_x : \bar{F} : Y : x \vdash \dak{r} : \bar{G} : Y : r
 $
@@
                 & \dak{x} & := h_x &
-                \dak{c_i \> r} & := f_i \> r \> \dak{r}\\
-                \dak{\pi_j \> r} & := \pi_j \> \dak{r} &
+                \dak{c_i : r} & := f_i : r : \dak{r}\\
+                \dak{\pi_j : r} & := \pi_j : \dak{r} &
                 \dak{(r_1, r_2)} & := (\dak{r_1}, \dak{r_2})
-                & \dak{\inn_j \> r} & := \dak{r}
+                & \dak{\inn_j : r} & := \dak{r}
         \end{align*}
@@
 \[
-c : A \> H \rightarrow H,
-\]
-\[
-p_i : \prod (x : B_i \> H), t_i = r_i.
+c : A : H \rightarrow H,
+\]
+\[
+p_i : \prod (x : B_i : H), t_i = r_i.
 \]
@@
         \noLine
-        \UnaryInfC{$\vdash f : \prod (x : A \> H), \bar{A} \> Y \> x \rightarrow Y \> (c \> x)$}
+        \UnaryInfC{$\vdash f : \prod (x : A : H), \bar{A} : Y : x \rightarrow Y : (c : x)$}
 %       \noLine
-        \AxiomC{$\vdash q_i : \prod (x : B_i \> H) (h_x : \bar{B}_i \> Y \> x), \hatt_i =_{p_j \, x} \hatr_j$}
-        \BinaryInfC{$\vdash H\frec(f, q_1, \ldots, q_n) : \prod (x : H), Y \> x$}
+        \AxiomC{$\vdash q_i : \prod (x : B_i : H) (h_x : \bar{B}_i : Y : x), \hatt_i =_{p_j \, x} \hatr_j$}
+        \BinaryInfC{$\vdash H\frec(f, q_1, \ldots, q_n) : \prod (x : H), Y : x$}
         \DisplayProof
@@
 Let us abbreviate $H\frec(f, q_1, \ldots, q_n)$ by $H\frec$.
-The type $H$ also has computation rules for each point $t : A \> H$
-\begin{equation*}
-H\frec \> (c \> t) \equiv f \> t \> (\bar{A} \> H\frec \> t),
-\end{equation*}
-and for each $a : B_i \> H$
-\begin{equation*}
-\apd \> H\frec \> (p_i \> a) \equiv q_i \> a \> (\bar{B}_i \> H\frec \> a).
+The type $H$ also has computation rules for each point $t : A : H$
+\begin{equation*}
+H\frec : (c : t) \equiv f : t : (\bar{A} : H\frec : t),
+\end{equation*}
+and for each $a : B_i : H$
+\begin{equation*}
+\apd : H\frec : (p_i : a) \equiv q_i : a : (\bar{B}_i : H\frec : a).
 \end{equation*}
@@
 Inductive $\coeq$ $(A, B : \Type)$ $(f, g : A \rightarrow B)$ :=
-| $\inC$ : $B \rightarrow \coeq \> A \> B \> f \> g$
-| $\glueC$ : $\prod (a : A), \inC \> (f \> a) = \inC \> (g \> a)$
+| $\inC$ : $B \rightarrow \coeq : A : B : f : g$
+| $\glueC$ : $\prod (a : A), \inC : (f : a) = \inC : (g : a)$
 \end{lstlisting}
@@
 \begin{equation*}
-        \AxiomC{$\vdash Y : \coeq \> A \> B \> f \> g \rightarrow \Type$}
+        \AxiomC{$\vdash Y : \coeq : A : B : f : g \rightarrow \Type$}
         \noLine
-        \UnaryInfC{$\vdash i_Y : \prod (b : B), Y \> (\inC \> b)$}
+        \UnaryInfC{$\vdash i_Y : \prod (b : B), Y : (\inC : b)$}
         %       \noLine
-        \AxiomC{$\vdash g_Y : \prod (a : A), \glueC_*(i_Y \> (f \> a)) = i_Y \> (g \> a)$}
-        \BinaryInfC{$\vdash \coeq\frec(i_Y, g_Y) : \prod (x : \coeq \> A \> B \> f \> g), Y \> x$}
+        \AxiomC{$\vdash g_Y : \prod (a : A), \glueC_*(i_Y : (f : a)) = i_Y : (g : a)$}
+        \BinaryInfC{$\vdash \coeq\frec(i_Y, g_Y) : \prod (x : \coeq : A : B : f : g), Y : x$}
         \DisplayProof
@@
 Inductive $\pcoeq$ $(A, B : \Type)$ $(p : A \rightarrow \sum (b_1, b_2 : B), (b_1 = b_2) \times (b_1 = b_2))$ :=
-| $\inP$ : $B \rightarrow \pcoeq \> A \> B \> f \> g$
-| $\glueP$ : $\prod (a : A), \ap \> \inC \> (\pi_1(\pi_3(p \> a))) = \ap \> \inC \> (\pi_2(\pi_3(p \> a)))$
+| $\inP$ : $B \rightarrow \pcoeq : A : B : f : g$
+| $\glueP$ : $\prod (a : A), \ap : \inC : (\pi_1(\pi_3(p : a))) = \ap : \inC : (\pi_2(\pi_3(p : a)))$
 \end{lstlisting}
-We will abbreviate $p_i \> a = \pi_i(\pi_3(p \> a))$ for $i = 1, 2$.
+We will abbreviate $p_i : a = \pi_i(\pi_3(p : a))$ for $i = 1, 2$.
 Note that this type has 2-paths, so it does not follow the given syntax.
@@
 \begin{equation*}
-        \AxiomC{$\vdash Y : \pcoeq \> A \> B \> f \> g \rightarrow \Type$}
+        \AxiomC{$\vdash Y : \pcoeq : A : B : f : g \rightarrow \Type$}
         \noLine
-        \UnaryInfC{$\vdash i_Y : \prod (b : B), Y \> (\inP \> b)$}
+        \UnaryInfC{$\vdash i_Y : \prod (b : B), Y : (\inP : b)$}
         %       \noLine
-        \AxiomC{$\vdash g_Y : \prod (a : A), \apd \> i_Y \> (p_1 \> a) = \apd \> i_Y \> (p_2 \> a)$}
-        \BinaryInfC{$\vdash \pcoeq\frec(i_Y, g_Y) : \prod (x : \pcoeq \> A \> B \> f \> g), Y \> x$}
+        \AxiomC{$\vdash g_Y : \prod (a : A), \apd : i_Y : (p_1 : a) = \apd : i_Y : (p_2 : a)$}
+        \BinaryInfC{$\vdash \pcoeq\frec(i_Y, g_Y) : \prod (x : \pcoeq : A : B : f : g), Y : x$}
         \DisplayProof
@@
 \begin{lstlisting}
-Inductive $\hocolim$ $(F : \mathbb{N} \rightarrow \Type)$ $(f : \prod (n : \mathbb{N}, F \> n \rightarrow F(n+1)))$ :=
-| $\inc$ : $\prod (n : \mathbb{N}), F \> n \rightarrow$ $\hocolim$ $F$ $f$
-| $\com$ : $\prod (n : \mathbb{N}) (x : F \> n), \inc \> n \> x = \inc \> (n+1) \> (f \> n \> x)$
+Inductive $\hocolim$ $(F : \mathbb{N} \rightarrow \Type)$ $(f : \prod (n : \mathbb{N}, F : n \rightarrow F(n+1)))$ :=
+| $\inc$ : $\prod (n : \mathbb{N}), F : n \rightarrow$ $\hocolim$ $F$ $f$
+| $\com$ : $\prod (n : \mathbb{N}) (x : F : n), \inc : n : x = \inc : (n+1) : (f : n : x)$
 \end{lstlisting}
@@
 \begin{equation*}
-        \AxiomC{$\vdash Y : \hocolim \> F \> f \rightarrow \Type$}
+        \AxiomC{$\vdash Y : \hocolim : F : f \rightarrow \Type$}
         \noLine
-        \UnaryInfC{$\vdash i_Y : \prod (n : \mathbb{N}) (x : F \> n), Y \> (\inc \> n \> x)$}
+        \UnaryInfC{$\vdash i_Y : \prod (n : \mathbb{N}) (x : F : n), Y : (\inc : n : x)$}
         \noLine
-        \UnaryInfC{$\vdash c_Y : \prod (n : \mathbb{N}) (x : F \> n), \com_*(i_Y \> n \> x) = i_Y \> (n+1) \> (f \> n \> x)$}
-        \UnaryInfC{$\vdash \hocolim\frec(i_Y, c_Y) : \prod (x : \hocolim \> F \> f), Y \> x$}
+        \UnaryInfC{$\vdash c_Y : \prod (n : \mathbb{N}) (x : F : n), \com_*(i_Y : n : x) = i_Y : (n+1) : (f : n : x)$}
+        \UnaryInfC{$\vdash \hocolim\frec(i_Y, c_Y) : \prod (x : \hocolim : F : f), Y : x$}
         \DisplayProof
@@
 Let $A, B$ be types, let $f, g : A \rightarrow B$ be maps, and let $x : A$ be a point of $A$.
-Then for all $e : f = g$ we define a path $e \fpath x : f \> x = g \> x$ using path induction which sends $\refl$ to $\refl$.
+Then for all $e : f = g$ we define a path $e \fpath x : f : x = g : x$ using path induction which sends $\refl$ to $\refl$.
 \end{definition}
@@
 \[
-\funext = (\prod (x : A), f \> x = g \> x) \rightarrow f = g.
+\funext = (\prod (x : A), f : x = g : x) \rightarrow f = g.
 \]
@@
 
-We will assume that we have an inhabitant $\FE : \funext$ such that for $p : \prod (x : A), f \> x = g \> x$ and $x : A$ we have
-\[
-(\FE \> p) \fpath x = p \> x.
+We will assume that we have an inhabitant $\FE : \funext$ such that for $p : \prod (x : A), f : x = g : x$ and $x : A$ we have
+\[
+(\FE : p) \fpath x = p : x.
 \]
@@
 Before giving the definition, let us acquire inspiration by looking in more detail at how an inductive type is constructed.
-Such a type $T$ is defined by a constructor $c : A \> T \rightarrow T$ with $A$ polynomial.
+Such a type $T$ is defined by a constructor $c : A : T \rightarrow T$ with $A$ polynomial.
 Equivalently, we can define the type $T$ with a signature which is a polynomial functor $A$, and then by Ad\'amek's theorem $T$ is the following colimit.
@@
 {
-        \zero \ar[r] & A \> \zero  \ar[r] & A(A \> \zero) \ar[r] & \ldots
-}
-\]
-To understand what this does, let us assume that $A \> X = 1 + X$, so that $T = \mathbb{N}$.
+        \zero \ar[r] & A : \zero  \ar[r] & A(A : \zero) \ar[r] & \ldots
+}
+\]
+To understand what this does, let us assume that $A : X = 1 + X$, so that $T = \mathbb{N}$.
 This means we have two inclusions  $\xymatrix{1 \ar[r] & 1+X}$ and  $\xymatrix{X \ar[r] & 1+X}$, and we call them $0_C$ and $S_C$ respectively.
-At every step we formally add for each $x : X$ a successor $S_C \> x$, and we add $0_C$.
+At every step we formally add for each $x : X$ a successor $S_C : x$, and we add $0_C$.
 Repeatedly applying this construction to the empty type $\zero$ gives the natural numbers $\mathbb{N}$.
@@
 | $S$ : $\mathbb{N}_2 \rightarrow \mathbb{N}_2$
-| $p$ : $S(S \> 0) = 0$
+| $p$ : $S(S : 0) = 0$
 \end{lstlisting}
 We build a sequence $F$ of approximations.
-The first approximation just has a constructor $0$, and after that we add a constructor for $S \> 0$ to obtain the second approximation.
-Continuing this way, we ultimately arrive at the third approximation, which we call $F' \> 3$, where we found inhabitants $0$, $S \> 0$, and $S(S \> 0)$.
+The first approximation just has a constructor $0$, and after that we add a constructor for $S : 0$ to obtain the second approximation.
+Continuing this way, we ultimately arrive at the third approximation, which we call $F' : 3$, where we found inhabitants $0$, $S : 0$, and $S(S : 0)$.
 Now we can make the first identification, and to do so, we take the following homotopy pushout
@@
 {
-        \one + \one \ar[d]_{0 + S(S \> 0)} \ar[r]^-{\delta} & I^1 \ar[d]\\
-        F' \> 3\ar[r] & F \> 3
-}
-\]
-to obtain the actual third approximation $F \> 3$, and we continue our construction with that one.
+        \one + \one \ar[d]_{0 + S(S : 0)} \ar[r]^-{\delta} & I^1 \ar[d]\\
+        F' : 3\ar[r] & F : 3
+}
+\]
+to obtain the actual third approximation $F : 3$, and we continue our construction with that one.
 Note that to glue during the $n$th step, we need refer to elements from the $(n-2)$th step.
@@
 | $f$ : $H \rightarrow H$
-| $p$ : $\prod (n : \mathbb{N}), f^n \> 0 = 0$
+| $p$ : $\prod (n : \mathbb{N}), f^n : 0 = 0$
 \end{lstlisting}
@@
 | $c$ : $A_{\nonrec} \rightarrow H$
-| $c_{\rec}$ : $A_{\rec} \> H \rightarrow H$
-| $p_i$ : $\prod (x : B_i \> H), t_i = r_i$ $\quad (i = 1, \ldots, m)$
+| $c_{\rec}$ : $A_{\rec} : H \rightarrow H$
+| $p_i$ : $\prod (x : B_i : H), t_i = r_i$ $\quad (i = 1, \ldots, m)$
 \end{lstlisting}
@@
 Inductive $H_{\rec}$ $(P : \Type)$:=
-| $c_{\rec}'$ : $A_{\rec} \> P \rightarrow H_{\rec} \> P$
+| $c_{\rec}'$ : $A_{\rec} : P \rightarrow H_{\rec} : P$
 \end{lstlisting}
@@
 Inductive $H_{\Con}^n$ $(P : \Type)$:=
-| $\term$ : $P + H_{\rec} \> P + \ldots + H_{\rec}^n \> P \rightarrow H_{\Con}^n \> P$
+| $\term$ : $P + H_{\rec} : P + \ldots + H_{\rec}^n : P \rightarrow H_{\Con}^n : P$
 \end{lstlisting}
@@
 Note that this type is actually a labeled sum.
-This is because $H_{\rec} \> P$ is isomorphic to $A_{\rec} \> P$, and thus this $H_{\Con}^n \> P$ is actually $P + A_{\rec} \> P + \ldots + A_{\rec}^n \> P$.
+This is because $H_{\rec} : P$ is isomorphic to $A_{\rec} : P$, and thus this $H_{\Con}^n : P$ is actually $P + A_{\rec} : P + \ldots + A_{\rec}^n : P$.
 Hence, we do not need inductive types in general for the construction, but we just need to have sums and products.
 If $n$ is clear from the context, then we shall not write it down.
-From Lemma \ref{lem:constrTerm} we can conclude that we can interpret the constructor terms in $H_{\Con} \> P$
+From Lemma \ref{lem:constrTerm} we can conclude that we can interpret the constructor terms in $H_{\Con} : P$
 
@@
         \item Types $P, Q, R$;
-        \item A map $j_Q : H_{\Con} \> Q \rightarrow P$;
-        \item An inclusion $j_R : H_{\Con} \> R \rightarrow Q$;
-        \item Paths $p_Q : \prod (x : Q), j_Q(\overline{t_i} \> x) = j_Q(\overline{r_i} \> x)$;
-        \item Paths $p_R : \prod (x : R), j_R(\overline{t_i} \> x) = j_R(\overline{r_i} \> x)$.
+        \item A map $j_Q : H_{\Con} : Q \rightarrow P$;
+        \item An inclusion $j_R : H_{\Con} : R \rightarrow Q$;
+        \item Paths $p_Q : \prod (x : Q), j_Q(\overline{t_i} : x) = j_Q(\overline{r_i} : x)$;
+        \item Paths $p_R : \prod (x : R), j_R(\overline{t_i} : x) = j_R(\overline{r_i} : x)$.
 \end{itemize}
 The type $H_{\Approx}$ depends on the given data, but for clarity we will suppress it from the notation.
-We start with $H_{\Con} \> P$.
+We start with $H_{\Con} : P$.
 
 First, we need to guarantee that the added paths have the right endpoints.
-Note that we have two maps $\overline{t_i}, \overline{r_i} : B_i \> P \rightarrow H_{\Con} \> P$, and that gives the first coequalizer.
+Note that we have two maps $\overline{t_i}, \overline{r_i} : B_i : P \rightarrow H_{\Con} : P$, and that gives the first coequalizer.
 \[
@@
 {
-        B_i \> P \ar@<-.5ex>[r]_-{\overline{r_i}} \ar@<.5ex>[r]^-{\overline{t_i}} & H_{\Con} \> P \ar[r]^-{\inC_1} & C_1
+        B_i : P \ar@<-.5ex>[r]_-{\overline{r_i}} \ar@<.5ex>[r]^-{\overline{t_i}} & H_{\Con} : P \ar[r]^-{\inC_1} & C_1
 }
@@
 However, this is not exactly the type we want due to coherency issues.
-For example, in $P$ we have terms using $c_{\rec}$ at most $k$ times, so in $H_{\Approx} \> P$ we have duplicates of terms using $c_{\rec}$ less than $k$ times.
-
-Remember that we we have $j_Q : H_{\Con} \> Q \rightarrow P$.
+For example, in $P$ we have terms using $c_{\rec}$ at most $k$ times, so in $H_{\Approx} : P$ we have duplicates of terms using $c_{\rec}$ less than $k$ times.
+
+Remember that we we have $j_Q : H_{\Con} : Q \rightarrow P$.
 Now we define the type $C_2$ which is the coequalizer of the following two arrows.
@@
 {
-        H_{\Con} \> Q \ar@<-.5ex>[rrr]_-{H_{\Con} \> (j_Q \circ \inn_1)} \ar@<.5ex>[rrr]^-{\inn_1 \circ j_Q} & & & H_{\Con} \> P \ar[rr]^-{\inC_1} & & C_1
+        H_{\Con} : Q \ar@<-.5ex>[rrr]_-{H_{\Con} : (j_Q \circ \inn_1)} \ar@<.5ex>[rrr]^-{\inn_1 \circ j_Q} & & & H_{\Con} : P \ar[rr]^-{\inC_1} & & C_1
 }
@@
 To explain what this does, let us assume for a moment that we have one construct $c$ with arity 1.
-For $c' \> x$ with $x : Q$, the upper map is the inclusion of $H_{\Con} \> Q$ on the first coordinate of $H_{\Con} \> P$.
-The lower map sends $c' \> x$ to $c' \> (j_Q \> (\inn_1 \> x))$, so it replaces $x$ by its image in $P$.
+For $c' : x$ with $x : Q$, the upper map is the inclusion of $H_{\Con} : Q$ on the first coordinate of $H_{\Con} : P$.
+The lower map sends $c' : x$ to $c' : (j_Q : (\inn_1 : x))$, so it replaces $x$ by its image in $P$.
 
@@
 The resulting type should be free, so these paths should be identified.
-We define a map $q : B_i \> R \rightarrow \sum (x, y : P), (x = y) \times (x = y)$ sending $x : B_i \> R$ to the pair
-\[
-(\overline{t_i} \> x, \overline{r_i} \> x, \ap \> (j_Q \circ \inn_1) \> (p_R \> x), p_Q \> (B_i \> j_R \> x))
-\]
-Concluding the construction, we define $H_{\Approx}$ as $\pcoeq \> (B_i \> R) \> C_2 \> q$.
+We define a map $q : B_i : R \rightarrow \sum (x, y : P), (x = y) \times (x = y)$ sending $x : B_i : R$ to the pair
+\[
+(\overline{t_i} : x, \overline{r_i} : x, \ap : (j_Q \circ \inn_1) : (p_R : x), p_Q : (B_i : j_R : x))
+\]
+Concluding the construction, we define $H_{\Approx}$ as $\pcoeq : (B_i : R) : C_2 : q$.
 
@@
 \begin{definition}
-In the setting as described, we simultaneously define a sequence of approximations $F : \mathbb{N} \rightarrow \Type$ to $H$ and maps $f : \prod(n : \mathbb{N}), F \> n \rightarrow F(n+1)$ as follows.
+In the setting as described, we simultaneously define a sequence of approximations $F : \mathbb{N} \rightarrow \Type$ to $H$ and maps $f : \prod(n : \mathbb{N}), F : n \rightarrow F(n+1)$ as follows.
 \begin{itemize}
-        \item We define $F \> 0 = H_{\nonrec}$.
-        \item We define $F \> 1 = H_{\Approx}$ taking $P = F \> 0$ and $Q, R = \zero$ and the maps are defined by $\zero\frec$.
-        \item We define $F \> 2 = H_{\Approx}$ with $P= F \> 1, Q = F \> 0$ and $R =\zero$. We have a map $Q \rightarrow P$ defined to be the composition of all $\inC$ with $\inn_1$.
-        \item We define $F(n+3) = H_{\Approx}$ with $P = (F(n+2)$, $Q = F(n+1)$, and $R = F \> n$.
+        \item We define $F : 0 = H_{\nonrec}$.
+        \item We define $F : 1 = H_{\Approx}$ taking $P = F : 0$ and $Q, R = \zero$ and the maps are defined by $\zero\frec$.
+        \item We define $F : 2 = H_{\Approx}$ with $P= F : 1, Q = F : 0$ and $R =\zero$. We have a map $Q \rightarrow P$ defined to be the composition of all $\inC$ with $\inn_1$.
+        \item We define $F(n+3) = H_{\Approx}$ with $P = (F(n+2)$, $Q = F(n+1)$, and $R = F : n$.
 The maps $Q \rightarrow P$ and $R \rightarrow Q$ are defined to be the composition of $\inC$ with $\inn_1$ as in the construction.
@@
 \end{itemize}
-For the maps $f \> n : F \> n \rightarrow F(n + 1)$, note that we always have the following sequence of maps
+For the maps $f : n : F : n \rightarrow F(n + 1)$, note that we always have the following sequence of maps
 \[
@@
 {
-        F \> n \ar[r] & H_{\Con} \> (F \> n) \ar[r] & C_1 \ar[r] & \ldots \ar[r] & C_4 \ar[r] & H_{\Approx}.
-}
-\]
-Taking $P$ to be $F \> n$, then we have $F (n+1) = H_{\Approx} (F \> n)$, and thus the composition gives the map $F \> n \rightarrow F(n + 1)$.
+        F : n \ar[r] & H_{\Con} : (F : n) \ar[r] & C_1 \ar[r] & \ldots \ar[r] & C_4 \ar[r] & H_{\Approx}.
+}
+\]
+Taking $P$ to be $F : n$, then we have $F (n+1) = H_{\Approx} (F : n)$, and thus the composition gives the map $F : n \rightarrow F(n + 1)$.
 \end{definition}
@@
 \label{sec:rules}
-Now we have defined an object $\hocolim \> F \> f$, which is supposed to interpret the higher inductive type.
+Now we have defined an object $\hocolim : F : f$, which is supposed to interpret the higher inductive type.
 In order to finish the proof of Theorem \ref{thm:three-hit}, we need to show that it satisfies the rules.
@@
 
-Let us start by defining a map $A_{\nonrec} \rightarrow \hocolim \> F \> f$ which gives the introduction rule for the nonrecursive point constructor.
-Since $F \> 0$ is defined by $H_{\nonrec}$, which has a constructor $c'_{\nonrec} : A_{\nonrec} \rightarrow H_{\nonrec}$, this can be defined by the following composition.
+Let us start by defining a map $A_{\nonrec} \rightarrow \hocolim : F : f$ which gives the introduction rule for the nonrecursive point constructor.
+Since $F : 0$ is defined by $H_{\nonrec}$, which has a constructor $c'_{\nonrec} : A_{\nonrec} \rightarrow H_{\nonrec}$, this can be defined by the following composition.
 \[
@@
         A_{\nonrec} \ar[rr]^-{c'_{\nonrec}}
-                & & F \> 0 \ar[rr]^-{\inc \> 0}
-                & & \hocolim \> F \> f
-}
-\]
-
-Next we show that we also have the recursive point constructor meaning that we have a map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
+                & & F : 0 \ar[rr]^-{\inc : 0}
+                & & \hocolim : F : f
+}
+\]
+
+Next we show that we also have the recursive point constructor meaning that we have a map $A_{\rec} : (\hocolim : F : f) \rightarrow \hocolim : F : f$.
 This is slightly more complicated, and for that we first need a lemma which says that colimits over $\mathbb{N}$ commute with polynomials.
@@
 \label{lem:colim_commute_poly}
-The types $A \> (\hocolim \> F \> f)$ and $\hocolim \> (A \comp F) \> (A \> f)$ are isomorphic for all polynomials $A$.
+The types $A : (\hocolim : F : f)$ and $\hocolim : (A \comp F) : (A : f)$ are isomorphic for all polynomials $A$.
 \end{lemma}
@@
 
-Now we will construct the map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$, and by Lemma \ref{lem:colim_commute_poly} it suffices to make a map $\hocolim \> (A_{\rec} \comp F) \> (A_{\rec} \> f) \rightarrow \hocolim \> F \> f$.
+Now we will construct the map $A_{\rec} : (\hocolim : F : f) \rightarrow \hocolim : F : f$, and by Lemma \ref{lem:colim_commute_poly} it suffices to make a map $\hocolim : (A_{\rec} \comp F) : (A_{\rec} : f) \rightarrow \hocolim : F : f$.
 For this we use the recursion rule of $\hocolim$, and we start with the following string of maps
@@
 {
-                A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} 
-                & H_{\rec}(F \> n) \ar[rr]^-{\term \comp \inn_2} &
-                & H_{\Con}(F \> n) \ar[r]^-{\inC}
-                & H_{\Approx}(F \> n) = F(n + 1)
-}
-\]
-Composing this map with $\inc$, gives maps $A_{\rec}(F \> n) \rightarrow \hocolim \> F \> f$ for all $n : \mathbb{N}$.
+                A_{\rec}(F : n) \ar[r]^-{c_{\rec}'} 
+                & H_{\rec}(F : n) \ar[rr]^-{\term \comp \inn_2} &
+                & H_{\Con}(F : n) \ar[r]^-{\inC}
+                & H_{\Approx}(F : n) = F(n + 1)
+}
+\]
+Composing this map with $\inc$, gives maps $A_{\rec}(F : n) \rightarrow \hocolim : F : f$ for all $n : \mathbb{N}$.
 
@@
 {
-        A_{\rec}(F \> n) \ar[rr]^{A_{\rec}(f \> n)} \ar[dr] & & A_{\rec}(F(n+1)) \ar[dl] \\
-        & \hocolim \> F \> f &
+        A_{\rec}(F : n) \ar[rr]^{A_{\rec}(f : n)} \ar[dr] & & A_{\rec}(F(n+1)) \ar[dl] \\
+        & \hocolim : F : f &
 }
@@
 Before we continue, let us recall that inductive types are functors.
-Suppose, we have an inductive type $T$ with a parameter $P$, then a function $f : P \rightarrow Q$ gives a function $T \> f : T \> P \rightarrow T \> Q$.
+Suppose, we have an inductive type $T$ with a parameter $P$, then a function $f : P \rightarrow Q$ gives a function $T : f : T : P \rightarrow T : Q$.
 Let us start with the following rectangle
@@
 {
-        A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} \ar[d]_{A_{\rec}(f \> n)} 
-                & H_{\rec}(F \> n) \ar[rr]^{\term \comp \inn_2} \ar[d]_{H_{\rec}(f \> n)} &
-                & H_{\Con}(F \> n) \ar[d]_{H_{\Con}(f \> n)}\\
+        A_{\rec}(F : n) \ar[r]^-{c_{\rec}'} \ar[d]_{A_{\rec}(f : n)} 
+                & H_{\rec}(F : n) \ar[rr]^{\term \comp \inn_2} \ar[d]_{H_{\rec}(f : n)} &
+                & H_{\Con}(F : n) \ar[d]_{H_{\Con}(f : n)}\\
         A_{\rec}(F(n+1)) \ar[r]_-{c_{\rec}'} 
@@
 \]
-The left square commutes, because by definition of $H_{\rec} \> f$ we have
-\[
-H_{\rec} \>(f \> n) \> (c_{\rec}' x) = c_{\rec}' (A_{\rec} \> (f \> n) \> x).
+The left square commutes, because by definition of $H_{\rec} : f$ we have
+\[
+H_{\rec} :(f : n) : (c_{\rec}' x) = c_{\rec}' (A_{\rec} : (f : n) : x).
 \]
@@
 {
-        H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> (f \> n)} \ar[r]^-{\inC}
+        H_{\Con}(F : n) \ar[d]_{H_{\Con} : (f : n)} \ar[r]^-{\inC}
                 & F(n+1) \ar[d]^{f(n+1)}\\
         H_{\Con}(F(n+1)) \ar[r]_-{\inC}
-                & H_{\Approx} \> (F(n+1))
-}
-\]
-Note that $H_{\Approx}(F(n+1)) = F(n+2)$ and $H_{\Approx}(F \> n) = F(n+1)$.
+                & H_{\Approx} : (F(n+1))
+}
+\]
+Note that $H_{\Approx}(F(n+1)) = F(n+2)$ and $H_{\Approx}(F : n) = F(n+1)$.
 Hence, this diagram commutes, because of the coherency added in $C_2$.
@@
 Next we need to define the introduction rules for the paths.
-Let us start by extending the maps $t_i, r_i : B_i \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
-Since homotopy colimits commute with polynomials, it suffices to make a map $\hocolim \> (B_i \> F) \> (B_i \> f)  \rightarrow \hocolim \> F \> f$, and for this we need to start by defining maps $B_i(F \> n) \rightarrow \hocolim \> F \> f$.
-Note that by construction we always have maps $\overline{t_i}, \overline{r_i} : B_i(F \> n) \rightarrow H_{\Con}(F \> n)$, and thus we obtain maps $B_i(F \> n) \rightarrow F(n+1)$ by composing these with $\inC$.
+Let us start by extending the maps $t_i, r_i : B_i : (\hocolim : F : f) \rightarrow \hocolim : F : f$.
+Since homotopy colimits commute with polynomials, it suffices to make a map $\hocolim : (B_i : F) : (B_i : f)  \rightarrow \hocolim : F : f$, and for this we need to start by defining maps $B_i(F : n) \rightarrow \hocolim : F : f$.
+Note that by construction we always have maps $\overline{t_i}, \overline{r_i} : B_i(F : n) \rightarrow H_{\Con}(F : n)$, and thus we obtain maps $B_i(F : n) \rightarrow F(n+1)$ by composing these with $\inC$.
 
@@
 {
-        B_i(F \> n) 
+        B_i(F : n) 
         \ar[r]^-{\overline{t_i}} 
-        \ar[d]_{B_i(f \> n)} 
+        \ar[d]_{B_i(f : n)} 
         & 
-        H_{\Con}(F \> n) 
+        H_{\Con}(F : n) 
         \ar[r]^-{\inC}
-        \ar[d]^{H_{\Con}(f \> n)}  
+        \ar[d]^{H_{\Con}(f : n)}  
         & 
-        C_2(F \> n)
+        C_2(F : n)
         \ar[r]^{\inC}
@@
         F(n+1) 
-        \ar[d]^{f \> n}\\
+        \ar[d]^{f : n}\\
         B_i(F(n+1)) 
@@
 The right rectangle commutes, because the maps $\inC$ are built by composing constructors of the coequalizer, and thus it commutes by definition.
-Now it computes overall due to Lemma \ref{lem:constrCoh} which says that $\inC(\overline{t_i}(B_i(f \> n) \> x))$ and $\inC(H_{\Con}(f \> n)(\overline{t_i} \> x))$ are equal for all $x : B_i(F \> n)$.
+Now it computes overall due to Lemma \ref{lem:constrCoh} which says that $\inC(\overline{t_i}(B_i(f : n) : x))$ and $\inC(H_{\Con}(f : n)(\overline{t_i} : x))$ are equal for all $x : B_i(F : n)$.
 
 In order to show that we indeed have paths $p_i$, we use the eliminator of the homotopy colimit.
-We need to show that for all $x : \hocolim \> F \> f$ we have $t_i \> x = r_i \> x$. 
-First, we need to give for all $x : F \> n$ an inhabitant of $t_i \> (\inc \> n \> x) = r_i \> (\inc \> n \> x)$.
-By the first identification we have a path $\glueC \> x$ between $\overline{t_i} \> x$ and $\overline{r_i} \> x$, and thus the right path is $\ap \> (\inc \> n) \> (\glueC \> x)$.
+We need to show that for all $x : \hocolim : F : f$ we have $t_i : x = r_i : x$. 
+First, we need to give for all $x : F : n$ an inhabitant of $t_i : (\inc : n : x) = r_i : (\inc : n : x)$.
+By the first identification we have a path $\glueC : x$ between $\overline{t_i} : x$ and $\overline{r_i} : x$, and thus the right path is $\ap : (\inc : n) : (\glueC : x)$.
 
@@
 \[
-(\com \> n \> x)_*(\ap \> (\inc \> n) \> (\glueC \> x)) = \ap \> (\inc \> (n+1)) \> (\glueC \> ((B_i \>(f \>n)) \> x)).
+(\com : n : x)_*(\ap : (\inc : n) : (\glueC : x)) = \ap : (\inc : (n+1)) : (\glueC : ((B_i :(f :n)) : x)).
 \]
@@
 \begin{split}
-\ap &\> (\inc \> (n+1)) \> (\glueC \> ((B_i \>(f \> n)) \> x))\\
-&= \ap \> (\inc \> (n+1)) \> (\ap \> (f \> n) \>\glueC \> x))\\
-&= \ap \> (\inc \> (n+1) \circ (f \> n)) \>\glueC \> x))\\
-&=\com_* \> (\ap \> (\inc \> n) \> (\glueC \> x))
+\ap &: (\inc : (n+1)) : (\glueC : ((B_i :(f : n)) : x))\\
+&= \ap : (\inc : (n+1)) : (\ap : (f : n) :\glueC : x))\\
+&= \ap : (\inc : (n+1) \circ (f : n)) :\glueC : x))\\
+&=\com_* : (\ap : (\inc : n) : (\glueC : x))
 \end{split}
@@
 \subsection{Elimination Rule}
-For the next step we define the right eliminator for $\hocolim \> F \> f$, so suppose that we are given the following data
-\[
-Y : \hocolim \> F \> f \rightarrow \Type,
-\]
-\[
-c_{Y, \nonrec} : \prod (a : A_{\nonrec}), Y(c_{\nonrec} \> a),
-\]
-\[
-c_{Y, \rec} : \prod (x : A_{\rec} \> \hocolim \> F \> f), \overline{A_{\rec}} \> Y \> x \rightarrow Y(c_{\rec} \> x),
-\]
-\[
-q_{Y, i} : \prod (x : B_i \> H)(h_x : \overline{B_i} \> Y \> x), \hatt_i =_{p_j \, x} \hatr_j.
-\]
-In order to make a map $h : \prod (x : \hocolim \> F \> f), Y \> x$, we use the induction principle of $\hocolim \> F \> f$, and for that we first need to make maps $h \> n : \prod (x : F \> n), Y(\inc \> n \> x)$ for $n : \mathbb{N}$.
-
-We start by making a map $h \> 0 : \prod (x : F \> 0), Y(\inc \> 0 \> x)$.
-Recall that $F \> 0$ was defined to be $H_{\nonrec}$ which only has a constructor $c'_{\nonrec} : A_{\nonrec} \rightarrow H_{\nonrec}$.
+For the next step we define the right eliminator for $\hocolim : F : f$, so suppose that we are given the following data
+\[
+Y : \hocolim : F : f \rightarrow \Type,
+\]
+\[
+c_{Y, \nonrec} : \prod (a : A_{\nonrec}), Y(c_{\nonrec} : a),
+\]
+\[
+c_{Y, \rec} : \prod (x : A_{\rec} : \hocolim : F : f), \overline{A_{\rec}} : Y : x \rightarrow Y(c_{\rec} : x),
+\]
+\[
+q_{Y, i} : \prod (x : B_i : H)(h_x : \overline{B_i} : Y : x), \hatt_i =_{p_j \, x} \hatr_j.
+\]
+In order to make a map $h : \prod (x : \hocolim : F : f), Y : x$, we use the induction principle of $\hocolim : F : f$, and for that we first need to make maps $h : n : \prod (x : F : n), Y(\inc : n : x)$ for $n : \mathbb{N}$.
+
+We start by making a map $h : 0 : \prod (x : F : 0), Y(\inc : 0 : x)$.
+Recall that $F : 0$ was defined to be $H_{\nonrec}$ which only has a constructor $c'_{\nonrec} : A_{\nonrec} \rightarrow H_{\nonrec}$.
 So, let us assume that we have $a : A_{\nonrec}$.
-Since $c_{\nonrec} \> a = \inc \> 0 \> (c_{\nonrec}' \> a)$, it suffices to find an inhabitant of $Y(c_{\nonrec} \> a)$, and for that we take $c_{Y, \nonrec} \> a$.
-Hence, we get a map $h \> 0$.
-
-Now suppose that we have a map $h \> n : \prod (x : F \> n), Y(\inc \> n \> x)$, and our goal is to make a map $h(n+1) : \prod  (x : F(n+1)), Y(\inc \> (n+1) \> x)$.
-In order to do so, we will first look at how to extend $h \> n$ to a map $\prod (x : H_{\Con} (F \> n)), Y(\inc \> (n+1) \> (\inC \> x))$.
+Since $c_{\nonrec} : a = \inc : 0 : (c_{\nonrec}' : a)$, it suffices to find an inhabitant of $Y(c_{\nonrec} : a)$, and for that we take $c_{Y, \nonrec} : a$.
+Hence, we get a map $h : 0$.
+
+Now suppose that we have a map $h : n : \prod (x : F : n), Y(\inc : n : x)$, and our goal is to make a map $h(n+1) : \prod  (x : F(n+1)), Y(\inc : (n+1) : x)$.
+In order to do so, we will first look at how to extend $h : n$ to a map $\prod (x : H_{\Con} (F : n)), Y(\inc : (n+1) : (\inC : x))$.
 
 Let us do this in the general case.
-Suppose, we have a map $g : P \rightarrow \hocolim \> F \> f$, and that we already constructed $\varphi : \prod (x : P), Y(g \> x)$.
-Our goal is to extend the map into $\varphi' : \prod (x : H_{\rec} P), Y(c_{Y, \rec} \> x)$, and for that we use $H_{\rec}$-induction.
-Note that for each $c'_{\rec} \> x$ with $x : A_{\rec} \> P$ we have the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$, and thus we have a type family on $H_{\rec}$.
-Now let $x : A_{\rec} \> P$ and $y : \overline{A_{\rec}} \> Y \> x$ be given.
-Then we need to give an element of the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$ for which we take $c_{Y,\rec} \> (A_{\rec} \> g \> x) \> y$.
-We will often leave the argument $A_{\rec} \> g \> x$ implicit.
-
-Now we can also extend the map to $H_{\Con}^n \> P$, because we can define this map on each component.
+Suppose, we have a map $g : P \rightarrow \hocolim : F : f$, and that we already constructed $\varphi : \prod (x : P), Y(g : x)$.
+Our goal is to extend the map into $\varphi' : \prod (x : H_{\rec} P), Y(c_{Y, \rec} : x)$, and for that we use $H_{\rec}$-induction.
+Note that for each $c'_{\rec} : x$ with $x : A_{\rec} : P$ we have the type $Y(c_{\rec} : (A_{\rec} : g : x))$, and thus we have a type family on $H_{\rec}$.
+Now let $x : A_{\rec} : P$ and $y : \overline{A_{\rec}} : Y : x$ be given.
+Then we need to give an element of the type $Y(c_{\rec} : (A_{\rec} : g : x))$ for which we take $c_{Y,\rec} : (A_{\rec} : g : x) : y$.
+We will often leave the argument $A_{\rec} : g : x$ implicit.
+
+Now we can also extend the map to $H_{\Con}^n : P$, because we can define this map on each component.
 On the component $P$ it is just $\varphi$, and on the other components we define it via extension.
@@
 This is done by the universal mapping property of the coequalizer, and that requires some steps.
-First, to give an paths between the images of $t_i \> x$ and $r_i \> x$.
-Note that the images of these are $\hatt_i \> x$ and $\hatr_i \> x$ respectively, and then $q_{Y, i}$ gives the desired paths.
+First, to give an paths between the images of $t_i : x$ and $r_i : x$.
+Note that the images of these are $\hatt_i : x$ and $\hatr_i : x$ respectively, and then $q_{Y, i}$ gives the desired paths.
 This gives an extension $h_2$ to $C_1$.
@@
 Next we check the coherency conditions, and we start with the first.
-We need to check that $\inn_1(\inC \> x)$ and $H_{\Con} \> \inC \> x$ get mapped to the same element for $x : H_{\Con}(F \> n)$ by $h_2$.
-To do so, we use a case distinction on $H_{\Con}(F \> n)$, and for the case $x \equiv \inn_1 \> y$ with $y : F \> n$, we have the following equations 
+We need to check that $\inn_1(\inC : x)$ and $H_{\Con} : \inC : x$ get mapped to the same element for $x : H_{\Con}(F : n)$ by $h_2$.
+To do so, we use a case distinction on $H_{\Con}(F : n)$, and for the case $x \equiv \inn_1 : y$ with $y : F : n$, we have the following equations 
 \begin{equation*}
 \begin{split}
-h_2 \> (\inC(\inn_1(\inC \> (\inn_1 \> y))))
-&\equiv 
-h_1 \> (\inn_1(\inC(\inn_1 \> y))),
+h_2 : (\inC(\inn_1(\inC : (\inn_1 : y))))
+&\equiv 
+h_1 : (\inn_1(\inC(\inn_1 : y))),
 \end{split}
@@
 \begin{split}
-h_2 \> (\inC(H_{\Con} \> (\inC \circ \inn_1) \> (\inn_1 \> y)))
-&\equiv
-h_1 \> (H_{\Con} \> (\inC \circ \inn_1) \> (\inn_1 \> y))\\
-&\equiv 
-h_1 \> (\inn_1(\inC(\inn_1 \> y)))
+h_2 : (\inC(H_{\Con} : (\inC \circ \inn_1) : (\inn_1 : y)))
+&\equiv
+h_1 : (H_{\Con} : (\inC \circ \inn_1) : (\inn_1 : y))\\
+&\equiv 
+h_1 : (\inn_1(\inC(\inn_1 : y)))
 \end{split}
@@
 
-For the other cases, we take a look at $c_{\rec}' \> y$, and for $y$ we assume that $h_1(\inn_1(\inC \> y)) = h_1(H_{\Con} \> (\inC \circ \inn_1) \> y)$.
+For the other cases, we take a look at $c_{\rec}' : y$, and for $y$ we assume that $h_1(\inn_1(\inC : y)) = h_1(H_{\Con} : (\inC \circ \inn_1) : y)$.
 Note that at each level $h$ is defined using the eliminator of the coequalizer.
-This means that $h \> n \> (\inC \> (c_{\rec}' \> y))$ and $c_{Y, \rec}(h \> n \> (\inC \> y))$ are equal by definition, and thus we can make the following computations.
+This means that $h : n : (\inC : (c_{\rec}' : y))$ and $c_{Y, \rec}(h : n : (\inC : y))$ are equal by definition, and thus we can make the following computations.
 \begin{equation*}
 \begin{split}
-h_1 \> (\inn_1(\inC \> (c_{\rec}' \> y))) 
-&\equiv 
-h \> n \> (\inC \> (c_{\rec}' \> y))\\
+h_1 : (\inn_1(\inC : (c_{\rec}' : y))) 
+&\equiv 
+h : n : (\inC : (c_{\rec}' : y))\\
 &
-= c_{Y, \rec} (h \> n \> (\inC \> y))
+= c_{Y, \rec} (h : n : (\inC : y))
 \end{split}
@@
 \begin{split}
-h_1 \> (H_{\Con} \> (\inC \circ \inn_1) \> (c_{\rec}' \> y)) 
-&\equiv 
-h_1 \> (c_{\rec}' \> (H_{\Con} \> (\inC \circ \inn_1) \> y))
+h_1 : (H_{\Con} : (\inC \circ \inn_1) : (c_{\rec}' : y)) 
+&\equiv 
+h_1 : (c_{\rec}' : (H_{\Con} : (\inC \circ \inn_1) : y))
 \\
 &\equiv
-c_{Y, \rec} \> (h_1 \> (H_{\Con} \> (\inC \circ \inn_1) \> y))\\
+c_{Y, \rec} : (h_1 : (H_{\Con} : (\inC \circ \inn_1) : y))\\
 &=
-c_{Y, \rec} \> (h_1(\inn_1(\inC \> y)))\\
-&\equiv
-c_{Y, \rec} \> (h \> n \> (\inC \> y)).
+c_{Y, \rec} : (h_1(\inn_1(\inC : y)))\\
+&\equiv
+c_{Y, \rec} : (h : n : (\inC : y)).
 \end{split}
@@
 
-For the second coherency we need to check that the paths $\ap \> h_2 \> (\ap \> (f \> n) \> (p_i \> x))$ and $\ap \> h_2 \> (p_i \> (f \> n \> x))$ are equal.
+For the second coherency we need to check that the paths $\ap : h_2 : (\ap : (f : n) : (p_i : x))$ and $\ap : h_2 : (p_i : (f : n : x))$ are equal.
 Here we use several Lemmata, namely Lemma 2.2.2 from \cite{hottbook} and Lemma \ref{lem:pathext}.
-For the first path we can show that it is equal to $q_{Y, i} \> (h \> n \> x)$.
+For the first path we can show that it is equal to $q_{Y, i} : (h : n : x)$.
 \begin{equation*}
 \begin{split}
-\ap \> h_2 \> (\ap \> (f \> n) \> (p_i \> x))
-&\equiv
-\ap \> h_2 \> (\ap \> (\inC \circ \inn_1) \> (p_i \> x))\\
+\ap : h_2 : (\ap : (f : n) : (p_i : x))
+&\equiv
+\ap : h_2 : (\ap : (\inC \circ \inn_1) : (p_i : x))\\
 &=
-\ap \> (h_2 \circ \inC) \> (\ap \> \inn_1 \> (p_i \> x))\\
+\ap : (h_2 \circ \inC) : (\ap : \inn_1 : (p_i : x))\\
 &=
-\ap \> h_1 \> (\ap \> \inn_1 \> (p_i \> x))\\
+\ap : h_1 : (\ap : \inn_1 : (p_i : x))\\
 &=
-\ap \> (h_1 \circ \inn_1) \> \> (p_i \> x)\\
+\ap : (h_1 \circ \inn_1) : : (p_i : x)\\
 &=
-\ap \> (h \> n) \> \> (p_i \> x)\\
-&\equiv
-q_{Y, i} \> (h \> n \> x)
+\ap : (h : n) : : (p_i : x)\\
+&\equiv
+q_{Y, i} : (h : n : x)
 \end{split}
 \end{equation*}
-Since $(h_2 \circ \inC) \> x \equiv h_1 \> x$ and $(h_1 \circ \inn_1) \> x \equiv h \> n \> x$, we can use the path $\refl$, and thus the transport is the identity.
+Since $(h_2 \circ \inC) : x \equiv h_1 : x$ and $(h_1 \circ \inn_1) : x \equiv h : n : x$, we can use the path $\refl$, and thus the transport is the identity.
 For the other path we can do the same.
@@
 \begin{split}
-\ap \> h_2 \> (p_i \> (f \> n \> x))
-&\equiv
-q_{Y, i} \> (h_2 \> (f \> n \> x))\\
-&\equiv
-q_{Y, i} \> (h_2 \> (\inC \> \inn_1 \> x))\\
-&\equiv
-q_{Y, i} \> (h_1 \> (\inn_1 \> x))\\
-&\equiv
-q_{Y, i} \> (h \> n \> x)
+\ap : h_2 : (p_i : (f : n : x))
+&\equiv
+q_{Y, i} : (h_2 : (f : n : x))\\
+&\equiv
+q_{Y, i} : (h_2 : (\inC : \inn_1 : x))\\
+&\equiv
+q_{Y, i} : (h_1 : (\inn_1 : x))\\
+&\equiv
+q_{Y, i} : (h : n : x)
 \end{split}
@@
 To finish the proof, we need to give the image for the path $\com$.
-More concretely, we need to show that $\inc \> n \> x$ and $\inc \> (n+1) \> (f \> x)$ are mapped to the same element.
-The map $f : F \> n \rightarrow F(n + 1)$ is defined by the elimination rule of the coequalizer as follows
+More concretely, we need to show that $\inc : n : x$ and $\inc : (n+1) : (f : x)$ are mapped to the same element.
+The map $f : F : n \rightarrow F(n + 1)$ is defined by the elimination rule of the coequalizer as follows
 \[
@@
 {
-        F \> n \ar[r]^-{\inn_1} & H_{\Con} \> (F \> n) \ar[r]^-{\inC} & \ldots \ar[r]^-{\inC} & F(n+1)
+        F : n \ar[r]^-{\inn_1} & H_{\Con} : (F : n) \ar[r]^-{\inC} & \ldots \ar[r]^-{\inC} & F(n+1)
 }
@@
 
-All in all, we have acquired a map $\prod (x : \hocolim \> F \> f), Y \> x$, and this way we defined the right eliminator for $\hocolim \> F \> f$.
+All in all, we have acquired a map $\prod (x : \hocolim : F : f), Y : x$, and this way we defined the right eliminator for $\hocolim : F : f$.
 We shall call the eliminator $H\ind$.
@@
 Lastly, we show that this eliminator also satisfies the computation rules.
-First, we prove that for each $t : A_{\rec}(\hocolim \> F \> f)$ that $H\ind(c_{\rec} \> t) \equiv f_i \> t \> (\overline{A_{\rec}} \> H\ind \> t)$.
+First, we prove that for each $t : A_{\rec}(\hocolim : F : f)$ that $H\ind(c_{\rec} : t) \equiv f_i : t : (\overline{A_{\rec}} : H\ind : t)$.
 Again we use that colimits commute with polynomials.
 
-Let $n : \mathbb{N}$ and $x : A_{\rec}(F \> n)$.
+Let $n : \mathbb{N}$ and $x : A_{\rec}(F : n)$.
 Now we can perform the computations in an intermediate stage of the construction, and using the computation rules we get
@@
 \begin{split}
-H\ind(c_{\rec} \> (\inc \> n \> x)) 
-&\equiv H\ind(\inc \> (n+1) \> (c_{\rec}' x)) \\
-&\equiv c_{Y,\rec} \> (A_{\rec} \> (\inc \> n) \> x) \> (\overline{A} \> H\ind \> x)
+H\ind(c_{\rec} : (\inc : n : x)) 
+&\equiv H\ind(\inc : (n+1) : (c_{\rec}' x)) \\
+&\equiv c_{Y,\rec} : (A_{\rec} : (\inc : n) : x) : (\overline{A} : H\ind : x)
 \end{split}
@@
 Note that the this computation rule is a propositional equality.
-This is logical, because it is proven all $x : A_{\rec}(F \> n)$.
+This is logical, because it is proven all $x : A_{\rec}(F : n)$.
 However, for terms built from $c_{\nonrec}$ and $c_{\rec}$, we have a definitional equality.
-This is because $c_{\nonrec} \> a$ for $a : A_{\nonrec}$ is defined to be $\inc \> 0 \> (c_{\nonrec}' \> a)$.
-All the closed terms are thus inhabitants of some $F \> n$, and since at every step the equalities are definitional, we can conclude that for closed terms the equality is definitional.
-
-Now we show the computation rules for the paths, and in that case we have a parameter $a : B_i \> (\hocolim \> F \> f)$.
-By using that polynomials commute with homotopy colimits, we can again assume that we have $n : \mathbb{N}$ and $x : B_i(F \> n)$.
+This is because $c_{\nonrec} : a$ for $a : A_{\nonrec}$ is defined to be $\inc : 0 : (c_{\nonrec}' : a)$.
+All the closed terms are thus inhabitants of some $F : n$, and since at every step the equalities are definitional, we can conclude that for closed terms the equality is definitional.
+
+Now we show the computation rules for the paths, and in that case we have a parameter $a : B_i : (\hocolim : F : f)$.
+By using that polynomials commute with homotopy colimits, we can again assume that we have $n : \mathbb{N}$ and $x : B_i(F : n)$.
 \begin{equation*}
 \begin{split}
-\apd \> H\ind \> (p_i \> (\inc \> n \> x))
-&\equiv \apd \> H\ind \> (\ap \> (\inc \> (n+1)) \> \glueC \> x)\\
-&= \apd \> (H\ind \comp  \> \inc (n+1)) \> (\glueC \> x)\\
-&= \apd \> (h \> n) \> (\glueC \> x)\\
-&\equiv q_i \> (B_i \> H\frec \> x)
+\apd : H\ind : (p_i : (\inc : n : x))
+&\equiv \apd : H\ind : (\ap : (\inc : (n+1)) : \glueC : x)\\
+&= \apd : (H\ind \comp  : \inc (n+1)) : (\glueC : x)\\
+&= \apd : (h : n) : (\glueC : x)\\
+&\equiv q_i : (B_i : H\frec : x)
 \end{split}
@@
 \label{lem:constrTerm}
-Suppose, we have a constructor term $t$ such that $x : F \> T \Vdash t : G \>T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow P$.
-Then $t$ induces a map $\overline{t} : F \> P \rightarrow H_{\Con}^n \> (G \> P)$ by replacing the constructors $c_{\nonrec}$ and $c_{\rec}$ by $c_{\nonrec}'$ and $c_{\rec}'$ respectively.
+Suppose, we have a constructor term $t$ such that $x : F : T \Vdash t : G :T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow P$.
+Then $t$ induces a map $\overline{t} : F : P \rightarrow H_{\Con}^n : (G : P)$ by replacing the constructors $c_{\nonrec}$ and $c_{\rec}$ by $c_{\nonrec}'$ and $c_{\rec}'$ respectively.
 \end{lemma}
@@
 \begin{itemize}
-        \item $t = a$ with $a : B$ and $B$ does not use $T$. Then we define $\overline{t} \> y = \inn_1 \> a$.
-        \item $t = x$ with $x : F \> T$. Then we define $\overline{t} \> y = \inn_1 \> y$.
-        \item $t = c_{\nonrec} \> a$ with $a : A_{\nonrec}$. Then we define $\overline{t} \> y = \inn_1 \> (c_{\nonrec}' \> a)$.
-        \item $t = c_{\rec} \> r$ with $r : A_{\rec} \> T$ where $r$ uses at most $n-1$ constructors. 
-        By induction we have a map $\overline{r} : F \> P \rightarrow A_{\rec} \> H_{\Con}^{n-1}$.
-        Then we define $\overline{t} \> y = c_{\rec}' (\overline{r} \> x)$.
+        \item $t = a$ with $a : B$ and $B$ does not use $T$. Then we define $\overline{t} : y = \inn_1 : a$.
+        \item $t = x$ with $x : F : T$. Then we define $\overline{t} : y = \inn_1 : y$.
+        \item $t = c_{\nonrec} : a$ with $a : A_{\nonrec}$. Then we define $\overline{t} : y = \inn_1 : (c_{\nonrec}' : a)$.
+        \item $t = c_{\rec} : r$ with $r : A_{\rec} : T$ where $r$ uses at most $n-1$ constructors. 
+        By induction we have a map $\overline{r} : F : P \rightarrow A_{\rec} : H_{\Con}^{n-1}$.
+        Then we define $\overline{t} : y = c_{\rec}' (\overline{r} : x)$.
         \item For the rules for the projection, pairing and injection it is trivial. \qedhere
@@
 \label{lem:constrCoh}
-Suppose, we have a constructor term $t$ such that $x : F \> T \Vdash t : G \> T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow Q$.
+Suppose, we have a constructor term $t$ such that $x : F : T \Vdash t : G : T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow Q$.
 Furthermore, we assume that we have a map $f : Q \rightarrow P$
-Then for all $x : F \> P$ the terms $\overline{t}(F \> f \> x)$ and $(H_{\Con} \circ G) \> f \> (\overline{t} \> x)$ are equal.
+Then for all $x : F : P$ the terms $\overline{t}(F : f : x)$ and $(H_{\Con} \circ G) : f : (\overline{t} : x)$ are equal.
 \end{lemma}
@@
         \item $t = a$ with $a : B$ and $B$ does not use $T$. 
-        Then we have $G \> P = B$, and thus 
+        Then we have $G : P = B$, and thus 
         $
-        \overline{t}(F \> f \> x) = a.
+        \overline{t}(F : f : x) = a.
         $
@@
         \[
-        (H_{\Con} \circ G) \> f \> (\overline{t} \> x) = G \> f \> a = a.
-        \]
-        \item $t = x$ with $x : F \> T$. 
-        Then $G \> P = F \> P$, and thus
+        (H_{\Con} \circ G) : f : (\overline{t} : x) = G : f : a = a.
+        \]
+        \item $t = x$ with $x : F : T$. 
+        Then $G : P = F : P$, and thus
         $
-        \overline{t}(F \> f \> x) = \inn_1(F \> f \> x).
+        \overline{t}(F : f : x) = \inn_1(F : f : x).
         $
@@
         \[
-        (H_{\Con} \circ G) \> f \> (\overline{t} \> x) = (H_{\Con} \circ G) \> f \> (\inn_1 \> x) = \inn_1(G \> f \> x) = \inn_1(F \> f \> x).
-        \]
-        \item $t = c_{\nonrec} \> a$ with $a : A_{\nonrec}$. 
-        Then $G \> P = P$, and thus
+        (H_{\Con} \circ G) : f : (\overline{t} : x) = (H_{\Con} \circ G) : f : (\inn_1 : x) = \inn_1(G : f : x) = \inn_1(F : f : x).
+        \]
+        \item $t = c_{\nonrec} : a$ with $a : A_{\nonrec}$. 
+        Then $G : P = P$, and thus
         $
-        \overline{t}(F \> f \> x) = \inn_1(f(c'_{\nonrec} \> a))
+        \overline{t}(F : f : x) = \inn_1(f(c'_{\nonrec} : a))
         $.
@@
         \[
-        (H_{\Con} \circ G) \> f \> (\overline{t} \> x) = H_{\Con} \> f \> (\inn_1(c'_{\nonrec} \> a)) = \inn_1(f(c'_{\nonrec} \> a))
-        \]
-        \item $t = c_{\rec} \> r$ with $r : A_{\rec} \> T$ where $r$ uses at most $n-1$ constructors. 
-        The induction hypothesis in this case is that $H_{\Con} \> f \> (\overline{r} \> x) = \overline{r}(F \> f \> x)$.
-        Then again $G \> P = P$, and thus
+        (H_{\Con} \circ G) : f : (\overline{t} : x) = H_{\Con} : f : (\inn_1(c'_{\nonrec} : a)) = \inn_1(f(c'_{\nonrec} : a))
+        \]
+        \item $t = c_{\rec} : r$ with $r : A_{\rec} : T$ where $r$ uses at most $n-1$ constructors. 
+        The induction hypothesis in this case is that $H_{\Con} : f : (\overline{r} : x) = \overline{r}(F : f : x)$.
+        Then again $G : P = P$, and thus
         $
-        \overline{t}(F \> f \> x) = c'_{\rec} \> (\overline{r}(F \> f \> x))
+        \overline{t}(F : f : x) = c'_{\rec} : (\overline{r}(F : f : x))
         $.
@@
         \[
-        (H_{\Con} \circ G) \> f \> (\overline{t} \> x) = H_{\Con} \> f \> (c'_{\rec} \> (\overline{r} \> x)) = c'_{\rec} \> (H_{\Con} \> f \> (\overline{r} \> x)) = c'_{\rec} \> (\overline{r}(F \> f \> x))
+        (H_{\Con} \circ G) : f : (\overline{t} : x) = H_{\Con} : f : (c'_{\rec} : (\overline{r} : x)) = c'_{\rec} : (H_{\Con} : f : (\overline{r} : x)) = c'_{\rec} : (\overline{r}(F : f : x))
         \]
@@
 \label{lem:colimcon}
-The type $\hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id})$ is isomorphic to $A$.
+The type $\hocolim : (\lambda n . A) : (\lambda n . \operatorname{Id})$ is isomorphic to $A$.
 \end{lemma}
@@
 \begin{proof}
-We define the map $f : A \rightarrow \hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id})$
-to be $\inc \> 0$.
-Next we define $g : \hocolim \> (\lambda n . A) \> (\lambda n . \operatorname{Id}) \rightarrow A$ by $\hocolim$ recursion.
-We send $\inc \> n \> a$ to $a$, and then the required diagrams commute by reflexivity.
+We define the map $f : A \rightarrow \hocolim : (\lambda n . A) : (\lambda n . \operatorname{Id})$
+to be $\inc : 0$.
+Next we define $g : \hocolim : (\lambda n . A) : (\lambda n . \operatorname{Id}) \rightarrow A$ by $\hocolim$ recursion.
+We send $\inc : n : a$ to $a$, and then the required diagrams commute by reflexivity.
 The proof that these maps are mutual inverses is straightforward but tedious, so we refer the reader to the accompanying Coq code \cite{CoqImpl}.
@@
 \label{lem:colimsum}
-Colimits commute with coproducts, so $\hocolim \> (G_1 + G_2) \> (g_1 + g_2)$ and $\hocolim \> G_1 \> g_1 + \hocolim \> G_2 \> g_2$ are isomorphic.
+Colimits commute with coproducts, so $\hocolim : (G_1 + G_2) : (g_1 + g_2)$ and $\hocolim : G_1 : g_1 + \hocolim : G_2 : g_2$ are isomorphic.
 \end{lemma}
@@
 \[
-\hocolim \> (G_1+G_2) \> (g_1 + g_2) \rightarrow \hocolim \> G_1 \> g_1 + \hocolim \> G_2 \> g_2.
-\]
-This map is defined by recursion over the colimit, so take any $n : \mathbb{N}$ and $x : G_i \> n$.
-Then the image of $\inc \> n \> (\inn_i \> x)$ is defined to be $\inn_i (\inc \> n \> x)$, and the image of $\com \> n \> (\inn_i \> x)$ is defined by
-$\ap \> \inn_i \> (\com \> G_i \> g_i \> n \> x)$.
+\hocolim : (G_1+G_2) : (g_1 + g_2) \rightarrow \hocolim : G_1 : g_1 + \hocolim : G_2 : g_2.
+\]
+This map is defined by recursion over the colimit, so take any $n : \mathbb{N}$ and $x : G_i : n$.
+Then the image of $\inc : n : (\inn_i : x)$ is defined to be $\inn_i (\inc : n : x)$, and the image of $\com : n : (\inn_i : x)$ is defined by
+$\ap : \inn_i : (\com : G_i : g_i : n : x)$.
 
@@
 \[
-\hocolim \> G_i \> g_i \rightarrow \hocolim \> (G_1 + G_2) \> (g_1 + g_2).
-\]
-We send $\inc \> n \> x$ to $\inc \> n \> (\inn_i \> x)$ and $\com \> n \> x$ to $\com \> n \> (\inn_i \> x)$.
+\hocolim : G_i : g_i \rightarrow \hocolim : (G_1 + G_2) : (g_1 + g_2).
+\]
+We send $\inc : n : x$ to $\inc : n : (\inn_i : x)$ and $\com : n : x$ to $\com : n : (\inn_i : x)$.
 \end{proof}
@@
 \[
-e_* \> (\ap \> f \> p) = \ap \> g \> p.
+e_* : (\ap : f : p) = \ap : g : p.
 \]
@@
 \[
-\prod (f, g : A \rightarrow B) (e : f = g) (x, y : A) (p : x = y), e_* \> (\ap \> f \> p) = \ap \> g \> p
+\prod (f, g : A \rightarrow B) (e : f = g) (x, y : A) (p : x = y), e_* : (\ap : f : p) = \ap : g : p
 \]
@@
 \label{lem:funTrans}
-Again we are given types $A, B$, functions $f, g : A \rightarrow B$, an inhabitant $e : f = g$, and a path $p : f \> x = f \> y$ with $x, y : A$.
+Again we are given types $A, B$, functions $f, g : A \rightarrow B$, an inhabitant $e : f = g$, and a path $p : f : x = f : y$ with $x, y : A$.
 Then we have a path 
 \[
-e_* \> p = (e \fpath x)^{-1} \conc p \conc (e \fpath x)
+e_* : p = (e \fpath x)^{-1} \conc p \conc (e \fpath x)
 \]
@@
 \[
-\prod (f, g : A \rightarrow B) (e : f = g) (x, y : A) (p : f \> x = f \> y), e_* \> p = (e \fpath x)^{-1} \conc p \conc (e \fpath y).
+\prod (f, g : A \rightarrow B) (e : f = g) (x, y : A) (p : f : x = f : y), e_* : p = (e \fpath x)^{-1} \conc p \conc (e \fpath y).
 \]

### 2017-03-27 Paper/Paper.tex
Reaplce `\Vdash` with `\vdash`.
Frege introduced `\vdash` more than a 100 years ago, so let's not change his notation
today. The symbol `\Vdash` is used in forcing and semantics, not in proof systems.

@@
 Given is a function $c : A : T \rightarrow T$ with $A$ polynomial and $T$ a type.
-Then we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F : T \Vdash t : G : T$ can be derived using the following rules.
+Then we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F : T \vdash t : G : T$ can be derived using the following rules.
 \begin{gather*}
@@
         \AxiomC{$T$ does not occur in $B$}
-        \BinaryInfC{$x:F : T \Vdash t : B$}
+        \BinaryInfC{$x:F : T \vdash t : B$}
         \bottomAlignProof
@@
         \AxiomC{}
-        \UnaryInfC{$x : F : T \Vdash x : F : T$}
+        \UnaryInfC{$x : F : T \vdash x : F : T$}
         \bottomAlignProof
@@
         \quad
-        \AxiomC{$x : F : T \Vdash r : A : T$}
-        \UnaryInfC{$x : F : T \Vdash c : r : T$}
+        \AxiomC{$x : F : T \vdash r : A : T$}
+        \UnaryInfC{$x : F : T \vdash c : r : T$}
         \bottomAlignProof
@@
         \AxiomC{$j \in \{1, 2\}$}
-        \AxiomC{$x : F : T \Vdash r : G_1 : T \times G_2 : T$}
-        \BinaryInfC{$x : F : T \Vdash\pi_j : r : G_j : T$}
+        \AxiomC{$x : F : T \vdash r : G_1 : T \times G_2 : T$}
+        \BinaryInfC{$x : F : T \vdash\pi_j : r : G_j : T$}
         \bottomAlignProof
@@
         \AxiomC{$j \in \{1, 2\}$}
-        \AxiomC{$x : F : T \Vdash r_j : G_j$}
-        \BinaryInfC{$x : F : T \Vdash (r_1, r_2) : G_1 : T\times G_2 : T$}
+        \AxiomC{$x : F : T \vdash r_j : G_j$}
+        \BinaryInfC{$x : F : T \vdash (r_1, r_2) : G_1 : T\times G_2 : T$}
         \bottomAlignProof
@@
         \AxiomC{$j \in \{1, 2\}$}
-        \AxiomC{$x : F : T \Vdash r : G_j : T$}
+        \AxiomC{$x : F : T \vdash r : G_j : T$}
         \BinaryInfC{$x : F : T : \inn_j : r : G_1 : T + G_2 : T$}
@@
 Given is a constructor $c : A : H \rightarrow H$, a type family $Y : H \rightarrow \Type$, and a term $f : \prod (x: A : H), \bar{A} : Y : x \rightarrow  Y(c : x)$.
-For a constructor term $F : H \Vdash r : G : H$ we define the \emph{lift $\dak{r}$ of $r$} with type 
+For a constructor term $F : H \vdash r : G : H$ we define the \emph{lift $\dak{r}$ of $r$} with type 
 $
@@
 \label{lem:constrTerm}
-Suppose, we have a constructor term $t$ such that $x : F : T \Vdash t : G :T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow P$.
+Suppose, we have a constructor term $t$ such that $x : F : T \vdash t : G :T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow P$.
 Then $t$ induces a map $\overline{t} : F : P \rightarrow H_{\Con}^n : (G : P)$ by replacing the constructors $c_{\nonrec}$ and $c_{\rec}$ by $c_{\nonrec}'$ and $c_{\rec}'$ respectively.
@@
 \label{lem:constrCoh}
-Suppose, we have a constructor term $t$ such that $x : F : T \Vdash t : G : T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow Q$.
+Suppose, we have a constructor term $t$ such that $x : F : T \vdash t : G : T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow Q$.
 Furthermore, we assume that we have a map $f : Q \rightarrow P$

### 2017-03-27 Paper/Paper.tex
Revert "Replace `\>` with `:`." (I was confused about the meaning of `\>`, sorry.)
This reverts commit 183cdf1d33d4ced299e909e07b3d21c983d40f69.

--- 2017-03-27 Paper/Paper.tex
@@
 Given is a function $c : A \> T \rightarrow T$ with $A$ polynomial and $T$ a type.
-Then we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F \> T \Vdash t : G \> T$ can be derived using the following rules.
+Then we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F \> T \vdash t : G \> T$ can be derived using the following rules.
 \begin{gather*}
@@
         \AxiomC{$T$ does not occur in $B$}
-        \BinaryInfC{$x:F \> T \Vdash t : B$}
+        \BinaryInfC{$x:F \> T \vdash t : B$}
         \bottomAlignProof
@@
         \AxiomC{}
-        \UnaryInfC{$x : F \> T \Vdash x : F \> T$}
+        \UnaryInfC{$x : F \> T \vdash x : F \> T$}
         \bottomAlignProof
@@
         \quad
-        \AxiomC{$x : F \> T \Vdash r : A \> T$}
-        \UnaryInfC{$x : F \> T \Vdash c \> r : T$}
+        \AxiomC{$x : F \> T \vdash r : A \> T$}
+        \UnaryInfC{$x : F \> T \vdash c \> r : T$}
         \bottomAlignProof
@@
         \AxiomC{$j \in \{1, 2\}$}
-        \AxiomC{$x : F \> T \Vdash r : G_1 \> T \times G_2 \> T$}
-        \BinaryInfC{$x : F \> T \Vdash\pi_j \> r : G_j \> T$}
+        \AxiomC{$x : F \> T \vdash r : G_1 \> T \times G_2 \> T$}
+        \BinaryInfC{$x : F \> T \vdash\pi_j \> r : G_j \> T$}
         \bottomAlignProof
@@
         \AxiomC{$j \in \{1, 2\}$}
-        \AxiomC{$x : F \> T \Vdash r_j : G_j$}
-        \BinaryInfC{$x : F \> T \Vdash (r_1, r_2) : G_1 \> T\times G_2 \> T$}
+        \AxiomC{$x : F \> T \vdash r_j : G_j$}
+        \BinaryInfC{$x : F \> T \vdash (r_1, r_2) : G_1 \> T\times G_2 \> T$}
         \bottomAlignProof
@@
         \AxiomC{$j \in \{1, 2\}$}
-        \AxiomC{$x : F \> T \Vdash r : G_j \> T$}
+        \AxiomC{$x : F \> T \vdash r : G_j \> T$}
         \BinaryInfC{$x : F \> T : \inn_j \> r : G_1 \> T + G_2 \> T$}
@@
 Given is a constructor $c : A \> H \rightarrow H$, a type family $Y : H \rightarrow \Type$, and a term $f : \prod (x: A \> H), \bar{A} \> Y \> x \rightarrow  Y(c \> x)$.
-For a constructor term $F \> H \Vdash r : G \> H$ we define the \emph{lift $\dak{r}$ of $r$} with type 
+For a constructor term $F \> H \vdash r : G \> H$ we define the \emph{lift $\dak{r}$ of $r$} with type 
 $
@@
 \label{lem:constrTerm}
-Suppose, we have a constructor term $t$ such that $x : F \> T \Vdash t : G \>T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow P$.
+Suppose, we have a constructor term $t$ such that $x : F \> T \vdash t : G \>T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow P$.
 Then $t$ induces a map $\overline{t} : F \> P \rightarrow H_{\Con}^n \> (G \> P)$ by replacing the constructors $c_{\nonrec}$ and $c_{\rec}$ by $c_{\nonrec}'$ and $c_{\rec}'$ respectively.
@@
 \label{lem:constrCoh}
-Suppose, we have a constructor term $t$ such that $x : F \> T \Vdash t : G \> T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow Q$.
+Suppose, we have a constructor term $t$ such that $x : F \> T \vdash t : G \> T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow Q$.
 Furthermore, we assume that we have a map $f : Q \rightarrow P$

### 2017-03-29 Paper/Paper.tex
Fix `:`

@@
 %
-while a map $f \> \dprod{x \> A} B_1\,x \to B_2\,x$ lifts to
-$\lift{P}[f] \> \dprod{u : P[A]} \lift{P}[B_1]\,u \to \lift{P}[B_2]\,u$:
+while a map $f : \dprod{x \> A} B_1\,x \to B_2\,x$ lifts to
+$\lift{P}[f] : \dprod{u : P[A]} \lift{P}[B_1]\,u \to \lift{P}[B_2]\,u$:
 %
@@
 \label{def:constructor-term}
-Given is a function $c : A \> T \rightarrow T$ with $A$ polynomial and $T$ a type.
-Then we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F \> T \vdash t : G \> T$ can be derived using the following rules.
+Given a function $c : A \> T \rightarrow T$ with $A$ a polynomial and $T$ a type,
+we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F \> T \vdash t : G \> T$ can be derived using the following rules.
 \begin{gather*}
@@
         \AxiomC{$x : F \> T \vdash r : G_j \> T$}
-        \BinaryInfC{$x : F \> T : \inn_j \> r : G_1 \> T + G_2 \> T$}
+        \BinaryInfC{$x : F \> T \vdash \inn_j \> r : G_1 \> T + G_2 \> T$}
+        % shouldn't this be inl/inj instead of in_1/in_2?
         \bottomAlignProof
@@
 Given is a constructor $c : A \> H \rightarrow H$, a type family $Y : H \rightarrow \Type$, and a term $f : \prod (x: A \> H), \bar{A} \> Y \> x \rightarrow  Y(c \> x)$.
-For a constructor term $F \> H \vdash r : G \> H$ we define the \emph{lift $\dak{r}$ of $r$} with type 
+For a constructor term $x : F \> H \vdash r : G \> H$ we define the \emph{lift $\dak{r}$ of $r$} with type 
 $

### 2017-04-03 Paper/Paper.tex
Fixed part on the path coequalizer (now included in formalization).

@@
 | $\inP$ : $B \rightarrow \pcoeq \> A \> B \> f \> g$
-| $\glueP$ : $\prod (a : A), \ap \> \inC \> (\pi_1(\pi_3(p \> a))) = \ap \> \inC \> (\pi_2(\pi_3(p \> a)))$
+| $\glueP$ : $\prod (a : A), \ap \> \inP \> (\pi_1(\pi_3(p \> a))) = \ap \> \inP \> (\pi_2(\pi_3(p \> a)))$
 \end{lstlisting}
@@
 The introduction and computation rules are as expected, but we will give the elimination rule.
+
+For the elimination rule we first need a lemma.
+\begin{lemma}
+\label{lem:coherency_compose}
+Given is $Y : \pcoeq \rightarrow \Type$ and $i_Y : \prod (b : B), Y(\inP \> b)$.
+Then we have a term 
+\[
+\operatorname{coh} : 
+\prod (a : A), 
+(\pi_1 \> a)_*^{\lambda b, \, Y (\inP b)} (i_Y \> b_1) 
+= (\pi_2 \> a)_*^{\lambda b, \, Y (\inP b)} (i_Y \> b_1)
+\]
+\end{lemma}
+
+\begin{proof}
+For this we need to prove that for all type families $Y : A \rightarrow \Type$, maps $f : A \rightarrow B$, points $z : Y(f \> a)$, and paths $p : a = b$ we have
+\[
+\operatorname{tc} : p_*^{\lambda x, \, Y (f \> x)} \> z  =  (\ap \> f \> p)_*^Y \> z.
+\]	
+This can be proven with path induction. 
+Now we have the following equalities
+\begin{equation*}
+\begin{split}
+(\pi_1 \> a)_*^{\lambda b, \, Y (\inP b)} (i_Y \> b_1)
+&= 
+(\ap \> \inP \> p_1)_*^Y \> (i_Y \> b_1)
+\\
+&= 
+(\ap \> \inP \> p_2)_*^Y \> (i_Y \> b_1)
+\\
+&=
+(\pi_2 \> a)_*^{\lambda b, \, Y (\inP b)} (i_Y \> b_1)
+\end{split}
+\end{equation*}
+The first and the last follow from $\operatorname{tc}$, and the second from $\glueP$.
+\end{proof}
+
+Now we give the elimination rule of $\pcoeq$ for which we use $\operatorname{coh}$.
 \begin{equation*}
@@
         %       \noLine
-        \AxiomC{$\vdash g_Y : \prod (a : A), \apd \> i_Y \> (p_1 \> a) = \apd \> i_Y \> (p_2 \> a)$}
+        \AxiomC{$\vdash g_Y : \prod (a : A), \operatorname{coh}^{-1} \conc \apd \> i_Y \> (p_1 \> a) = \apd \> i_Y \> (p_2 \> a)$}
         \BinaryInfC{$\vdash \pcoeq\frec(i_Y, g_Y) : \prod (x : \pcoeq \> A \> B \> f \> g), Y \> x$}

### 2017-05-13 Paper/Paper.tex
Added new files to project

@@
   \texttt{Andrej.Bauer@andrej.com}}
-\affil[2]{Department of Computer Science, Radboud University, Nijmegen, The Netherlands\\
+\affil[2]{iCIS, Radboud University, Nijmegen, The Netherlands\\
   \texttt{nweide@cs.ru.nl}}
@@
 \begin{definition}
+\label{def:ap_ext_pt}
 Let $A, B$ be types, let $f, g : A \rightarrow B$ be maps, and let $x : A$ be a point of $A$.
